---
title: "SonarQube Warning Analysis: Pre vs Post Cursor Adoption"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)
```

# Overview

This analysis compares the distribution of SonarQube warnings before and after Cursor adoption, focusing on:

1. **Severity distribution** (BLOCKER, CRITICAL, MAJOR, MINOR, INFO)
2. **Warning type distribution** (BUG, CODE_SMELL, VULNERABILITY)
3. **Category distribution** (Logic Error, Code Hygiene, Accessibility, etc.)

## Load Required Libraries

```{r libraries}
library(tidyverse)
library(scales)
library(knitr)
library(kableExtra)
library(ggplot2)
library(gridExtra)
library(RColorBrewer)

# Set theme
theme_set(theme_minimal(base_size = 12))
```

# Data Loading

```{r load-data}
# Load warning definitions (rule metadata)
definitions <- read_csv("../data/sonarqube_warning_definitions.csv",
                       show_col_types = FALSE)

# Load actual warnings
warnings <- read_csv("../data/sonarqube_warnings.csv",
                    show_col_types = FALSE)

# Display data structure
cat("Warning definitions:", nrow(definitions), "rules\n")
cat("Total warnings:", nrow(warnings), "warnings\n")
cat("\nColumns in warnings data:\n")
print(names(warnings))
```

# Data Preparation

```{r data-prep}
# Join warnings with definitions to get severity, type, and category
warnings_enriched <- warnings %>%
  left_join(definitions, by = "rule") %>%
  mutate(
    # Create period label
    period = ifelse(relative_period < 0, "Pre-Cursor", "Post-Cursor"),
    period = factor(period, levels = c("Pre-Cursor", "Post-Cursor")),

    # Ensure severity is ordered
    severity = factor(severity,
                     levels = c("INFO", "MINOR", "MAJOR", "CRITICAL", "BLOCKER")),

    # Ensure type is factor
    type = factor(type, levels = c("CODE_SMELL", "BUG", "VULNERABILITY")),

    # Fill in missing categories as "Unmapped"
    category = ifelse(is.na(category) | category == "", "Unmapped", category),
    category = factor(category)
  )

# Summary statistics
cat("\nData summary:\n")
cat("Pre-Cursor warnings:", sum(warnings_enriched$period == "Pre-Cursor"), "\n")
cat("Post-Cursor warnings:", sum(warnings_enriched$period == "Post-Cursor"), "\n")
cat("Total repos:", n_distinct(warnings_enriched$repo_name), "\n")
```

# Overall Statistics

```{r overall-stats}
# Calculate summary statistics by period
overall_summary <- warnings_enriched %>%
  group_by(period) %>%
  summarise(
    total_warnings = n(),
    unique_repos = n_distinct(repo_name),
    unique_rules = n_distinct(rule),
    warnings_per_repo = n() / n_distinct(repo_name)
  )

kable(overall_summary,
      caption = "Overall Warning Statistics by Period",
      digits = 2) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

# Severity Distribution

## Severity Counts

```{r severity-counts}
severity_summary <- warnings_enriched %>%
  filter(!is.na(severity)) %>%
  group_by(period, severity) %>%
  summarise(count = n(), .groups = "drop") %>%
  group_by(period) %>%
  mutate(
    total = sum(count),
    percentage = (count / total) * 100
  )

# Wide format for comparison
severity_wide <- severity_summary %>%
  select(severity, period, count, percentage) %>%
  pivot_wider(
    names_from = period,
    values_from = c(count, percentage),
    names_glue = "{period}_{.value}"
  ) %>%
  mutate(
    count_change = `Post-Cursor_count` - `Pre-Cursor_count`,
    pct_change = `Post-Cursor_percentage` - `Pre-Cursor_percentage`
  )

kable(severity_wide,
      caption = "Severity Distribution Comparison",
      digits = 2) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

## Severity Visualization

```{r severity-plot, fig.height=6}
# Bar plot of severity distribution
p1 <- ggplot(severity_summary, aes(x = severity, y = percentage, fill = period)) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0.8) +
  geom_text(aes(label = sprintf("%.1f%%", percentage)),
            position = position_dodge(width = 0.9),
            vjust = -0.5, size = 3) +
  scale_fill_manual(values = c("Pre-Cursor" = "#E69F00", "Post-Cursor" = "#56B4E9")) +
  labs(
    title = "Severity Distribution: Pre vs Post Cursor",
    x = "Severity Level",
    y = "Percentage of Warnings",
    fill = "Period"
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "top")

# Stacked percentage
p2 <- severity_summary %>%
  group_by(period) %>%
  mutate(cum_pct = cumsum(percentage)) %>%
  ggplot(aes(x = period, y = percentage, fill = severity)) +
  geom_bar(stat = "identity", alpha = 0.8) +
  geom_text(aes(label = sprintf("%.1f%%", percentage)),
            position = position_stack(vjust = 0.5), size = 3) +
  scale_fill_brewer(palette = "YlOrRd", direction = 1) +
  labs(
    title = "Severity Distribution (Stacked)",
    x = "Period",
    y = "Percentage",
    fill = "Severity"
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "right")

grid.arrange(p1, p2, ncol = 2)
```

# Warning Type Distribution

## Type Counts

```{r type-counts}
type_summary <- warnings_enriched %>%
  filter(!is.na(type)) %>%
  group_by(period, type) %>%
  summarise(count = n(), .groups = "drop") %>%
  group_by(period) %>%
  mutate(
    total = sum(count),
    percentage = (count / total) * 100
  )

# Wide format
type_wide <- type_summary %>%
  select(type, period, count, percentage) %>%
  pivot_wider(
    names_from = period,
    values_from = c(count, percentage),
    names_glue = "{period}_{.value}"
  ) %>%
  mutate(
    count_change = `Post-Cursor_count` - `Pre-Cursor_count`,
    pct_change = `Post-Cursor_percentage` - `Pre-Cursor_percentage`
  )

kable(type_wide,
      caption = "Warning Type Distribution Comparison",
      digits = 2) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

## Type Visualization

```{r type-plot, fig.height=6}
ggplot(type_summary, aes(x = type, y = percentage, fill = period)) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0.8) +
  geom_text(aes(label = sprintf("%.1f%%\n(n=%s)", percentage,
                                scales::comma(count))),
            position = position_dodge(width = 0.9),
            vjust = -0.5, size = 3.5) +
  scale_fill_manual(values = c("Pre-Cursor" = "#E69F00", "Post-Cursor" = "#56B4E9")) +
  labs(
    title = "Warning Type Distribution: Pre vs Post Cursor",
    subtitle = "BUG = Actual bugs, CODE_SMELL = Maintainability issues, VULNERABILITY = Security issues",
    x = "Warning Type",
    y = "Percentage of Warnings",
    fill = "Period"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "top",
    plot.subtitle = element_text(size = 10, color = "gray40")
  )
```

# Category Distribution

## Top 20 Categories

```{r category-counts}
category_summary <- warnings_enriched %>%
  filter(!is.na(category)) %>%
  group_by(period, category) %>%
  summarise(count = n(), .groups = "drop") %>%
  group_by(period) %>%
  mutate(
    total = sum(count),
    percentage = (count / total) * 100
  ) %>%
  ungroup()

# Get top 20 categories overall
top_categories <- category_summary %>%
  group_by(category) %>%
  summarise(total_count = sum(count)) %>%
  arrange(desc(total_count)) %>%
  head(20) %>%
  pull(category)

# Filter to top categories
category_top <- category_summary %>%
  filter(category %in% top_categories)

# Wide format
category_wide <- category_top %>%
  select(category, period, count, percentage) %>%
  pivot_wider(
    names_from = period,
    values_from = c(count, percentage),
    names_glue = "{period}_{.value}"
  ) %>%
  mutate(
    count_change = `Post-Cursor_count` - `Pre-Cursor_count`,
    pct_change = `Post-Cursor_percentage` - `Pre-Cursor_percentage`
  ) %>%
  arrange(desc(`Pre-Cursor_count` + `Post-Cursor_count`))

kable(category_wide,
      caption = "Top 20 Category Distribution Comparison",
      digits = 2) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                font_size = 11) %>%
  scroll_box(height = "500px")
```

## Category Visualization

```{r category-plot, fig.height=10}
# Reorder categories by total count
category_top <- category_top %>%
  mutate(category = fct_reorder(category, count, .fun = sum))

ggplot(category_top, aes(x = percentage, y = category, fill = period)) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0.8) +
  geom_text(aes(label = sprintf("%.1f%%", percentage)),
            position = position_dodge(width = 0.9),
            hjust = -0.1, size = 2.5) +
  scale_fill_manual(values = c("Pre-Cursor" = "#E69F00", "Post-Cursor" = "#56B4E9")) +
  scale_x_continuous(expand = expansion(mult = c(0, 0.15))) +
  labs(
    title = "Top 20 Warning Categories: Pre vs Post Cursor",
    x = "Percentage of Warnings",
    y = "Category",
    fill = "Period"
  ) +
  theme_minimal(base_size = 11) +
  theme(
    legend.position = "top",
    axis.text.y = element_text(size = 9)
  )
```

## Category Change Analysis

```{r category-change}
# Calculate percentage point change for all categories
category_change <- category_summary %>%
  select(category, period, percentage) %>%
  pivot_wider(names_from = period, values_from = percentage, values_fill = 0) %>%
  mutate(
    change = `Post-Cursor` - `Pre-Cursor`,
    abs_change = abs(change)
  ) %>%
  arrange(desc(abs_change)) %>%
  head(15)

ggplot(category_change, aes(x = change, y = fct_reorder(category, change))) +
  geom_col(aes(fill = change > 0), alpha = 0.8) +
  geom_text(aes(label = sprintf("%+.2f%%", change)),
            hjust = ifelse(category_change$change > 0, -0.1, 1.1),
            size = 3) +
  scale_fill_manual(
    values = c("TRUE" = "#D55E00", "FALSE" = "#009E73"),
    labels = c("Decreased", "Increased"),
    name = "Direction"
  ) +
  labs(
    title = "Top 15 Category Changes (Percentage Point Difference)",
    subtitle = "Post-Cursor % minus Pre-Cursor %",
    x = "Percentage Point Change",
    y = "Category"
  ) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "top")
```

# Statistical Tests

## Chi-Square Test: Severity Distribution

```{r chi-square-severity}
# Create contingency table
severity_table <- warnings_enriched %>%
  filter(!is.na(severity)) %>%
  count(period, severity) %>%
  pivot_wider(names_from = period, values_from = n, values_fill = 0) %>%
  column_to_rownames("severity")

# Chi-square test
chi_result_severity <- chisq.test(severity_table)

cat("Chi-Square Test for Severity Distribution\n")
cat("=========================================\n")
cat("X-squared =", chi_result_severity$statistic, "\n")
cat("df =", chi_result_severity$parameter, "\n")
cat("p-value =", chi_result_severity$p.value, "\n")
cat("\nInterpretation:",
    ifelse(chi_result_severity$p.value < 0.05,
           "SIGNIFICANT difference in severity distribution (p < 0.05)",
           "NO significant difference in severity distribution (p >= 0.05)"), "\n")
```

## Chi-Square Test: Type Distribution

```{r chi-square-type}
# Create contingency table
type_table <- warnings_enriched %>%
  filter(!is.na(type)) %>%
  count(period, type) %>%
  pivot_wider(names_from = period, values_from = n, values_fill = 0) %>%
  column_to_rownames("type")

# Chi-square test
chi_result_type <- chisq.test(type_table)

cat("Chi-Square Test for Type Distribution\n")
cat("======================================\n")
cat("X-squared =", chi_result_type$statistic, "\n")
cat("df =", chi_result_type$parameter, "\n")
cat("p-value =", chi_result_type$p.value, "\n")
cat("\nInterpretation:",
    ifelse(chi_result_type$p.value < 0.05,
           "SIGNIFICANT difference in type distribution (p < 0.05)",
           "NO significant difference in type distribution (p >= 0.05)"), "\n")
```

## Chi-Square Test: Top Category Distribution

```{r chi-square-category}
# Create contingency table for top 10 categories
category_table <- warnings_enriched %>%
  filter(category %in% top_categories[1:10]) %>%
  count(period, category) %>%
  pivot_wider(names_from = period, values_from = n, values_fill = 0) %>%
  column_to_rownames("category")

# Chi-square test
chi_result_category <- chisq.test(category_table)

cat("Chi-Square Test for Top 10 Category Distribution\n")
cat("=================================================\n")
cat("X-squared =", chi_result_category$statistic, "\n")
cat("df =", chi_result_category$parameter, "\n")
cat("p-value =", chi_result_category$p.value, "\n")
cat("\nInterpretation:",
    ifelse(chi_result_category$p.value < 0.05,
           "SIGNIFICANT difference in category distribution (p < 0.05)",
           "NO significant difference in category distribution (p >= 0.05)"), "\n")
```

# Per-Repository Analysis

```{r per-repo-analysis}
# Calculate warnings per repo by period
repo_summary <- warnings_enriched %>%
  group_by(repo_name, period) %>%
  summarise(
    total_warnings = n(),
    .groups = "drop"
  ) %>%
  pivot_wider(
    names_from = period,
    values_from = total_warnings,
    values_fill = 0
  ) %>%
  mutate(
    change = `Post-Cursor` - `Pre-Cursor`,
    pct_change = ifelse(`Pre-Cursor` > 0,
                        (change / `Pre-Cursor`) * 100,
                        NA)
  )

# Summary statistics
cat("Per-Repository Warning Changes\n")
cat("===============================\n")
cat("Repos with decreased warnings:", sum(repo_summary$change < 0, na.rm = TRUE), "\n")
cat("Repos with increased warnings:", sum(repo_summary$change > 0, na.rm = TRUE), "\n")
cat("Repos with no change:", sum(repo_summary$change == 0, na.rm = TRUE), "\n")
cat("\nMean change:", mean(repo_summary$change, na.rm = TRUE), "\n")
cat("Median change:", median(repo_summary$change, na.rm = TRUE), "\n")
cat("Mean % change:", mean(repo_summary$pct_change, na.rm = TRUE), "%\n")
cat("Median % change:", median(repo_summary$pct_change, na.rm = TRUE), "%\n")
```

```{r repo-change-histogram, fig.height=6}
ggplot(repo_summary, aes(x = change)) +
  geom_histogram(binwidth = 10, fill = "#56B4E9", alpha = 0.7, color = "black") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "red", linewidth = 1) +
  geom_vline(xintercept = median(repo_summary$change, na.rm = TRUE),
             linetype = "dashed", color = "blue", linewidth = 1) +
  labs(
    title = "Distribution of Warning Count Changes per Repository",
    subtitle = "Red line = no change, Blue line = median change",
    x = "Change in Warning Count (Post - Pre)",
    y = "Number of Repositories"
  ) +
  theme_minimal(base_size = 12)
```

# Session Info

```{r session-info}
sessionInfo()
```
