---
title: "Diff-in-Diff Borusyak: AI-Generated-Like Code Outcomes"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
params:
  panel_file: "repo_python/run-py-3b/strict/panel_event_monthly_agc_py.csv"
  validation_summary_file: "repo_python/tmp/run-py-3c/strict/agc_did_input_validation_summary.json"
  helper_file: "proc_r/diff_in_diff_borusyak_helpers.R"
  out_dir: "repo_python/run-py-3d/strict"
  panel_label: "strict"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = TRUE, message = TRUE)
options(bitmapType = "cairo")

project_root <- Sys.getenv("PROJECT_ROOT", unset = normalizePath(".", mustWork = TRUE))
project_root <- normalizePath(project_root, mustWork = TRUE)

resolve_project_path <- function(path_value) {
  if (is.null(path_value) || identical(path_value, "")) {
    return("")
  }

  if (grepl("^/", path_value)) {
    return(normalizePath(path_value, mustWork = FALSE))
  }

  normalizePath(file.path(project_root, path_value), mustWork = FALSE)
}

panel_path <- resolve_project_path(params$panel_file)
validation_summary_path <- resolve_project_path(params$validation_summary_file)
helper_path <- resolve_project_path(params$helper_file)
out_dir <- resolve_project_path(params$out_dir)
panel_label <- as.character(params$panel_label)

dir.create(out_dir, recursive = TRUE, showWarnings = FALSE)
```

# Purpose

This notebook estimates the effect of observed Cursor adoption on repository-month AI-generated-like code outcomes using the Borusyak et al. imputation difference-in-differences estimator.

The primary outcome is the proportion of scored top-level Python function and class blocks whose AST-based structural representations are classified as AI-generated-like. Function-only and class-only proportions are analyzed as robustness outcomes.

Two adjusted specifications are compared on the same complete-case sample for each outcome:

1. **Paper NCLOC specification:** uses `ncloc_paper` from the frozen paper panel.
2. **Python snapshot NCLOC specification:** uses `ncloc_python_snapshot` calculated from the exact exported historical Python snapshot.

The outcome captures structural patterns associated with AI-generated code. It does not establish the actual provenance of an individual block or identify which AI tool generated or assisted with it.

Because the outcomes are proportions, coefficients are reported in both proportion units and percentage points. They are not transformed with `exp(beta) - 1`.

# Load Packages and Helper Functions

```{r load-packages}
library(data.table)
library(dplyr)
library(ggplot2)
library(didimputation)
library(jsonlite)

if (!file.exists(helper_path)) {
  stop("Borusyak helper file not found: ", helper_path)
}

source(helper_path)
```

# Utility Functions

```{r utility-functions}
normalize_yyyymm <- function(x) {
  x <- as.character(x)
  x[x %in% c("", "NA", "NaN", "NULL", "None")] <- NA_character_
  x <- gsub("-", "", x)
  suppressWarnings(as.integer(x))
}

yyyymm_to_month_id <- function(x) {
  x <- as.integer(x)
  year <- x %/% 100L
  month <- x %% 100L

  out <- year * 12L + month
  out[is.na(x) | month < 1L | month > 12L] <- NA_integer_
  out
}

require_columns <- function(data, required, label) {
  missing <- setdiff(required, names(data))
  if (length(missing) > 0) {
    stop(label, " missing required columns: ", paste(missing, collapse = ", "))
  }
}

numeric_if_present <- function(data, columns) {
  for (column_name in intersect(columns, names(data))) {
    set(
      data,
      j = column_name,
      value = suppressWarnings(as.numeric(data[[column_name]]))
    )
  }

  invisible(data)
}

safe_ratio <- function(numerator, denominator) {
  out <- rep(NA_real_, length(denominator))
  valid <- !is.na(numerator) & !is.na(denominator) & denominator > 0
  out[valid] <- numerator[valid] / denominator[valid]
  out
}

empty_model_error_table <- function() {
  data.frame(
    panel = character(),
    specification = character(),
    outcome = character(),
    model_type = character(),
    error = character(),
    stringsAsFactors = FALSE
  )
}
```

# Validate the Upstream Input

```{r validate-upstream}
cat("Project root:", project_root, "\n")
cat("Panel path:", panel_path, "\n")
cat("Validation summary:", validation_summary_path, "\n")
cat("Output directory:", out_dir, "\n")
cat("Panel label:", panel_label, "\n")

if (!file.exists(panel_path)) {
  stop("AGC DiD input panel not found: ", panel_path)
}

if (!file.exists(validation_summary_path)) {
  stop("run-py-3c validation summary not found: ", validation_summary_path)
}

validation_summary <- jsonlite::fromJSON(validation_summary_path)

if (is.null(validation_summary$status) || validation_summary$status != "PASS") {
  stop(
    "run-py-3c validation status must be PASS. Found: ",
    validation_summary$status
  )
}

if (!is.null(validation_summary$checks_failed) &&
    as.integer(validation_summary$checks_failed) != 0L) {
  stop(
    "run-py-3c validation reports failed checks: ",
    validation_summary$checks_failed
  )
}

cat("Validated upstream rows:", validation_summary$rows, "\n")
cat("Validated upstream repositories:", validation_summary$repositories, "\n")
cat("Validated upstream checks:", validation_summary$checks_passed,
    "/", validation_summary$checks_total, "\n")
```

# Load and Normalize the AGC Panel

```{r load-panel}
panel_raw <- fread(panel_path)

required_columns <- c(
  "repo_name",
  "time",
  "dataset_source",
  "event",
  "post_event",
  "time_to_event",
  "is_treatment",
  "contributors",
  "stars",
  "issues",
  "age",
  "ncloc_paper",
  "ncloc_python_snapshot",
  "top_level_blocks_scored",
  "agc_top_level_blocks",
  "human_top_level_blocks",
  "agc_top_level_block_ratio",
  "function_blocks_scored",
  "agc_function_blocks",
  "human_function_blocks",
  "agc_function_block_ratio",
  "class_blocks_scored",
  "agc_class_blocks",
  "human_class_blocks",
  "agc_class_block_ratio"
)

require_columns(panel_raw, required_columns, "AGC DiD input panel")

numeric_columns <- c(
  "post_event",
  "time_to_event",
  "is_treatment",
  "contributors",
  "stars",
  "issues",
  "age",
  "ncloc_paper",
  "ncloc_python_snapshot",
  "top_level_blocks_scored",
  "agc_top_level_blocks",
  "human_top_level_blocks",
  "agc_top_level_block_ratio",
  "function_blocks_scored",
  "agc_function_blocks",
  "human_function_blocks",
  "agc_function_block_ratio",
  "class_blocks_scored",
  "agc_class_blocks",
  "human_class_blocks",
  "agc_class_block_ratio"
)

numeric_if_present(panel_raw, numeric_columns)

panel_raw[, time_yyyymm := normalize_yyyymm(time)]
panel_raw[, event_yyyymm := normalize_yyyymm(event)]
panel_raw[dataset_source == "control", event_yyyymm := 0L]

panel_raw[, time_id := yyyymm_to_month_id(time_yyyymm)]
panel_raw[, event_id := fifelse(
  dataset_source == "control",
  0L,
  yyyymm_to_month_id(event_yyyymm)
)]

panel_raw[, repo_name_str := repo_name]
panel_raw[, repo_id := as.integer(factor(repo_name_str))]
panel_raw[, ever_treated := as.integer(dataset_source == "treatment")]

# Match the original paper covariate scaling. NCLOC remains on its raw scale.
panel_raw[, age_log := fifelse(!is.na(age) & age >= 0, log1p(age), NA_real_)]
panel_raw[, contributors_log := fifelse(
  !is.na(contributors) & contributors >= 0,
  log1p(contributors),
  NA_real_
)]
panel_raw[, stars_log := fifelse(
  !is.na(stars) & stars >= 0,
  log1p(stars),
  NA_real_
)]
panel_raw[, issues_log := fifelse(
  !is.na(issues) & issues >= 0,
  log1p(issues),
  NA_real_
)]

cat("Loaded rows:", nrow(panel_raw), "\n")
cat("Loaded repositories:", uniqueN(panel_raw$repo_name), "\n")
cat("Treatment rows:", sum(panel_raw$dataset_source == "treatment"), "\n")
cat("Control rows:", sum(panel_raw$dataset_source == "control"), "\n")
cat("Calendar range:", min(panel_raw$time, na.rm = TRUE), "to",
    max(panel_raw$time, na.rm = TRUE), "\n")
```

# Panel Sanity Checks

```{r panel-checks}
key_columns <- c("repo_name", "time", "dataset_source")
duplicate_keys <- duplicated(panel_raw, by = key_columns)

recomputed_time_to_event <- rep(NA_real_, nrow(panel_raw))
treated_idx <- panel_raw$dataset_source == "treatment"
recomputed_time_to_event[treated_idx] <-
  panel_raw$time_id[treated_idx] - panel_raw$event_id[treated_idx]

panel_checks <- data.frame(
  check = c(
    "panel_label",
    "rows",
    "repositories",
    "treatment_rows",
    "control_rows",
    "treatment_repositories",
    "control_repositories",
    "duplicate_keys",
    "time_id_missing",
    "treatment_event_id_missing",
    "control_event_id_nonzero",
    "is_treatment_post_event_mismatch",
    "time_to_event_mismatch",
    "top_level_count_mismatch",
    "function_count_mismatch",
    "class_count_mismatch",
    "top_level_ratio_mismatch",
    "function_ratio_mismatch",
    "class_ratio_mismatch",
    "ncloc_paper_nonmissing",
    "ncloc_python_snapshot_nonmissing",
    "upstream_validation_status",
    "upstream_checks_failed"
  ),
  value = c(
    panel_label,
    nrow(panel_raw),
    uniqueN(panel_raw$repo_name),
    sum(panel_raw$dataset_source == "treatment"),
    sum(panel_raw$dataset_source == "control"),
    uniqueN(panel_raw[dataset_source == "treatment", repo_name]),
    uniqueN(panel_raw[dataset_source == "control", repo_name]),
    sum(duplicate_keys),
    sum(is.na(panel_raw$time_id)),
    sum(panel_raw$dataset_source == "treatment" & is.na(panel_raw$event_id)),
    sum(panel_raw$dataset_source == "control" & panel_raw$event_id != 0L),
    sum(panel_raw$is_treatment != panel_raw$post_event, na.rm = TRUE),
    sum(
      panel_raw$dataset_source == "treatment" &
        !is.na(panel_raw$time_to_event) &
        panel_raw$time_to_event != recomputed_time_to_event,
      na.rm = TRUE
    ),
    sum(
      panel_raw$top_level_blocks_scored !=
        panel_raw$function_blocks_scored + panel_raw$class_blocks_scored,
      na.rm = TRUE
    ),
    sum(
      panel_raw$function_blocks_scored !=
        panel_raw$agc_function_blocks + panel_raw$human_function_blocks,
      na.rm = TRUE
    ),
    sum(
      panel_raw$class_blocks_scored !=
        panel_raw$agc_class_blocks + panel_raw$human_class_blocks,
      na.rm = TRUE
    ),
    sum(
      abs(
        panel_raw$agc_top_level_block_ratio -
          safe_ratio(
            panel_raw$agc_top_level_blocks,
            panel_raw$top_level_blocks_scored
          )
      ) > 1e-12,
      na.rm = TRUE
    ),
    sum(
      abs(
        panel_raw$agc_function_block_ratio -
          safe_ratio(
            panel_raw$agc_function_blocks,
            panel_raw$function_blocks_scored
          )
      ) > 1e-12,
      na.rm = TRUE
    ),
    sum(
      abs(
        panel_raw$agc_class_block_ratio -
          safe_ratio(
            panel_raw$agc_class_blocks,
            panel_raw$class_blocks_scored
          )
      ) > 1e-12,
      na.rm = TRUE
    ),
    sum(!is.na(panel_raw$ncloc_paper)),
    sum(!is.na(panel_raw$ncloc_python_snapshot)),
    validation_summary$status,
    validation_summary$checks_failed
  ),
  stringsAsFactors = FALSE
)

print(panel_checks)

fwrite(
  panel_checks,
  file.path(out_dir, "borusyak_agc_panel_checks.csv")
)

hard_failure_checks <- c(
  sum(duplicate_keys),
  sum(is.na(panel_raw$time_id)),
  sum(panel_raw$dataset_source == "treatment" & is.na(panel_raw$event_id)),
  sum(panel_raw$dataset_source == "control" & panel_raw$event_id != 0L),
  sum(panel_raw$is_treatment != panel_raw$post_event, na.rm = TRUE)
)

if (any(hard_failure_checks != 0)) {
  stop("AGC panel sanity checks failed. See borusyak_agc_panel_checks.csv.")
}
```

# Outcomes and Specifications

```{r outcomes-and-specifications}
outcome_definitions <- data.frame(
  outcome = c(
    "agc_top_level_block_ratio",
    "agc_function_block_ratio",
    "agc_class_block_ratio"
  ),
  outcome_label = c(
    "AGC-like Top-Level Block Share",
    "AGC-like Function Block Share",
    "AGC-like Class Block Share"
  ),
  denominator = c(
    "top_level_blocks_scored",
    "function_blocks_scored",
    "class_blocks_scored"
  ),
  role = c("primary", "robustness", "robustness"),
  stringsAsFactors = FALSE
)

specification_definitions <- data.frame(
  specification = c("paper_ncloc", "python_snapshot_ncloc"),
  specification_label = c(
    "Paper NCLOC",
    "Python Snapshot NCLOC"
  ),
  ncloc_column = c("ncloc_paper", "ncloc_python_snapshot"),
  stringsAsFactors = FALSE
)

print(outcome_definitions)
print(specification_definitions)
```

# Prepare Common Samples

```{r prepare-common-samples}
common_covariates <- c(
  "age_log",
  "contributors_log",
  "stars_log",
  "issues_log",
  "ncloc_paper",
  "ncloc_python_snapshot"
)

common_samples <- list()
sample_summary_rows <- list()

for (outcome_var in outcome_definitions$outcome) {
  required <- c(
    "repo_id",
    "time_id",
    "event_id",
    "dataset_source",
    outcome_var,
    common_covariates
  )

  sample_data <- copy(panel_raw)
  sample_data <- sample_data[complete.cases(sample_data[, ..required])]

  if (nrow(sample_data) == 0) {
    stop("No complete rows remain for outcome: ", outcome_var)
  }

  sample_data[, sample_key := paste(repo_name, time, dataset_source, sep = "|")]
  common_samples[[outcome_var]] <- sample_data

  sample_summary_rows[[length(sample_summary_rows) + 1]] <- data.frame(
    outcome = outcome_var,
    outcome_label = outcome_definitions$outcome_label[
      match(outcome_var, outcome_definitions$outcome)
    ],
    rows = nrow(sample_data),
    repositories = uniqueN(sample_data$repo_id),
    treatment_rows = sum(sample_data$dataset_source == "treatment"),
    control_rows = sum(sample_data$dataset_source == "control"),
    treatment_repositories = uniqueN(
      sample_data[dataset_source == "treatment", repo_id]
    ),
    control_repositories = uniqueN(
      sample_data[dataset_source == "control", repo_id]
    ),
    min_time = min(sample_data$time),
    max_time = max(sample_data$time),
    stringsAsFactors = FALSE
  )
}

sample_summary <- bind_rows(sample_summary_rows)
print(sample_summary)

fwrite(
  sample_summary,
  file.path(out_dir, "borusyak_agc_sample_by_outcome.csv")
)
```

# First-Stage Definition

```{r first-stage}
first_stage_formula <-
  ~ age_log + ncloc_model + contributors_log + stars_log + issues_log |
    repo_id + time_id

cat("First-stage formula shared by both specifications:\n")
print(first_stage_formula)
cat("\nOnly ncloc_model changes between the two specifications.\n")
```

# Static Borusyak Effects

```{r static-effects}
static_rows <- list()
model_error_rows <- list()

for (outcome_var in outcome_definitions$outcome) {
  base_sample <- common_samples[[outcome_var]]
  outcome_label <- outcome_definitions$outcome_label[
    match(outcome_var, outcome_definitions$outcome)
  ]

  for (spec_index in seq_len(nrow(specification_definitions))) {
    specification <- specification_definitions$specification[spec_index]
    specification_label <-
      specification_definitions$specification_label[spec_index]
    ncloc_column <- specification_definitions$ncloc_column[spec_index]

    model_data <- copy(base_sample)
    model_data[, ncloc_model := get(ncloc_column)]

    cat(
      "Running static Borusyak model:",
      specification,
      "|",
      outcome_var,
      "| rows =",
      nrow(model_data),
      "\n"
    )

    result <- tryCatch(
      run_borusyak_static(
        data = model_data,
        outcome_var = outcome_var,
        first_stage_formula = first_stage_formula,
        idname = "repo_id",
        tname = "time_id",
        gname = "event_id"
      ),
      error = function(e) {
        model_error_rows[[length(model_error_rows) + 1]] <<- data.frame(
          panel = panel_label,
          specification = specification,
          outcome = outcome_var,
          model_type = "static",
          error = conditionMessage(e),
          stringsAsFactors = FALSE
        )
        NULL
      }
    )

    extracted <- extract_static_result(result, outcome_var)
    extracted$panel <- panel_label
    extracted$specification <- specification
    extracted$specification_label <- specification_label
    extracted$ncloc_column <- ncloc_column
    extracted$outcome_label <- outcome_label
    extracted$sample_rows <- nrow(model_data)
    extracted$sample_repositories <- uniqueN(model_data$repo_id)
    extracted$estimate_percentage_points <- extracted$estimate * 100
    extracted$conf_low_percentage_points <- extracted$conf_low * 100
    extracted$conf_high_percentage_points <- extracted$conf_high * 100

    static_rows[[length(static_rows) + 1]] <- extracted
  }
}

static_df <- bind_rows(static_rows)
print(static_df)

fwrite(
  static_df,
  file.path(out_dir, "borusyak_agc_static_effects.csv")
)
```

# Dynamic Borusyak Effects

```{r dynamic-effects}
dynamic_rows <- list()

for (outcome_var in outcome_definitions$outcome) {
  base_sample <- common_samples[[outcome_var]]
  outcome_label <- outcome_definitions$outcome_label[
    match(outcome_var, outcome_definitions$outcome)
  ]

  for (spec_index in seq_len(nrow(specification_definitions))) {
    specification <- specification_definitions$specification[spec_index]
    specification_label <-
      specification_definitions$specification_label[spec_index]
    ncloc_column <- specification_definitions$ncloc_column[spec_index]

    model_data <- copy(base_sample)
    model_data[, ncloc_model := get(ncloc_column)]

    cat(
      "Running dynamic Borusyak model:",
      specification,
      "|",
      outcome_var,
      "| rows =",
      nrow(model_data),
      "\n"
    )

    result <- tryCatch(
      run_borusyak_dynamic(
        data = model_data,
        outcome_var = outcome_var,
        first_stage_formula = first_stage_formula,
        horizon = -6:6,
        pretrends = -6:-2,
        idname = "repo_id",
        tname = "time_id",
        gname = "event_id"
      ),
      error = function(e) {
        model_error_rows[[length(model_error_rows) + 1]] <<- data.frame(
          panel = panel_label,
          specification = specification,
          outcome = outcome_var,
          model_type = "dynamic",
          error = conditionMessage(e),
          stringsAsFactors = FALSE
        )
        NULL
      }
    )

    extracted <- extract_dynamic_result(
      result,
      outcome = outcome_var,
      outcome_label = outcome_label,
      min_horizon = -6,
      max_horizon = 6
    )

    if (nrow(extracted) > 0) {
      extracted$panel <- panel_label
      extracted$specification <- specification
      extracted$specification_label <- specification_label
      extracted$ncloc_column <- ncloc_column
      extracted$sample_rows <- nrow(model_data)
      extracted$sample_repositories <- uniqueN(model_data$repo_id)
      extracted$estimate_percentage_points <- extracted$estimate * 100
      extracted$conf_low_percentage_points <- extracted$conf_low * 100
      extracted$conf_high_percentage_points <- extracted$conf_high * 100

      dynamic_rows[[length(dynamic_rows) + 1]] <- extracted
    }
  }
}

dynamic_df <- bind_rows(dynamic_rows)
print(dynamic_df)

fwrite(
  dynamic_df,
  file.path(out_dir, "borusyak_agc_dynamic_effects.csv")
)

model_errors <- if (length(model_error_rows) > 0) {
  bind_rows(model_error_rows)
} else {
  empty_model_error_table()
}

fwrite(
  model_errors,
  file.path(out_dir, "borusyak_agc_model_errors.csv")
)

if (nrow(model_errors) > 0) {
  print(model_errors)
  stop("One or more Borusyak models failed. See borusyak_agc_model_errors.csv.")
}
```

# Pre-Treatment Diagnostics

```{r pretrend-diagnostics}
if (nrow(dynamic_df) > 0) {
  pretrend_summary <- dynamic_df %>%
    filter(time >= -6, time <= -2) %>%
    group_by(
      panel,
      specification,
      specification_label,
      outcome,
      outcome_label
    ) %>%
    summarise(
      pre_periods_available = n(),
      pre_periods_ci_excludes_zero = sum(significant %in% TRUE, na.rm = TRUE),
      all_preperiod_cis_include_zero = all(!(significant %in% TRUE)),
      max_absolute_pretrend_estimate = max(abs(estimate), na.rm = TRUE),
      .groups = "drop"
    )
} else {
  pretrend_summary <- data.frame()
}

print(pretrend_summary)

fwrite(
  pretrend_summary,
  file.path(out_dir, "borusyak_agc_pretrend_summary.csv")
)
```

# Static Effect Table

```{r static-table}
static_display <- static_df %>%
  select(
    specification_label,
    outcome_label,
    estimate_percentage_points,
    conf_low_percentage_points,
    conf_high_percentage_points,
    sample_rows,
    sample_repositories,
    note
  ) %>%
  arrange(outcome_label, specification_label)

knitr::kable(
  static_display,
  digits = 3,
  caption = paste(
    "Static Borusyak Effects on AGC-Like Block Shares",
    "(percentage points)"
  )
)
```

# Dynamic Event-Study Plot

```{r dynamic-plot, fig.width=12, fig.height=6}
if (nrow(dynamic_df) > 0) {
  dynamic_plot_data <- copy(as.data.table(dynamic_df))
  dynamic_plot_data[, outcome_label := factor(
    outcome_label,
    levels = outcome_definitions$outcome_label
  )]
  dynamic_plot_data[, specification_label := factor(
    specification_label,
    levels = specification_definitions$specification_label
  )]

  position <- position_dodge(width = 0.35)

  dynamic_plot <- ggplot(
    dynamic_plot_data,
    aes(
      x = time,
      y = estimate_percentage_points,
      color = specification_label,
      group = specification_label
    )
  ) +
    geom_errorbar(
      aes(
        ymin = conf_low_percentage_points,
        ymax = conf_high_percentage_points,
        linetype = significant
      ),
      position = position,
      width = 0.3
    ) +
    geom_point(
      aes(shape = significant),
      position = position,
      size = 1.8
    ) +
    geom_hline(yintercept = 0, linetype = "dashed") +
    geom_vline(xintercept = -0.5, linetype = "dashed") +
    scale_x_continuous(breaks = -6:6) +
    scale_shape_manual(
      values = c("TRUE" = 19, "FALSE" = 1),
      name = "CI excludes zero"
    ) +
    scale_linetype_manual(
      values = c("TRUE" = "solid", "FALSE" = "dotted"),
      name = "CI excludes zero"
    ) +
    facet_wrap(~ outcome_label, scales = "free_y", ncol = 1) +
    labs(
      title = paste("Borusyak AGC DiD:", panel_label),
      subtitle = paste(
        "Common outcome-specific samples;",
        "paper NCLOC versus exact Python snapshot NCLOC"
      ),
      x = "Months Relative to First Observed Cursor Adoption",
      y = "Treatment Effect (percentage points)",
      color = "Specification",
      caption = paste(
        "Outcomes are AGC-like block proportions.",
        "Filled points indicate that the confidence interval excludes zero."
      )
    ) +
    theme_minimal() +
    theme(
      panel.grid.minor = element_blank(),
      legend.position = "bottom",
      plot.caption = element_text(hjust = 0.5, size = 8)
    )

  print(dynamic_plot)

  ggsave(
    filename = file.path(out_dir, "dynamic_effects_borusyak_agc.pdf"),
    plot = dynamic_plot,
    width = 12,
    height = 6
  )
} else {
  cat("No dynamic effects are available to plot.\n")
}
```

# Model Metadata

```{r metadata}
metadata <- data.frame(
  key = c(
    "script",
    "source_notebook",
    "helper_file",
    "panel_label",
    "panel_path",
    "validation_summary_path",
    "validation_status",
    "validation_checks_passed",
    "validation_checks_total",
    "out_dir",
    "outcomes",
    "primary_outcome",
    "specifications",
    "common_covariates",
    "first_stage_formula",
    "time_encoding",
    "dynamic_horizon",
    "pretrend_horizon",
    "outcome_scale",
    "interpretation",
    "limitation"
  ),
  value = c(
    "proc_r/DiffInDiffBorusyak_AGC.Rmd",
    "DiffInDiffBorusyak.Rmd",
    params$helper_file,
    panel_label,
    panel_path,
    validation_summary_path,
    validation_summary$status,
    validation_summary$checks_passed,
    validation_summary$checks_total,
    out_dir,
    paste(outcome_definitions$outcome, collapse = ", "),
    "agc_top_level_block_ratio",
    paste(specification_definitions$specification, collapse = ", "),
    paste(common_covariates, collapse = ", "),
    paste(deparse(first_stage_formula), collapse = " "),
    "sequential calendar-month id",
    "-6 through +6 months",
    "-6 through -2 months",
    "proportion; reported as percentage points",
    paste(
      "Change in the repository-month share of top-level Python blocks",
      "classified as AI-generated-like after observed Cursor adoption"
    ),
    paste(
      "The detector outcome captures structural similarity to AI-generated",
      "code and does not establish block provenance or tool identity."
    )
  ),
  stringsAsFactors = FALSE
)

print(metadata)

fwrite(
  metadata,
  file.path(out_dir, "borusyak_agc_model_metadata.csv")
)
```

# Session Info

```{r session-info}
sessionInfo()
```
