---
title: "Diff-in-Diff Borusyak: Regular-Function Count Contrast"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = TRUE, message = TRUE)
options(bitmapType = "cairo")

project_root <- Sys.getenv(
  "PROJECT_ROOT",
  unset = normalizePath(".", mustWork = TRUE)
)
project_root <- normalizePath(project_root, mustWork = TRUE)

resolve_project_path <- function(path_value) {
  if (is.null(path_value) || path_value == "") {
    return("")
  }
  if (grepl("^/", path_value)) {
    return(normalizePath(path_value, mustWork = FALSE))
  }
  normalizePath(file.path(project_root, path_value), mustWork = FALSE)
}

panel_path <- resolve_project_path(Sys.getenv("PANEL_PATH", unset = ""))
out_dir <- resolve_project_path(Sys.getenv("OUT_DIR", unset = ""))
panel_label <- Sys.getenv("PANEL_LABEL", unset = "panel")
outcome_group <- tolower(Sys.getenv("OUTCOME_GROUP", unset = ""))
specification_name <- Sys.getenv(
  "SPECIFICATION_NAME",
  unset = "range100_200"
)
ncloc_spec <- tolower(Sys.getenv("NCLOC_SPEC", unset = "python_snapshot"))
time_mode <- tolower(Sys.getenv("TIME_MODE", unset = "calendar_month"))
parse_exclusion_mode <- tolower(
  Sys.getenv("PARSE_EXCLUSION_MODE", unset = "parse_clean")
)
helper_path <- resolve_project_path(
  Sys.getenv(
    "HELPER_FILE",
    unset = "proc_r/diff_in_diff_borusyak_helpers.R"
  )
)
rmd_source_path <- Sys.getenv(
  "RMD_SOURCE_PATH",
  unset = "proc_r/DiffInDiffBorusyak_reg_fun_count_contrast.Rmd"
)
rmd_sha256 <- Sys.getenv("RMD_SHA256", unset = "")

valid_groups <- c("other_minus_testing")
if (!(outcome_group %in% valid_groups)) {
  stop(
    "OUTCOME_GROUP must be one of: ",
    paste(valid_groups, collapse = ", "),
    ". Got: ", outcome_group
  )
}
if (ncloc_spec != "python_snapshot") {
  stop("run-py-7f11 locks NCLOC_SPEC to python_snapshot.")
}
if (time_mode != "calendar_month") {
  stop("run-py-7f11 locks TIME_MODE to calendar_month.")
}
if (parse_exclusion_mode != "parse_clean") {
  stop("run-py-7f11 locks PARSE_EXCLUSION_MODE to parse_clean.")
}
if (panel_path == "") {
  stop("PANEL_PATH environment variable is required.")
}
if (out_dir == "") {
  stop("OUT_DIR environment variable is required.")
}

dir.create(out_dir, recursive = TRUE, showWarnings = FALSE)
```

# Purpose

This notebook applies the locked `run-py-7f09` Borusyak imputation DiD
specification to the `run-py-7f10` row-level count contrast:

`AGC-like non-testing regular-function bodies - AGC-like testing bodies`.

The subtraction is performed within each identical repository-month before
estimation. The resulting standard error therefore reflects the covariance of
the two component outcomes. The contrast is a raw count difference, can be
negative, and is not transformed with `log1p`.

The null hypothesis is `ATT_other_functions - ATT_testing = 0`. A positive and
statistically significant ATT means that Cursor adoption increased AGC-like
unique-body counts more in non-testing regular functions than in testing-related
regular functions. It does not compare AGC usage rates or propensities.

The requested event-study window is -6 through +6. The `didimputation`
estimator normalizes month -1 to zero as the omitted reference period, so it
returns 12 estimated dynamic effects: -6 through -2 and 0 through +6. The
reference period is documented but is not fabricated as an estimated row.

# Load Packages and Helper Functions

```{r load-packages}
library(data.table)
library(dplyr)
library(ggplot2)
library(didimputation)

if (!file.exists(helper_path)) {
  stop("Helper file not found: ", helper_path)
}
source(helper_path)
```

# Utility Functions

```{r utility-functions}
normalize_yyyymm <- function(x) {
  x <- as.character(x)
  x[x %in% c("", "NA", "NaN", "NULL", "None")] <- NA_character_
  x <- gsub("-", "", x)
  suppressWarnings(as.integer(x))
}

yyyymm_to_month_id <- function(x) {
  x <- as.integer(x)
  year <- x %/% 100L
  month <- x %% 100L
  out <- year * 12L + month
  out[is.na(x) | month < 1L | month > 12L] <- NA_integer_
  out
}

require_columns <- function(data, required, label) {
  missing <- setdiff(required, names(data))
  if (length(missing) > 0) {
    stop(label, " missing required columns: ", paste(missing, collapse = ", "))
  }
}

write_error_table <- function(errors, stage, output_path) {
  if (length(errors) == 0) {
    fwrite(
      data.frame(
        stage = character(),
        outcome_group = character(),
        outcome = character(),
        error = character()
      ),
      output_path
    )
    return(invisible(NULL))
  }

  fwrite(
    data.frame(
      stage = stage,
      outcome_group = outcome_group,
      outcome = names(errors),
      error = unlist(errors),
      row.names = NULL,
      stringsAsFactors = FALSE
    ),
    output_path
  )
}

add_normal_p_value <- function(data) {
  data$p_value <- ifelse(
    !is.na(data$estimate) & !is.na(data$std_error) & data$std_error > 0,
    2 * pnorm(abs(data$estimate / data$std_error), lower.tail = FALSE),
    NA_real_
  )
  data
}
```

# Outcome Configuration

```{r outcome-configuration}
group_config <- data.frame(
  outcome_group = "other_minus_testing",
  outcome_label = "AGC-Like Non-Testing Minus Testing Unique Bodies",
  expected_total = 995L,
  expected_negative_rows = 112L,
  expected_zero_rows = 1064L,
  expected_positive_rows = 345L,
  stringsAsFactors = FALSE
)

selected_config <- group_config[group_config$outcome_group == outcome_group, ]
outcome_label <- selected_config$outcome_label[[1]]
expected_total <- selected_config$expected_total[[1]]
expected_negative_rows <- selected_config$expected_negative_rows[[1]]
expected_positive_rows <- selected_config$expected_positive_rows[[1]]
expected_zero_rows <- selected_config$expected_zero_rows[[1]]

testing_count_var <- "npr_agc_testing_regular_module_function_unique_bodies"
other_count_var <- "npr_agc_other_regular_module_function_unique_bodies"
all_count_var <- "npr_agc_all_regular_module_function_unique_bodies"
outcome_var <-
  "npr_agc_other_minus_testing_regular_module_function_unique_bodies"
positive_var <- "has_positive_npr_agc_other_minus_testing_contrast"
negative_var <- "has_negative_npr_agc_other_minus_testing_contrast"
zero_var <- "zero_npr_agc_other_minus_testing_contrast"
output_prefix <- "borusyak_reg_fun_count_contrast_other_minus_testing"
```

# Load and Validate Input Panel

```{r load-panel}
cat("Project root:", project_root, "\n")
cat("Panel path:", panel_path, "\n")
cat("Panel label:", panel_label, "\n")
cat("Outcome group:", outcome_group, "\n")
cat("Outcome label:", outcome_label, "\n")
cat("Specification:", specification_name, "\n")
cat("Output directory:", out_dir, "\n")

if (!file.exists(panel_path)) {
  stop("Panel file not found: ", panel_path)
}

panel_raw <- fread(panel_path)

covariates <- c(
  "log1p_age",
  "ncloc_python_snapshot",
  "log1p_contributors",
  "log1p_stars",
  "log1p_issues"
)
readiness_column <-
  "analysis_ready_regular_module_function_agc_unique_body_python_snapshot_ncloc"

base_required <- c(
  "dataset_source",
  "repo_name",
  "time",
  "event",
  "time_to_event",
  testing_count_var,
  other_count_var,
  all_count_var,
  outcome_var,
  positive_var,
  negative_var,
  zero_var,
  covariates,
  readiness_column,
  "has_parse_exclusion",
  "npr_detection_complete",
  "npr_specification",
  "treatment_group",
  "regular_function_scope",
  "agc_count_unit",
  "agc_outcome_scale",
  "regular_function_outcome_schema_version",
  "regular_function_taxonomy_status",
  "regular_function_taxonomy_version",
  "regular_function_contrast_id",
  "regular_function_contrast_scale",
  "regular_function_contrast_unit",
  "regular_function_contrast_schema_version",
  "regular_function_contrast_covariance_handling"
)
require_columns(panel_raw, base_required, "Input panel")

if (nrow(panel_raw) != 1521L) {
  stop("Expected 1,521 input rows; got ", nrow(panel_raw), ".")
}
if (uniqueN(panel_raw$repo_name) != 218L) {
  stop("Expected 218 repositories; got ", uniqueN(panel_raw$repo_name), ".")
}
if (anyDuplicated(panel_raw[, .(dataset_source, repo_name, time)]) > 0) {
  stop("Input panel has duplicate dataset_source/repo_name/time keys.")
}
if (!all(panel_raw$dataset_source %in% c("control", "treatment"))) {
  stop("dataset_source contains unexpected values.")
}
if (!all(as.character(panel_raw$regular_function_contrast_id) == outcome_group)) {
  stop("regular_function_contrast_id does not match OUTCOME_GROUP.")
}
if (!all(
  as.character(panel_raw$regular_function_outcome_schema_version) ==
    "run-py-7f08-v1"
)) {
  stop("Unexpected run-py-7f08 outcome schema version.")
}
if (!all(
  as.character(panel_raw$regular_function_taxonomy_status) == "FROZEN_BINARY"
)) {
  stop("Binary taxonomy is not uniformly frozen.")
}
if (!all(
  as.character(panel_raw$regular_function_taxonomy_version) ==
    "testing-vs-other-functions-v1"
)) {
  stop("Unexpected binary taxonomy version.")
}
if (!all(as.character(panel_raw$npr_specification) == specification_name)) {
  stop("npr_specification does not match the requested specification.")
}
if (!all(as.character(panel_raw$regular_function_scope) == "module_function")) {
  stop("Regular-function scope is not uniformly module_function.")
}
if (!all(as.character(panel_raw$agc_outcome_scale) == "raw_count")) {
  stop("Upstream component scale is not uniformly raw_count.")
}
if (!all(
  as.character(panel_raw$agc_count_unit) ==
    "distinct_function_body_sha256_per_repository_month"
)) {
  stop("Unexpected AGC count unit.")
}
if (!all(
  as.character(panel_raw$regular_function_contrast_schema_version) ==
    "run-py-7f10-v1"
)) {
  stop("Unexpected run-py-7f10 contrast schema version.")
}
if (!all(
  as.character(panel_raw$regular_function_contrast_scale) ==
    "raw_count_difference"
)) {
  stop("Contrast scale is not uniformly raw_count_difference.")
}
if (!all(
  as.character(panel_raw$regular_function_contrast_unit) ==
    "distinct_function_body_count_difference_per_repository_month"
)) {
  stop("Unexpected contrast outcome unit.")
}
if (!all(
  as.character(panel_raw$treatment_group) ==
    as.character(panel_raw$dataset_source)
)) {
  stop("treatment_group does not match dataset_source.")
}

detection_complete_true <- panel_raw$npr_detection_complete %in%
  c(TRUE, 1L, 1.0, "True", "TRUE", "true", "1", "1.0")
if (!all(detection_complete_true)) {
  stop("npr_detection_complete is not uniformly true.")
}

outcome_values <- suppressWarnings(as.numeric(panel_raw[[outcome_var]]))
outcome_missing_rows <- sum(is.na(outcome_values))
outcome_negative_rows <- sum(outcome_values < 0, na.rm = TRUE)
outcome_noninteger_rows <- sum(
  !is.na(outcome_values) & abs(outcome_values - round(outcome_values)) > 1e-12
)
positive_flag_mismatch_rows <- sum(
  as.integer(panel_raw[[positive_var]]) != as.integer(outcome_values > 0),
  na.rm = TRUE
)
negative_flag_mismatch_rows <- sum(
  as.integer(panel_raw[[negative_var]]) != as.integer(outcome_values < 0),
  na.rm = TRUE
)
zero_flag_mismatch_rows <- sum(
  as.integer(panel_raw[[zero_var]]) != as.integer(outcome_values == 0),
  na.rm = TRUE
)
component_arithmetic_mismatch_rows <- sum(
  as.numeric(panel_raw[[other_count_var]]) -
    as.numeric(panel_raw[[testing_count_var]]) != outcome_values,
  na.rm = TRUE
)
aggregate_reconciliation_mismatch_rows <- sum(
  as.numeric(panel_raw[[testing_count_var]]) +
    as.numeric(panel_raw[[other_count_var]]) !=
    as.numeric(panel_raw[[all_count_var]]),
  na.rm = TRUE
)

if (
  outcome_missing_rows > 0 ||
    outcome_noninteger_rows > 0 ||
    positive_flag_mismatch_rows > 0 ||
    negative_flag_mismatch_rows > 0 ||
    zero_flag_mismatch_rows > 0 ||
    component_arithmetic_mismatch_rows > 0 ||
    aggregate_reconciliation_mismatch_rows > 0
) {
  stop("Raw-count-difference contrast contract failed.")
}

observed_total <- sum(outcome_values)
observed_negative_rows <- sum(outcome_values < 0)
observed_positive_rows <- sum(outcome_values > 0)
observed_zero_rows <- sum(outcome_values == 0)

if (observed_total != expected_total) {
  stop("Outcome total mismatch: ", observed_total, " != ", expected_total)
}
if (observed_positive_rows != expected_positive_rows) {
  stop(
    "Positive-row mismatch: ",
    observed_positive_rows, " != ", expected_positive_rows
  )
}
if (observed_negative_rows != expected_negative_rows) {
  stop(
    "Negative-row mismatch: ",
    observed_negative_rows, " != ", expected_negative_rows
  )
}
if (observed_zero_rows != expected_zero_rows) {
  stop("Zero-row mismatch: ", observed_zero_rows, " != ", expected_zero_rows)
}

cat("Loaded rows:", nrow(panel_raw), "\n")
cat("Loaded repositories:", uniqueN(panel_raw$repo_name), "\n")
cat("Negative-outcome rows:", observed_negative_rows, "\n")
cat("Positive-outcome rows:", observed_positive_rows, "\n")
cat("Zero-outcome rows:", observed_zero_rows, "\n")
cat("Total raw count difference:", observed_total, "\n")
```

# Configure Locked Borusyak Model

```{r configure-model}
panel_data <- copy(panel_raw)
panel_data <- panel_data[get(readiness_column) == 1]
rows_after_readiness_filter <- nrow(panel_data)

panel_data <- panel_data[has_parse_exclusion == 0]
rows_after_parse_filter <- nrow(panel_data)

model_required <- c(outcome_var, covariates)
implicit_missing_rows <- sum(!complete.cases(panel_data[, ..model_required]))
if (implicit_missing_rows > 0) {
  stop(
    "Analysis-ready flag allowed rows with missing model variables: ",
    implicit_missing_rows
  )
}

panel_data[, time_yyyymm := normalize_yyyymm(time)]
event_yyyymm_raw <- normalize_yyyymm(panel_data$event)
event_yyyymm_raw[is.na(event_yyyymm_raw)] <- 0L
panel_data[, event_yyyymm := event_yyyymm_raw]

event_membership_mismatch_rows <- panel_data[
  ,
  sum((dataset_source == "treatment") != (event_yyyymm > 0L))
]
if (event_membership_mismatch_rows > 0) {
  stop("Event encoding disagrees with dataset_source.")
}

# Preserve the cohort restriction from the original and run-py-7f models.
panel_data <- panel_data[
  event_yyyymm == 0L |
    (event_yyyymm > 202407L & event_yyyymm <= 202503L)
]
rows_after_cohort_filter <- nrow(panel_data)

panel_data[, repo_name_str := as.character(repo_name)]
panel_data[, repo_id := as.integer(factor(repo_name_str))]
panel_data[, time_id := yyyymm_to_month_id(time_yyyymm)]
panel_data[, event_id := fifelse(
  event_yyyymm == 0L,
  0L,
  yyyymm_to_month_id(event_yyyymm)
)]
panel_data <- panel_data[!is.na(time_id)]
panel_data <- panel_data[event_id == 0L | !is.na(event_id)]
panel_data[, treated := as.integer(event_id > 0L)]

first_stage_rhs <- paste(covariates, collapse = " + ")
first_stage_formula <- as.formula(
  paste0("~ ", first_stage_rhs, " | repo_id + time_id")
)

cat("Outcome:", outcome_var, "\n")
cat("Outcome group:", outcome_group, "\n")
cat("Outcome scale: raw count difference (other minus testing)\n")
cat("Negative outcome values: allowed\n")
cat("Rows used by models:", nrow(panel_data), "\n")
cat("Repositories used:", uniqueN(panel_data$repo_id), "\n")
cat("Time encoding: sequential calendar-month id\n")
cat("First-stage formula:\n")
print(first_stage_formula)
cat("Inference clustering: repository id (didimputation idname default)\n")
```

# Panel Checks and Input Summary

```{r panel-checks}
panel_checks <- data.frame(
  check = c(
    "schema_version",
    "panel_label",
    "outcome_group",
    "specification_name",
    "ncloc_specification",
    "time_mode",
    "parse_exclusion_mode",
    "input_rows",
    "input_repositories",
    "rows_after_readiness_filter",
    "rows_after_parse_filter",
    "rows_after_cohort_filter",
    "rows_used_by_models",
    "repositories_used_by_models",
    "treated_repositories",
    "control_repositories",
    "negative_outcome_rows_in_model_sample",
    "zero_outcome_rows_in_model_sample",
    "positive_outcome_rows_in_model_sample",
    "total_outcome_difference_in_model_sample",
    "parse_exclusion_rows_in_model_sample",
    "outcome_missing_rows",
    "outcome_negative_rows",
    "outcome_noninteger_rows",
    "positive_flag_arithmetic_mismatch_rows",
    "negative_flag_arithmetic_mismatch_rows",
    "zero_flag_arithmetic_mismatch_rows",
    "component_arithmetic_mismatch_rows",
    "aggregate_reconciliation_mismatch_rows",
    "event_membership_mismatch_rows",
    "covariate_missing_sum",
    "first_stage_covariates",
    "fixed_effects",
    "cluster_variable"
  ),
  value = c(
    "run-py-7f11-v1",
    panel_label,
    outcome_group,
    specification_name,
    ncloc_spec,
    time_mode,
    parse_exclusion_mode,
    nrow(panel_raw),
    uniqueN(panel_raw$repo_name),
    rows_after_readiness_filter,
    rows_after_parse_filter,
    rows_after_cohort_filter,
    nrow(panel_data),
    uniqueN(panel_data$repo_id),
    uniqueN(panel_data[treated == 1, repo_id]),
    uniqueN(panel_data[treated == 0, repo_id]),
    sum(panel_data[[outcome_var]] < 0),
    sum(panel_data[[outcome_var]] == 0),
    sum(panel_data[[outcome_var]] > 0),
    sum(panel_data[[outcome_var]]),
    sum(panel_data$has_parse_exclusion == 1),
    outcome_missing_rows,
    outcome_negative_rows,
    outcome_noninteger_rows,
    positive_flag_mismatch_rows,
    negative_flag_mismatch_rows,
    zero_flag_mismatch_rows,
    component_arithmetic_mismatch_rows,
    aggregate_reconciliation_mismatch_rows,
    event_membership_mismatch_rows,
    sum(is.na(panel_data[, ..covariates])),
    first_stage_rhs,
    "repo_id + time_id",
    "repo_id (idname default)"
  ),
  stringsAsFactors = FALSE
)

print(panel_checks)
fwrite(
  panel_checks,
  file.path(out_dir, paste0(output_prefix, "_panel_checks.csv"))
)

input_summary <- panel_data[, .(
  rows = .N,
  repositories = uniqueN(repo_id),
  testing_unique_body_total = sum(get(testing_count_var)),
  other_unique_body_total = sum(get(other_count_var)),
  all_unique_body_total = sum(get(all_count_var)),
  total_count_difference = sum(get(outcome_var)),
  mean_count_difference = mean(get(outcome_var)),
  median_count_difference = as.numeric(median(get(outcome_var))),
  minimum_count_difference = min(get(outcome_var)),
  maximum_count_difference = max(get(outcome_var)),
  negative_month_share = mean(get(outcome_var) < 0),
  positive_month_share = mean(get(outcome_var) > 0),
  zero_month_share = mean(get(outcome_var) == 0),
  mean_python_snapshot_ncloc = mean(ncloc_python_snapshot)
), by = dataset_source]
input_summary$outcome_group <- outcome_group
input_summary$outcome_label <- outcome_label

print(input_summary)
fwrite(
  input_summary,
  file.path(out_dir, paste0(output_prefix, "_input_summary.csv"))
)
```

# Static ATT

```{r static-effect}
static_errors <- list()
static_result <- tryCatch(
  run_borusyak_static(
    data = panel_data,
    outcome_var = outcome_var,
    first_stage_formula = first_stage_formula,
    idname = "repo_id",
    tname = "time_id",
    gname = "event_id"
  ),
  error = function(e) {
    static_errors[[outcome_var]] <<- conditionMessage(e)
    NULL
  }
)

static_df <- extract_static_result(static_result, outcome_var)
static_df <- add_normal_p_value(static_df)
static_df$outcome_group <- outcome_group
static_df$outcome_label <- outcome_label
static_df$outcome_scale <- "raw_count_difference"
static_df$outcome_unit <-
  "non-testing minus testing distinct bodies per repository-month"
static_df$panel <- panel_label
static_df$specification <- specification_name
static_df$ncloc_spec <- ncloc_spec
static_df$time_mode <- time_mode
static_df$parse_exclusion_mode <- parse_exclusion_mode
static_df$cluster_variable <- "repo_id"
static_df$confidence_level <- 0.95

print(static_df)
fwrite(
  static_df,
  file.path(out_dir, paste0(output_prefix, "_static_effects.csv"))
)
write_error_table(
  static_errors,
  "static",
  file.path(out_dir, paste0(output_prefix, "_static_errors.csv"))
)
```

# Dynamic Effects

```{r dynamic-effects}
dynamic_errors <- list()
dynamic_result <- tryCatch(
  run_borusyak_dynamic(
    data = panel_data,
    outcome_var = outcome_var,
    first_stage_formula = first_stage_formula,
    horizon = -6:6,
    pretrends = -6:-2,
    idname = "repo_id",
    tname = "time_id",
    gname = "event_id"
  ),
  error = function(e) {
    dynamic_errors[[outcome_var]] <<- conditionMessage(e)
    NULL
  }
)

dynamic_df <- extract_dynamic_result(
  dynamic_result,
  outcome = outcome_var,
  outcome_label = outcome_label,
  min_horizon = -6,
  max_horizon = 6
)
dynamic_df <- add_normal_p_value(dynamic_df)

if (nrow(dynamic_df) > 0) {
  dynamic_df$outcome_group <- outcome_group
  dynamic_df$outcome_scale <- "raw_count_difference"
  dynamic_df$outcome_unit <-
    "non-testing minus testing distinct bodies per repository-month"
  dynamic_df$panel <- panel_label
  dynamic_df$specification <- specification_name
  dynamic_df$ncloc_spec <- ncloc_spec
  dynamic_df$time_mode <- time_mode
  dynamic_df$parse_exclusion_mode <- parse_exclusion_mode
  dynamic_df$cluster_variable <- "repo_id"
  dynamic_df$confidence_level <- 0.95
}

print(dynamic_df)
fwrite(
  dynamic_df,
  file.path(out_dir, paste0(output_prefix, "_dynamic_effects.csv"))
)
write_error_table(
  dynamic_errors,
  "dynamic",
  file.path(out_dir, paste0(output_prefix, "_dynamic_errors.csv"))
)
```

# Uncertainty Results

```{r uncertainty-results}
static_uncertainty <- data.frame(
  outcome_group = outcome_group,
  outcome_label = outcome_label,
  effect_type = "static_att",
  event_time = NA_real_,
  estimate = static_df$estimate,
  std_error = static_df$std_error,
  conf_low = static_df$conf_low,
  conf_high = static_df$conf_high,
  p_value = static_df$p_value,
  significant_05 = !is.na(static_df$conf_low) &
    !is.na(static_df$conf_high) &
    (static_df$conf_low > 0 | static_df$conf_high < 0),
  confidence_level = 0.95,
  cluster_variable = "repo_id",
  inference_method = paste(
    "didimputation analytic standard errors;",
    "repository clustering through idname default"
  ),
  stringsAsFactors = FALSE
)

dynamic_uncertainty <- data.frame(
  outcome_group = outcome_group,
  outcome_label = outcome_label,
  effect_type = "dynamic_event_time",
  event_time = dynamic_df$time,
  estimate = dynamic_df$estimate,
  std_error = dynamic_df$std_error,
  conf_low = dynamic_df$conf_low,
  conf_high = dynamic_df$conf_high,
  p_value = dynamic_df$p_value,
  significant_05 = dynamic_df$significant,
  confidence_level = 0.95,
  cluster_variable = "repo_id",
  inference_method = paste(
    "didimputation analytic standard errors;",
    "repository clustering through idname default"
  ),
  stringsAsFactors = FALSE
)

uncertainty_df <- bind_rows(static_uncertainty, dynamic_uncertainty)
print(uncertainty_df)
fwrite(
  uncertainty_df,
  file.path(out_dir, paste0(output_prefix, "_uncertainty.csv"))
)
```

# Pre-Trend Results

```{r pretrend-results}
pretrend_df <- dynamic_df[dynamic_df$time %in% -6:-2, , drop = FALSE]
pretrend_period_count <- nrow(pretrend_df)

if (pretrend_period_count > 0) {
  pretrend_df$p_value_unadjusted <- pretrend_df$p_value
  pretrend_df$p_value_bonferroni <- pmin(
    1,
    pretrend_period_count * pretrend_df$p_value_unadjusted
  )
  pretrend_df$significant_unadjusted_05 <-
    !is.na(pretrend_df$p_value_unadjusted) &
    pretrend_df$p_value_unadjusted < 0.05
  pretrend_df$significant_bonferroni_05 <-
    !is.na(pretrend_df$p_value_bonferroni) &
    pretrend_df$p_value_bonferroni < 0.05
}

minimum_pretrend_p <- if (pretrend_period_count > 0) {
  min(pretrend_df$p_value_unadjusted, na.rm = TRUE)
} else {
  NA_real_
}
global_bonferroni_p <- if (!is.na(minimum_pretrend_p)) {
  min(1, pretrend_period_count * minimum_pretrend_p)
} else {
  NA_real_
}

pretrend_conclusion <- if (is.na(global_bonferroni_p)) {
  "UNAVAILABLE"
} else if (global_bonferroni_p < 0.05) {
  "EVIDENCE_OF_NONZERO_PRETREND"
} else {
  "NO_EVIDENCE_OF_NONZERO_PRETREND"
}

pretrend_summary <- data.frame(
  outcome_group = outcome_group,
  outcome_label = outcome_label,
  expected_pretrend_periods = 5L,
  available_pretrend_periods = pretrend_period_count,
  significant_unadjusted_periods = if (pretrend_period_count > 0) {
    sum(pretrend_df$significant_unadjusted_05)
  } else {
    NA_integer_
  },
  significant_bonferroni_periods = if (pretrend_period_count > 0) {
    sum(pretrend_df$significant_bonferroni_05)
  } else {
    NA_integer_
  },
  minimum_unadjusted_p_value = minimum_pretrend_p,
  global_bonferroni_p_value = global_bonferroni_p,
  family_wise_alpha = 0.05,
  pretrend_conclusion = pretrend_conclusion,
  diagnostic_method = paste(
    "Five marginal lead tests (-6:-2) with a conservative",
    "Bonferroni family-wise diagnostic"
  ),
  interpretation_note = paste(
    "Failure to reject does not prove parallel trends;",
    "it means these five lead estimates do not provide evidence against them."
  ),
  stringsAsFactors = FALSE
)

print(pretrend_df)
print(pretrend_summary)
fwrite(
  pretrend_df,
  file.path(out_dir, paste0(output_prefix, "_pretrend_effects.csv"))
)
fwrite(
  pretrend_summary,
  file.path(out_dir, paste0(output_prefix, "_pretrend_summary.csv"))
)
```

# Dynamic Plot

```{r dynamic-plot, fig.width=10, fig.height=4.5}
if (nrow(dynamic_df) > 0) {
  plot_object <- ggplot(dynamic_df, aes(x = time, y = estimate)) +
    geom_errorbar(
      data = subset(dynamic_df, significant %in% TRUE),
      aes(ymin = conf_low, ymax = conf_high),
      width = 0.4,
      linetype = "solid"
    ) +
    geom_errorbar(
      data = subset(dynamic_df, !(significant %in% TRUE)),
      aes(ymin = conf_low, ymax = conf_high),
      width = 0.4,
      linetype = "dotted"
    ) +
    geom_point(
      data = subset(dynamic_df, significant %in% TRUE),
      shape = 19,
      size = 1.8
    ) +
    geom_point(
      data = subset(dynamic_df, !(significant %in% TRUE)),
      shape = 21,
      fill = "transparent",
      size = 1.8
    ) +
    geom_hline(yintercept = 0, linetype = "dashed") +
    geom_vline(xintercept = -0.5, linetype = "dashed") +
    scale_x_continuous(breaks = -6:6) +
    coord_cartesian(xlim = c(-6.5, 6.5)) +
    labs(
      title = paste("Borusyak DiD:", outcome_label),
      subtitle = paste(
        "Raw count difference | Python-snapshot NCLOC | Calendar month |",
        "Repository-clustered 95% CI"
      ),
      x = "Months Relative to Cursor Adoption",
      y = "ATT: Non-Testing Minus Testing Bodies per Repository-Month",
      caption = paste(
        "Filled dots: 95% CI excludes 0.",
        "Month -1 is the omitted reference period normalized to zero.",
        "Negative, zero, and positive contrast months are retained."
      )
    ) +
    theme_minimal() +
    theme(
      panel.grid.minor = element_blank(),
      plot.caption = element_text(hjust = 0.5, size = 8)
    )

  print(plot_object)
  ggsave(
    filename = file.path(
      out_dir,
      "dynamic_effects_borusyak_reg_fun_count_contrast_other_minus_testing.pdf"
    ),
    plot = plot_object,
    width = 10,
    height = 4.5
  )
}
```

# Final Model Validation

```{r final-model-validation}
static_model_error_count <- length(static_errors)
dynamic_model_error_count <- length(dynamic_errors)
expected_dynamic_times <- c(-6:-2, 0:6)

static_effect_complete <- nrow(static_df) == 1 &&
  !is.na(static_df$estimate[1]) &&
  !is.na(static_df$std_error[1]) &&
  !is.na(static_df$conf_low[1]) &&
  !is.na(static_df$conf_high[1]) &&
  !is.na(static_df$p_value[1])
dynamic_effects_complete <- nrow(dynamic_df) == 12L &&
  identical(sort(as.integer(dynamic_df$time)), expected_dynamic_times) &&
  all(complete.cases(
    dynamic_df[, c("estimate", "std_error", "conf_low", "conf_high", "p_value")]
  ))
pretrend_effects_complete <- nrow(pretrend_df) == 5L &&
  identical(sort(as.integer(pretrend_df$time)), -6:-2)
uncertainty_rows_complete <- nrow(uncertainty_df) == 13L

final_model_validation <- data.frame(
  check = c(
    "schema_version",
    "outcome_group",
    "static_model_error_count",
    "dynamic_model_error_count",
    "static_effect_complete",
    "dynamic_effects_complete_12_estimated_periods",
    "pretrend_effects_complete_5_periods",
    "uncertainty_rows_complete_13_rows",
    "rows_used_by_models",
    "repositories_used_by_models",
    "covariate_missing_sum",
    "status"
  ),
  value = c(
    "run-py-7f11-v1",
    outcome_group,
    static_model_error_count,
    dynamic_model_error_count,
    static_effect_complete,
    dynamic_effects_complete,
    pretrend_effects_complete,
    uncertainty_rows_complete,
    nrow(panel_data),
    uniqueN(panel_data$repo_id),
    sum(is.na(panel_data[, ..covariates])),
    if (
      static_model_error_count == 0 &&
        dynamic_model_error_count == 0 &&
        static_effect_complete &&
        dynamic_effects_complete &&
        pretrend_effects_complete &&
        uncertainty_rows_complete
    ) "PASS" else "FAIL"
  ),
  stringsAsFactors = FALSE
)

print(final_model_validation)
fwrite(
  final_model_validation,
  file.path(out_dir, paste0(output_prefix, "_final_model_validation.csv"))
)

if (static_model_error_count > 0 || dynamic_model_error_count > 0) {
  stop("One or more Borusyak models failed.")
}
if (!static_effect_complete) {
  stop("Static ATT or its uncertainty fields are incomplete.")
}
if (!dynamic_effects_complete) {
  stop(
    "Dynamic effects do not contain all 12 estimated periods ",
    "(-6:-2 and 0:6); month -1 is the omitted reference period."
  )
}
if (!pretrend_effects_complete) {
  stop("Pre-trend results do not contain all five leads from -6 through -2.")
}
if (!uncertainty_rows_complete) {
  stop("Uncertainty table does not contain one static plus 12 dynamic rows.")
}
```

# Metadata

```{r metadata}
metadata <- data.frame(
  key = c(
    "schema_version",
    "script",
    "script_sha256",
    "helper_file",
    "panel_label",
    "panel_path",
    "out_dir",
    "outcome_group",
    "outcome_label",
    "outcome",
    "outcome_scale",
    "outcome_unit",
    "zero_inclusive",
    "negative_values_allowed",
    "contrast_definition",
    "null_hypothesis",
    "covariance_handling",
    "specification_name",
    "taxonomy_status",
    "taxonomy_version",
    "ncloc_specification",
    "time_mode",
    "parse_exclusion_mode",
    "covariates",
    "covariate_scaling",
    "fixed_effects",
    "first_stage_formula",
    "cohort_restriction",
    "rows_used_by_models",
    "repositories_used_by_models",
    "estimator",
    "time_encoding",
    "horizon",
    "reference_period",
    "estimated_dynamic_periods",
    "pretrends",
    "cluster_variable",
    "uncertainty_method",
    "confidence_level",
    "pretrend_diagnostic",
    "global_bonferroni_p_value",
    "pretrend_conclusion",
    "interpretation_note"
  ),
  value = c(
    "run-py-7f11-v1",
    rmd_source_path,
    rmd_sha256,
    helper_path,
    panel_label,
    panel_path,
    out_dir,
    outcome_group,
    outcome_label,
    outcome_var,
    "raw_count_difference",
    "non-testing minus testing distinct bodies per repository-month",
    "true",
    "true",
    "other_functions count - testing count within repository-month",
    "ATT_other_functions - ATT_testing = 0",
    paste(
      "component outcomes combined within repository-month before estimation;",
      "repository-clustered uncertainty is covariance-aware"
    ),
    specification_name,
    "FROZEN_BINARY",
    "testing-vs-other-functions-v1",
    "python_snapshot",
    "calendar_month",
    "parse_clean",
    first_stage_rhs,
    paste(
      "log1p(age, contributors, stars, issues);",
      "raw ncloc_python_snapshot"
    ),
    "repo_id + time_id",
    paste(deparse(first_stage_formula), collapse = " "),
    "controls plus treatment cohorts 2024-08 through 2025-03",
    nrow(panel_data),
    uniqueN(panel_data$repo_id),
    "Borusyak imputation via didimputation::did_imputation",
    "sequential_calendar_month_id",
    "-6:6",
    "-1 (omitted and normalized to zero; not an estimated coefficient)",
    "-6:-2 and 0:6 (12 estimated periods)",
    "-6:-2",
    "repo_id",
    paste(
      "didimputation analytic standard errors and 95% confidence intervals;",
      "repository clustering through idname default"
    ),
    "0.95",
    "five marginal leads with conservative Bonferroni family-wise diagnostic",
    global_bonferroni_p,
    pretrend_conclusion,
    paste(
      "A positive significant ATT means Cursor adoption increased absolute",
      "AGC-like unique-body counts more in non-testing than testing regular",
      "functions. This count contrast does not compare usage rates."
    )
  ),
  stringsAsFactors = FALSE
)

print(metadata)
fwrite(
  metadata,
  file.path(out_dir, paste0(output_prefix, "_metadata.csv"))
)
```

# Session Info

```{r session-info}
sessionInfo()
```
