---
title: "Borusyak DiD for SonarQube Warning Subcategories"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
params:
  panel_label: "strict_1to3_unbalanced"
  panel_path: "tmp_jsts_test/data/jsts_did_final/panel_event_monthly_matched_final_clean_1to3_only_with_sonarqube_quality_did_input_complete.csv"
  out_dir: "tmp_jsts_test/data/jsts_did_final/quality_did_borusyak_warning_subcategories/strict_1to3_unbalanced"
  helpers_path: "diff_in_diff_borusyak_helpers.R"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = TRUE,
  warning = TRUE,
  error = FALSE
)
```

# Purpose

This report estimates Borusyak imputation-based Difference-in-Differences models for SonarQube static-analysis warning subcategories.

The outcomes are:

- `bugs`
- `vulnerabilities`
- `code_smells`

These decompose the aggregate `static_analysis_warnings` outcome.

# Load Packages

```{r packages}
required_packages <- c(
  "data.table",
  "dplyr",
  "ggplot2",
  "knitr",
  "didimputation"
)

for (pkg in required_packages) {
  if (!requireNamespace(pkg, quietly = TRUE)) {
    stop("Required package is not installed: ", pkg)
  }
}

library(data.table)
library(dplyr)
library(ggplot2)
library(knitr)
library(didimputation)
```

# Parameters

```{r params}
panel_label <- params$panel_label
panel_path <- params$panel_path
out_dir <- params$out_dir
helpers_path_param <- params$helpers_path

dir.create(out_dir, recursive = TRUE, showWarnings = FALSE)

cat("Panel label:", panel_label, "\n")
cat("Panel path:", panel_path, "\n")
cat("Output dir:", out_dir, "\n")
cat("Helpers path parameter:", helpers_path_param, "\n")
```

# Source Shared Borusyak Helpers

```{r source-helpers}
resolve_helpers_path <- function(configured_path) {
  current_input <- tryCatch(knitr::current_input(), error = function(e) NA_character_)

  rmd_dir <- NA_character_
  if (!is.na(current_input) && nzchar(current_input)) {
    rmd_dir <- dirname(normalizePath(current_input, mustWork = FALSE))
  }

  candidates <- unique(c(
    configured_path,
    file.path("proc_r", basename(configured_path)),
    if (!is.na(rmd_dir)) file.path(rmd_dir, basename(configured_path)) else character(0),
    basename(configured_path)
  ))

  existing <- candidates[file.exists(candidates)]

  if (length(existing) == 0) {
    stop(
      "Could not find diff_in_diff_borusyak_helpers.R. Tried: ",
      paste(candidates, collapse = ", ")
    )
  }

  normalizePath(existing[1], mustWork = TRUE)
}

helpers_path <- resolve_helpers_path(helpers_path_param)
cat("Sourcing shared helpers from:", helpers_path, "\n")
source(helpers_path)

required_helper_functions <- c(
  "run_borusyak_static",
  "run_borusyak_dynamic",
  "extract_static_result",
  "extract_dynamic_result"
)

missing_helper_functions <- required_helper_functions[
  !vapply(required_helper_functions, exists, logical(1), mode = "function")
]

if (length(missing_helper_functions) > 0) {
  stop("Missing helper functions: ", paste(missing_helper_functions, collapse = ", "))
}

cat("Shared Borusyak helper reuse: PASS\n")
```

# Local Helper Functions

```{r helper-functions}
normalize_yyyymm <- function(x) {
  x_chr <- as.character(x)
  out <- rep(NA_integer_, length(x_chr))

  is_missing <- is.na(x_chr) | x_chr == "" | x_chr == "NA" | x_chr == "NaN"
  x_chr[is_missing] <- NA_character_

  dash_format <- !is.na(x_chr) & grepl("^\\d{4}-\\d{2}$", x_chr)
  out[dash_format] <- as.integer(gsub("-", "", x_chr[dash_format]))

  numeric_format <- !is.na(x_chr) & grepl("^\\d{6}$", x_chr)
  out[numeric_format] <- as.integer(x_chr[numeric_format])

  out
}

yyyymm_to_month_id <- function(yyyymm) {
  yyyymm <- as.integer(yyyymm)
  year <- yyyymm %/% 100L
  month <- yyyymm %% 100L

  out <- year * 12L + month
  out[is.na(yyyymm) | month < 1L | month > 12L] <- NA_integer_
  out
}

calc_p_value <- function(estimate, std_error) {
  ifelse(
    is.na(estimate) | is.na(std_error) | std_error <= 0,
    NA_real_,
    2 * pnorm(-abs(estimate / std_error))
  )
}

fill_missing_p_values <- function(df) {
  if (!("p_value" %in% names(df))) {
    df$p_value <- NA_real_
  }

  if ("std_error" %in% names(df) && "estimate" %in% names(df)) {
    missing_p <- is.na(df$p_value)
    df$p_value[missing_p] <- calc_p_value(
      df$estimate[missing_p],
      df$std_error[missing_p]
    )
  }

  df
}

alias_metric_column <- function(dt, raw_col, fallback_col) {
  if (!(raw_col %in% names(dt)) && fallback_col %in% names(dt)) {
    dt[, (raw_col) := get(fallback_col)]
  }
  invisible(dt)
}
```

# Load Panel

```{r load-panel}
if (!file.exists(panel_path)) {
  stop("Panel file not found: ", panel_path)
}

panel_raw <- fread(panel_path)

alias_metric_column(panel_raw, "bugs_raw", "bugs")
alias_metric_column(panel_raw, "vulnerabilities_raw", "vulnerabilities")
alias_metric_column(panel_raw, "code_smells_raw", "code_smells")
alias_metric_column(panel_raw, "ncloc_raw", "ncloc")

required_cols <- c(
  "repo_name",
  "time",
  "event",
  "dataset_source",
  "post_event",
  "contributors",
  "log_ncloc",
  "bugs_raw",
  "vulnerabilities_raw",
  "code_smells_raw"
)

missing_cols <- setdiff(required_cols, names(panel_raw))

if (length(missing_cols) > 0) {
  stop("Missing required columns: ", paste(missing_cols, collapse = ", "))
}

cat("Rows:", nrow(panel_raw), "\n")
cat("Repos:", uniqueN(panel_raw$repo_name), "\n")
cat("Columns:", ncol(panel_raw), "\n")
cat("Months:", min(panel_raw$time, na.rm = TRUE), "to", max(panel_raw$time, na.rm = TRUE), "\n")
```

# Raw Panel Sanity Checks

```{r raw-panel-checks}
raw_panel_checks <- data.frame(
  check = c(
    "panel_label",
    "rows",
    "repos",
    "treatment_rows",
    "control_rows",
    "treated_repos",
    "control_repos",
    "bugs_raw_nonmissing",
    "vulnerabilities_raw_nonmissing",
    "code_smells_raw_nonmissing",
    "duplicate_repo_time_source_rows"
  ),
  value = c(
    panel_label,
    nrow(panel_raw),
    uniqueN(panel_raw$repo_name),
    sum(panel_raw$dataset_source == "treatment", na.rm = TRUE),
    sum(panel_raw$dataset_source == "control", na.rm = TRUE),
    uniqueN(panel_raw[dataset_source == "treatment"]$repo_name),
    uniqueN(panel_raw[dataset_source == "control"]$repo_name),
    sum(!is.na(panel_raw$bugs_raw)),
    sum(!is.na(panel_raw$vulnerabilities_raw)),
    sum(!is.na(panel_raw$code_smells_raw)),
    sum(duplicated(panel_raw[, .(repo_name, time, dataset_source)]))
  )
)

print(raw_panel_checks)

fwrite(
  raw_panel_checks,
  file.path(out_dir, "borusyak_warning_subcategories_panel_checks_pre_filter.csv")
)
```

# Warning Composition

```{r warning-composition}
warning_cols <- c("bugs_raw", "vulnerabilities_raw", "code_smells_raw")

composition_overall_wide <- panel_raw[, lapply(.SD, sum, na.rm = TRUE), .SDcols = warning_cols]
composition_overall <- data.table::melt(
  composition_overall_wide,
  measure.vars = warning_cols,
  variable.name = "subcategory",
  value.name = "count"
)
composition_overall[, dataset_source := "overall"]
composition_overall[, share_pct := count / sum(count) * 100]

composition_by_source_wide <- panel_raw[, lapply(.SD, sum, na.rm = TRUE), by = dataset_source, .SDcols = warning_cols]
composition_by_source <- data.table::melt(
  composition_by_source_wide,
  id.vars = "dataset_source",
  measure.vars = warning_cols,
  variable.name = "subcategory",
  value.name = "count"
)
composition_by_source[, share_pct := count / sum(count), by = dataset_source]
composition_by_source[, share_pct := share_pct * 100]

composition <- rbindlist(
  list(
    composition_overall[, .(dataset_source, subcategory, count, share_pct)],
    composition_by_source[, .(dataset_source, subcategory, count, share_pct)]
  ),
  use.names = TRUE
)

composition[, panel := panel_label]

print(composition)

fwrite(
  composition,
  file.path(out_dir, "borusyak_warning_subcategories_composition.csv")
)
```

# Prepare Data for Borusyak Estimator

```{r prepare-data}
panel_data <- copy(panel_raw)

panel_data[, time_yyyymm := normalize_yyyymm(time)]

event_yyyymm_raw <- normalize_yyyymm(panel_data$event)
event_yyyymm_raw[is.na(event_yyyymm_raw)] <- 0L
panel_data[, event_yyyymm := event_yyyymm_raw]

# Safety rule:
# Controls are never-treated in the Borusyak estimator.
# Even if a control row carries a pseudo-event month for matching provenance,
# it should not be treated as an adoption event.
panel_data[, dataset_source := as.character(dataset_source)]
panel_data[dataset_source != "treatment", event_yyyymm := 0L]

if ("post_event" %in% names(panel_data)) {
  panel_data[dataset_source != "treatment", post_event := 0L]
}

# Match the cohort restriction used in the aggregate quality Borusyak pipeline.
# Keep never-treated controls and treatment cohorts with sufficient pre/post support.
panel_data <- panel_data[
  event_yyyymm == 0L |
    (event_yyyymm > 202407L & event_yyyymm <= 202503L)
]

panel_data[, time_id := yyyymm_to_month_id(time_yyyymm)]
panel_data[, event_id := ifelse(event_yyyymm == 0L, 0L, yyyymm_to_month_id(event_yyyymm))]

panel_data <- panel_data[!is.na(time_id)]
panel_data <- panel_data[event_id == 0L | !is.na(event_id)]

panel_data[, repo_name_str := repo_name]
panel_data[, repo_id := as.integer(factor(repo_name_str))]
panel_data[, treated := ifelse(event_id > 0L, 1L, 0L)]
panel_data[, time_to_event_calc := ifelse(treated == 1L, time_id - event_id, NA_integer_)]

metric_cols <- c("bugs_raw", "vulnerabilities_raw", "code_smells_raw")
for (col in metric_cols) {
  panel_data[, (col) := as.numeric(get(col))]
  panel_data[get(col) < 0, (col) := NA_real_]
}

panel_data[, contributors_log := log1p(as.numeric(contributors))]

if (!("log_ncloc" %in% names(panel_data))) {
  if ("ncloc_raw" %in% names(panel_data)) {
    panel_data[, log_ncloc := log1p(as.numeric(ncloc_raw))]
  } else if ("ncloc" %in% names(panel_data)) {
    panel_data[, log_ncloc := log1p(as.numeric(ncloc))]
  } else {
    stop("Cannot create log_ncloc because ncloc_raw/ncloc is missing.")
  }
} else {
  panel_data[, log_ncloc := as.numeric(log_ncloc)]
}

panel_data[, log_bugs := log1p(bugs_raw)]
panel_data[, log_vulnerabilities := log1p(vulnerabilities_raw)]
panel_data[, log_code_smells := log1p(code_smells_raw)]

model_required_cols <- c(
  "log_bugs",
  "log_vulnerabilities",
  "log_code_smells",
  "contributors_log",
  "log_ncloc"
)

panel_data <- panel_data[complete.cases(panel_data[, ..model_required_cols])]

cat("Rows after readiness and cohort filtering:", nrow(panel_data), "\n")
cat("Repos after filtering:", uniqueN(panel_data$repo_id), "\n")
cat("Treated repos:", uniqueN(panel_data[treated == 1, repo_id]), "\n")
cat("Control repos:", uniqueN(panel_data[treated == 0, repo_id]), "\n")
cat("Time id range:", min(panel_data$time_id), "to", max(panel_data$time_id), "\n")
```

# Estimation Input Summary

```{r input-summary}
input_summary <- panel_data[, .(
  rows = .N,
  repos = uniqueN(repo_id),
  mean_bugs_raw = mean(bugs_raw, na.rm = TRUE),
  mean_vulnerabilities_raw = mean(vulnerabilities_raw, na.rm = TRUE),
  mean_code_smells_raw = mean(code_smells_raw, na.rm = TRUE),
  mean_log_bugs = mean(log_bugs, na.rm = TRUE),
  mean_log_vulnerabilities = mean(log_vulnerabilities, na.rm = TRUE),
  mean_log_code_smells = mean(log_code_smells, na.rm = TRUE),
  mean_contributors_log = mean(contributors_log, na.rm = TRUE),
  mean_log_ncloc = mean(log_ncloc, na.rm = TRUE),
  zero_share_bugs = mean(bugs_raw == 0, na.rm = TRUE),
  zero_share_vulnerabilities = mean(vulnerabilities_raw == 0, na.rm = TRUE),
  zero_share_code_smells = mean(code_smells_raw == 0, na.rm = TRUE)
), by = dataset_source]

input_summary[, panel := panel_label]

print(input_summary)

fwrite(
  input_summary,
  file.path(out_dir, "borusyak_warning_subcategories_input_summary.csv")
)

event_time_counts <- panel_data[treated == 1, .N, by = time_to_event_calc][order(time_to_event_calc)]
print(event_time_counts)

fwrite(
  event_time_counts,
  file.path(out_dir, "borusyak_warning_subcategories_event_time_counts.csv")
)
```

# Panel Checks After Filtering

```{r panel-checks-after-filter}
control_post_event_sum <- if ("post_event" %in% names(panel_data)) {
  sum(panel_data[treated == 0]$post_event, na.rm = TRUE)
} else {
  NA_integer_
}

treated_post_rows <- panel_data[treated == 1 & time_id >= event_id, .N]

post_event_mismatch_rows <- if ("post_event" %in% names(panel_data)) {
  expected_post <- ifelse(panel_data$treated == 1L & panel_data$time_id >= panel_data$event_id, 1L, 0L)
  sum(as.integer(panel_data$post_event) != expected_post, na.rm = TRUE)
} else {
  NA_integer_
}

panel_checks_filtered <- data.frame(
  panel = panel_label,
  check = c(
    "rows",
    "repos",
    "treatment_rows",
    "control_rows",
    "treated_repos",
    "control_repos",
    "control_post_event_sum",
    "treated_post_rows",
    "post_event_mismatch_rows",
    "analysis_ready_warning_subcategory_did_rows",
    "bugs_raw_nonmissing",
    "vulnerabilities_raw_nonmissing",
    "code_smells_raw_nonmissing",
    "log_bugs_nonmissing",
    "log_vulnerabilities_nonmissing",
    "log_code_smells_nonmissing",
    "contributors_log_nonmissing",
    "log_ncloc_nonmissing",
    "bugs_zero_rows",
    "vulnerabilities_zero_rows",
    "code_smells_zero_rows",
    "min_time",
    "max_time"
  ),
  value = c(
    nrow(panel_data),
    uniqueN(panel_data$repo_id),
    sum(panel_data$dataset_source == "treatment", na.rm = TRUE),
    sum(panel_data$dataset_source == "control", na.rm = TRUE),
    uniqueN(panel_data[treated == 1]$repo_id),
    uniqueN(panel_data[treated == 0]$repo_id),
    control_post_event_sum,
    treated_post_rows,
    post_event_mismatch_rows,
    nrow(panel_data),
    sum(!is.na(panel_data$bugs_raw)),
    sum(!is.na(panel_data$vulnerabilities_raw)),
    sum(!is.na(panel_data$code_smells_raw)),
    sum(!is.na(panel_data$log_bugs)),
    sum(!is.na(panel_data$log_vulnerabilities)),
    sum(!is.na(panel_data$log_code_smells)),
    sum(!is.na(panel_data$contributors_log)),
    sum(!is.na(panel_data$log_ncloc)),
    sum(panel_data$bugs_raw == 0, na.rm = TRUE),
    sum(panel_data$vulnerabilities_raw == 0, na.rm = TRUE),
    sum(panel_data$code_smells_raw == 0, na.rm = TRUE),
    min(panel_data$time, na.rm = TRUE),
    max(panel_data$time, na.rm = TRUE)
  )
)

print(panel_checks_filtered)

fwrite(
  panel_checks_filtered,
  file.path(out_dir, "borusyak_warning_subcategories_panel_checks.csv")
)
```

# Outcomes and First Stage

```{r outcomes-first-stage}
outcome_vars <- c(
  "log_bugs",
  "log_vulnerabilities",
  "log_code_smells"
)

outcome_names <- c(
  "Bugs",
  "Vulnerabilities",
  "Code Smells"
)

first_stage_formula <- as.formula(
  "~ contributors_log + log_ncloc | repo_id + time_id"
)

cat("Outcomes:\n")
print(data.frame(outcome = outcome_vars, label = outcome_names))

cat("\nFirst-stage formula:\n")
print(first_stage_formula)
```

# Static Borusyak Effects

```{r static-effects}
static_results <- list()
static_errors <- list()

for (var in outcome_vars) {
  cat("Running static Borusyak model for:", var, "\n")

  static_results[[var]] <- tryCatch(
    run_borusyak_static(
      data = as.data.frame(panel_data),
      outcome_var = var,
      first_stage_formula = first_stage_formula,
      idname = "repo_id",
      tname = "time_id",
      gname = "event_id"
    ),
    error = function(e) {
      static_errors[[var]] <<- conditionMessage(e)
      NULL
    }
  )
}

static_df <- dplyr::bind_rows(lapply(outcome_vars, function(v) {
  if (is.null(static_results[[v]])) {
    return(data.frame(
      outcome = v,
      term = "treat",
      estimate = NA_real_,
      std_error = NA_real_,
      conf_low = NA_real_,
      conf_high = NA_real_,
      p_value = NA_real_,
      note = "model failed"
    ))
  }

  extract_static_result(static_results[[v]], v)
}))

static_df <- fill_missing_p_values(static_df)

static_df$outcome_label <- outcome_names[match(static_df$outcome, outcome_vars)]
static_df$panel <- panel_label

static_df$estimate_pct <- (exp(static_df$estimate) - 1) * 100
static_df$conf_low_pct <- (exp(static_df$conf_low) - 1) * 100
static_df$conf_high_pct <- (exp(static_df$conf_high) - 1) * 100

print(static_df)

fwrite(
  static_df,
  file.path(out_dir, "borusyak_warning_subcategories_static_effects.csv")
)

if (length(static_errors) > 0) {
  static_error_df <- data.frame(
    panel = panel_label,
    outcome = names(static_errors),
    error = unlist(static_errors),
    row.names = NULL
  )

  print(static_error_df)

  fwrite(
    static_error_df,
    file.path(out_dir, "borusyak_warning_subcategories_static_errors.csv")
  )
}
```

# Dynamic Borusyak Effects

```{r dynamic-effects}
dynamic_results <- list()
dynamic_errors <- list()

for (var in outcome_vars) {
  cat("Running dynamic Borusyak model for:", var, "\n")

  dynamic_results[[var]] <- tryCatch(
    run_borusyak_dynamic(
      data = as.data.frame(panel_data),
      outcome_var = var,
      first_stage_formula = first_stage_formula,
      horizon = -6:6,
      pretrends = -6:-2,
      idname = "repo_id",
      tname = "time_id",
      gname = "event_id"
    ),
    error = function(e) {
      dynamic_errors[[var]] <<- conditionMessage(e)
      NULL
    }
  )
}

dynamic_df <- dplyr::bind_rows(lapply(seq_along(outcome_vars), function(i) {
  v <- outcome_vars[i]

  if (is.null(dynamic_results[[v]])) {
    return(data.frame())
  }

  extract_dynamic_result(
    dynamic_results[[v]],
    outcome = v,
    outcome_label = outcome_names[i],
    min_horizon = -6,
    max_horizon = 6
  )
}))

if (nrow(dynamic_df) > 0) {
  dynamic_df <- fill_missing_p_values(dynamic_df)

  dynamic_df$panel <- panel_label
  dynamic_df$estimate_pct <- (exp(dynamic_df$estimate) - 1) * 100
  dynamic_df$conf_low_pct <- (exp(dynamic_df$conf_low) - 1) * 100
  dynamic_df$conf_high_pct <- (exp(dynamic_df$conf_high) - 1) * 100

  if (!("significant" %in% names(dynamic_df))) {
    dynamic_df$significant <- !is.na(dynamic_df$conf_low) &
      !is.na(dynamic_df$conf_high) &
      ((dynamic_df$conf_low > 0) | (dynamic_df$conf_high < 0))
  }
}

print(dynamic_df)

fwrite(
  dynamic_df,
  file.path(out_dir, "borusyak_warning_subcategories_dynamic_effects.csv")
)

if (length(dynamic_errors) > 0) {
  dynamic_error_df <- data.frame(
    panel = panel_label,
    outcome = names(dynamic_errors),
    error = unlist(dynamic_errors),
    row.names = NULL
  )

  print(dynamic_error_df)

  fwrite(
    dynamic_error_df,
    file.path(out_dir, "borusyak_warning_subcategories_dynamic_errors.csv")
  )
}
```

# Dynamic Plot

```{r dynamic-plot, fig.width=11, fig.height=6}
if (nrow(dynamic_df) > 0) {
  p <- ggplot(dynamic_df, aes(x = time, y = estimate)) +
    geom_hline(yintercept = 0, linetype = "dashed") +
    geom_vline(xintercept = -1, linetype = "dotted") +
    geom_errorbar(aes(ymin = conf_low, ymax = conf_high), width = 0.15) +
    geom_point(aes(shape = significant)) +
    geom_line() +
    facet_wrap(~ outcome_label, scales = "free_y") +
    labs(
      title = paste("Borusyak Dynamic Effects for Warning Subcategories:", panel_label),
      x = "Months relative to Cursor adoption",
      y = "Estimate on log scale",
      shape = "95% CI excludes 0"
    ) +
    theme_minimal()

  print(p)

  ggsave(
    filename = file.path(out_dir, "dynamic_effects_borusyak_warning_subcategories.pdf"),
    plot = p,
    width = 11,
    height = 6
  )
} else {
  cat("No dynamic effects to plot.\n")
}
```

# Metadata

```{r metadata}
metadata <- data.frame(
  key = c(
    "script",
    "helper_file",
    "panel_label",
    "panel_path",
    "out_dir",
    "outcomes",
    "covariates",
    "estimator",
    "time_encoding",
    "cohort_filter",
    "input_source",
    "interpretation_note"
  ),
  value = c(
    "proc_r/DiffInDiffBorusyak_warning_subcategories_v2.Rmd",
    helpers_path,
    panel_label,
    panel_path,
    out_dir,
    paste(outcome_vars, collapse = ", "),
    "contributors_log + log_ncloc",
    "Borusyak imputation via didimputation::did_imputation",
    "YYYY-MM converted to month_id = year * 12 + month",
    "controls kept with event_yyyymm == 0; treatment cohorts kept if 202407 < event_yyyymm <= 202503",
    "run9e complete-case quality DiD input",
    "Warning subcategory decomposition of aggregate static_analysis_warnings"
  )
)

print(metadata)

fwrite(
  metadata,
  file.path(out_dir, "borusyak_warning_subcategories_metadata.csv")
)
```
