---
title: "Diff-in-Diff Borusyak: NPR-Based Python Commit-Function AGC Outcomes"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = TRUE, message = TRUE)
options(bitmapType = "cairo")

project_root <- Sys.getenv(
  "PROJECT_ROOT",
  unset = normalizePath(".", mustWork = TRUE)
)
project_root <- normalizePath(project_root, mustWork = TRUE)

resolve_project_path <- function(path_value) {
  if (is.null(path_value) || path_value == "") {
    return("")
  }
  if (grepl("^/", path_value)) {
    return(normalizePath(path_value, mustWork = FALSE))
  }
  normalizePath(file.path(project_root, path_value), mustWork = FALSE)
}

panel_path <- resolve_project_path(Sys.getenv("PANEL_PATH", unset = ""))
out_dir <- resolve_project_path(Sys.getenv("OUT_DIR", unset = ""))
panel_label <- Sys.getenv("PANEL_LABEL", unset = "panel")
specification_name <- Sys.getenv(
  "SPECIFICATION_NAME",
  unset = "range100_200"
)
ncloc_spec <- tolower(Sys.getenv("NCLOC_SPEC", unset = "paper"))
sample_type <- tolower(Sys.getenv("SAMPLE_TYPE", unset = "full"))
time_mode <- tolower(Sys.getenv("TIME_MODE", unset = "calendar_month"))
parse_exclusion_mode <- tolower(
  Sys.getenv("PARSE_EXCLUSION_MODE", unset = "parse_clean")
)
helper_path <- resolve_project_path(
  Sys.getenv(
    "HELPER_FILE",
    unset = "proc_r/diff_in_diff_borusyak_helpers.R"
  )
)

valid_ncloc_specs <- c("paper", "python_snapshot")
valid_sample_types <- c("full", "ratio")
valid_time_modes <- c("original_yyyymm", "calendar_month")
valid_parse_exclusion_modes <- c("all", "parse_clean")

if (!(ncloc_spec %in% valid_ncloc_specs)) {
  stop("NCLOC_SPEC must be paper or python_snapshot. Got: ", ncloc_spec)
}
if (!(sample_type %in% valid_sample_types)) {
  stop("SAMPLE_TYPE must be full or ratio. Got: ", sample_type)
}
if (!(time_mode %in% valid_time_modes)) {
  stop(
    "TIME_MODE must be original_yyyymm or calendar_month. Got: ",
    time_mode
  )
}
if (!(parse_exclusion_mode %in% valid_parse_exclusion_modes)) {
  stop(
    "PARSE_EXCLUSION_MODE must be all or parse_clean. Got: ",
    parse_exclusion_mode
  )
}
if (panel_path == "") {
  stop("PANEL_PATH environment variable is required.")
}
if (out_dir == "") {
  out_dir <- file.path(
    project_root,
    "repo_python/run-py-7c/strict/specifications",
    specification_name,
    sample_type,
    paste0(ncloc_spec, "_ncloc"),
    time_mode,
    parse_exclusion_mode
  )
}

dir.create(out_dir, recursive = TRUE, showWarnings = FALSE)
```

# Purpose

This notebook estimates Borusyak imputation Difference-in-Differences models
for NPR-based commit-function AGC outcomes prepared by run-py-7b.

The default `range100_200` specification includes only function-change events
whose implementation bodies contain 100--200 literal-space tokens and were
successfully scored by the frozen StarCoder2-7B perturbation detector.

The notebook separates:

1. Full zero-inclusive repository-month occurrence and count outcomes.
2. The conditional AGC-like event ratio among months with at least one
   NPR-scored function-change event.
3. Paper NCLOC and Python-snapshot NCLOC covariate specifications.
4. All and parse-clean samples.

The detector specification is fixed before the causal analysis. The notebook
validates the NPR specification name, threshold, scoring-completeness flag,
zero-event arithmetic, and AGC/HWC event partition before estimating models.

# Load Packages and Helper Functions

```{r load-packages}
library(data.table)
library(dplyr)
library(ggplot2)
library(didimputation)

if (!file.exists(helper_path)) {
  stop("Helper file not found: ", helper_path)
}
source(helper_path)
```

# Utility Functions

```{r utility-functions}
normalize_yyyymm <- function(x) {
  x <- as.character(x)
  x[x %in% c("", "NA", "NaN", "NULL", "None")] <- NA_character_
  x <- gsub("-", "", x)
  suppressWarnings(as.integer(x))
}

yyyymm_to_month_id <- function(x) {
  x <- as.integer(x)
  year <- x %/% 100L
  month <- x %% 100L
  out <- year * 12L + month
  out[is.na(x) | month < 1L | month > 12L] <- NA_integer_
  out
}

require_columns <- function(data, required, label) {
  missing <- setdiff(required, names(data))
  if (length(missing) > 0) {
    stop(label, " missing required columns: ", paste(missing, collapse = ", "))
  }
}

write_error_table <- function(errors, stage, output_path) {
  if (length(errors) == 0) {
    fwrite(
      data.frame(
        stage = character(),
        outcome = character(),
        error = character()
      ),
      output_path
    )
    return(invisible(NULL))
  }

  fwrite(
    data.frame(
      stage = stage,
      outcome = names(errors),
      error = unlist(errors),
      row.names = NULL,
      stringsAsFactors = FALSE
    ),
    output_path
  )
}
```

# Load and Validate Input Panel

```{r load-panel}
cat("Project root:", project_root, "\n")
cat("Panel path:", panel_path, "\n")
cat("Panel label:", panel_label, "\n")
cat("Specification:", specification_name, "\n")
cat("Output directory:", out_dir, "\n")
cat("NCLOC specification:", ncloc_spec, "\n")
cat("Sample type:", sample_type, "\n")
cat("Time mode:", time_mode, "\n")
cat("Parse-exclusion mode:", parse_exclusion_mode, "\n")

if (!file.exists(panel_path)) {
  stop("Panel file not found: ", panel_path)
}

panel_raw <- fread(panel_path)

base_required <- c(
  "dataset_source",
  "repo_name",
  "time",
  "event",
  "time_to_event",
  "npr_scored_function_change_events",
  "has_npr_scored_function_change_event",
  "zero_npr_scored_function_event_month",
  "npr_agc_function_change_events",
  "npr_hwc_function_change_events",
  "npr_agc_function_change_event_ratio",
  "log1p_npr_scored_function_change_events",
  "log1p_npr_agc_function_change_events",
  "log1p_npr_hwc_function_change_events",
  "log1p_age",
  "log1p_contributors",
  "log1p_stars",
  "log1p_issues",
  "ncloc_paper",
  "ncloc_python_snapshot",
  "analysis_ready_npr_paper_ncloc",
  "analysis_ready_npr_python_snapshot_ncloc",
  "analysis_ready_npr_ratio_paper_ncloc",
  "analysis_ready_npr_ratio_python_snapshot_ncloc",
  "has_parse_exclusion",
  "npr_detection_complete",
  "npr_specification",
  "npr_agc_threshold",
  "npr_algorithm_version",
  "npr_decision_rule",
  "npr_window_policy",
  "npr_function_aggregation",
  "npr_partial_body_policy",
  "npr_scoring_model",
  "npr_window_size_literal_space_tokens",
  "npr_perturbations_per_window",
  "npr_random_seed",
  "treatment_group"
)
require_columns(panel_raw, base_required, "Input panel")

if (anyDuplicated(panel_raw[, .(dataset_source, repo_name, time)]) > 0) {
  stop("Input panel has duplicate dataset_source/repo_name/time keys.")
}
if (!all(panel_raw$dataset_source %in% c("control", "treatment"))) {
  stop("dataset_source contains unexpected values.")
}

specification_mismatch_rows <- sum(
  as.character(panel_raw$npr_specification) != specification_name,
  na.rm = TRUE
) + sum(is.na(panel_raw$npr_specification))
if (specification_mismatch_rows > 0) {
  stop(
    "npr_specification does not match the requested specification on ",
    specification_mismatch_rows,
    " rows."
  )
}

treatment_group_mismatch_rows <- sum(
  as.character(panel_raw$treatment_group) !=
    as.character(panel_raw$dataset_source),
  na.rm = TRUE
) + sum(is.na(panel_raw$treatment_group))
if (treatment_group_mismatch_rows > 0) {
  stop(
    "treatment_group does not match dataset_source on ",
    treatment_group_mismatch_rows,
    " rows."
  )
}

detection_complete_true <- panel_raw$npr_detection_complete %in%
  c(TRUE, 1L, 1.0, "True", "TRUE", "true", "1", "1.0")
detection_incomplete_rows <- sum(!detection_complete_true)
if (detection_incomplete_rows > 0) {
  stop(
    "npr_detection_complete is not uniformly true: ",
    detection_incomplete_rows,
    " rows are false, missing, or malformed."
  )
}

core_na_rows <- sum(
  is.na(panel_raw$npr_scored_function_change_events) |
    is.na(panel_raw$has_npr_scored_function_change_event) |
    is.na(panel_raw$zero_npr_scored_function_event_month) |
    is.na(panel_raw$npr_agc_function_change_events) |
    is.na(panel_raw$npr_hwc_function_change_events)
)
if (core_na_rows > 0) {
  stop("Missing NPR event values on ", core_na_rows, " rows.")
}

occurrence_mismatch_rows <- sum(
  as.integer(panel_raw$has_npr_scored_function_change_event) !=
    as.integer(panel_raw$npr_scored_function_change_events > 0),
  na.rm = TRUE
)
zero_flag_mismatch_rows <- sum(
  as.integer(panel_raw$zero_npr_scored_function_event_month) !=
    (1L - as.integer(panel_raw$has_npr_scored_function_change_event)),
  na.rm = TRUE
)
partition_mismatch_rows <- sum(
  panel_raw$npr_agc_function_change_events +
    panel_raw$npr_hwc_function_change_events !=
    panel_raw$npr_scored_function_change_events,
  na.rm = TRUE
)

if (
  occurrence_mismatch_rows > 0 ||
    zero_flag_mismatch_rows > 0 ||
    partition_mismatch_rows > 0
) {
  stop(
    "NPR event arithmetic violated. Occurrence mismatches: ",
    occurrence_mismatch_rows,
    "; zero-flag mismatches: ",
    zero_flag_mismatch_rows,
    "; AGC/HWC partition mismatches: ",
    partition_mismatch_rows
  )
}

positive_event_mask <- panel_raw$npr_scored_function_change_events > 0
zero_event_mask <- !positive_event_mask
ratio_missing_positive_rows <- sum(
  is.na(panel_raw$npr_agc_function_change_event_ratio[positive_event_mask])
)
ratio_nonmissing_zero_rows <- sum(
  !is.na(panel_raw$npr_agc_function_change_event_ratio[zero_event_mask])
)
ratio_out_of_bounds_rows <- sum(
  !panel_raw$npr_agc_function_change_event_ratio[positive_event_mask] %between%
    c(0, 1),
  na.rm = TRUE
)
if (
  ratio_missing_positive_rows > 0 ||
    ratio_nonmissing_zero_rows > 0 ||
    ratio_out_of_bounds_rows > 0
) {
  stop(
    "Conditional NPR ratio contract violated. Missing-positive: ",
    ratio_missing_positive_rows,
    "; nonmissing-zero: ",
    ratio_nonmissing_zero_rows,
    "; out-of-bounds: ",
    ratio_out_of_bounds_rows
  )
}

cat("Loaded rows:", nrow(panel_raw), "\n")
cat("Loaded repositories:", uniqueN(panel_raw$repo_name), "\n")
cat("Zero NPR-event rows:", sum(zero_event_mask), "\n")
cat("NPR-positive rows:", sum(positive_event_mask), "\n")
```

# Select Outcomes, Covariates, and Analysis Sample

```{r configure-model}
if (sample_type == "full") {
  outcome_vars <- c(
    "has_npr_scored_function_change_event",
    "log1p_npr_scored_function_change_events",
    "log1p_npr_agc_function_change_events",
    "log1p_npr_hwc_function_change_events"
  )
  outcome_names <- c(
    "Any NPR-Scored Function-Change Event",
    "NPR-Scored Function-Change Events (log1p)",
    "NPR AGC-Like Function-Change Events (log1p)",
    "NPR HWC-Like Function-Change Events (log1p)"
  )
} else {
  outcome_vars <- c("npr_agc_function_change_event_ratio")
  outcome_names <- c(
    "NPR AGC-Like Event Share | Positive NPR-Event Month"
  )
}

if (ncloc_spec == "paper") {
  ncloc_column <- "ncloc_paper"
  readiness_column <- if (sample_type == "full") {
    "analysis_ready_npr_paper_ncloc"
  } else {
    "analysis_ready_npr_ratio_paper_ncloc"
  }
} else {
  ncloc_column <- "ncloc_python_snapshot"
  readiness_column <- if (sample_type == "full") {
    "analysis_ready_npr_python_snapshot_ncloc"
  } else {
    "analysis_ready_npr_ratio_python_snapshot_ncloc"
  }
}

covariates <- c(
  "log1p_age",
  ncloc_column,
  "log1p_contributors",
  "log1p_stars",
  "log1p_issues"
)
require_columns(
  panel_raw,
  c(outcome_vars, covariates, readiness_column),
  "Configured model"
)

panel_data <- copy(panel_raw)
panel_data <- panel_data[get(readiness_column) == 1]
rows_after_readiness_filter <- nrow(panel_data)

if (parse_exclusion_mode == "parse_clean") {
  panel_data <- panel_data[has_parse_exclusion == 0]
}
rows_after_parse_filter <- nrow(panel_data)

if (sample_type == "ratio") {
  panel_data <- panel_data[
    npr_scored_function_change_events > 0 &
      !is.na(npr_agc_function_change_event_ratio)
  ]
}
rows_after_ratio_filter <- nrow(panel_data)

if (nrow(panel_data) == 0) {
  stop("No rows remain after the explicit analysis filters.")
}

model_required <- c(outcome_vars, covariates)
implicit_missing_rows <- sum(!complete.cases(panel_data[, ..model_required]))
if (implicit_missing_rows > 0) {
  stop(
    "Analysis-ready flag allowed rows with missing model variables: ",
    implicit_missing_rows
  )
}

panel_data[, time_yyyymm := normalize_yyyymm(time)]
event_yyyymm_raw <- normalize_yyyymm(panel_data$event)
event_yyyymm_raw[is.na(event_yyyymm_raw)] <- 0L
panel_data[, event_yyyymm := event_yyyymm_raw]

event_membership_mismatch_rows <- panel_data[
  ,
  sum((dataset_source == "treatment") != (event_yyyymm > 0L))
]
if (event_membership_mismatch_rows > 0) {
  stop(
    "Event encoding disagrees with dataset_source on ",
    event_membership_mismatch_rows,
    " rows."
  )
}

panel_data <- panel_data[
  event_yyyymm == 0L |
    (event_yyyymm > 202407L & event_yyyymm <= 202503L)
]
rows_after_cohort_filter <- nrow(panel_data)

panel_data[, repo_name_str := as.character(repo_name)]
panel_data[, repo_id := as.integer(factor(repo_name_str))]

if (time_mode == "original_yyyymm") {
  panel_data[, time_id := time_yyyymm]
  panel_data[, event_id := event_yyyymm]
  time_encoding_used <- "numeric_YYYYMM_original_notebook_compatible"
} else {
  panel_data[, time_id := yyyymm_to_month_id(time_yyyymm)]
  panel_data[, event_id := fifelse(
    event_yyyymm == 0L,
    0L,
    yyyymm_to_month_id(event_yyyymm)
  )]
  time_encoding_used <- "sequential_calendar_month_id"
}

panel_data <- panel_data[!is.na(time_id)]
panel_data <- panel_data[event_id == 0L | !is.na(event_id)]
panel_data[, treated := as.integer(event_id > 0L)]

first_stage_rhs <- paste(covariates, collapse = " + ")
first_stage_formula <- as.formula(
  paste0("~ ", first_stage_rhs, " | repo_id + time_id")
)

cat("Readiness column:", readiness_column, "\n")
cat("Rows after readiness filter:", rows_after_readiness_filter, "\n")
cat("Rows after parse filter:", rows_after_parse_filter, "\n")
cat("Rows after ratio filter:", rows_after_ratio_filter, "\n")
cat("Rows after cohort filter:", rows_after_cohort_filter, "\n")
cat("Rows used by models:", nrow(panel_data), "\n")
cat("Repositories used:", uniqueN(panel_data$repo_id), "\n")
cat("Time encoding:", time_encoding_used, "\n")
cat("First-stage formula:\n")
print(first_stage_formula)
```

# Panel Checks and Input Summary

```{r panel-checks}
panel_checks <- data.frame(
  check = c(
    "panel_label",
    "specification_name",
    "sample_type",
    "ncloc_specification",
    "readiness_column",
    "time_mode",
    "parse_exclusion_mode",
    "input_rows",
    "input_repositories",
    "specification_mismatch_rows",
    "treatment_group_mismatch_rows",
    "event_membership_mismatch_rows",
    "occurrence_arithmetic_mismatch_rows",
    "zero_flag_arithmetic_mismatch_rows",
    "agc_hwc_partition_mismatch_rows",
    "detection_incomplete_rows",
    "ratio_missing_positive_rows",
    "ratio_nonmissing_zero_rows",
    "ratio_out_of_bounds_rows",
    "rows_after_readiness_filter",
    "rows_after_parse_filter",
    "rows_after_ratio_filter",
    "rows_after_cohort_filter",
    "rows_used_by_models",
    "repositories_used_by_models",
    "treated_repositories",
    "control_repositories",
    "zero_npr_event_rows_in_model_sample",
    "parse_exclusion_rows_in_model_sample",
    "outcome_missing_sum",
    "covariate_missing_sum",
    "npr_agc_threshold",
    "npr_algorithm_version",
    "npr_decision_rule",
    "npr_window_policy",
    "npr_function_aggregation",
    "npr_partial_body_policy",
    "npr_scoring_model",
    "npr_window_size_literal_space_tokens",
    "npr_perturbations_per_window",
    "npr_random_seed"
  ),
  value = c(
    panel_label,
    specification_name,
    sample_type,
    ncloc_spec,
    readiness_column,
    time_mode,
    parse_exclusion_mode,
    nrow(panel_raw),
    uniqueN(panel_raw$repo_name),
    specification_mismatch_rows,
    treatment_group_mismatch_rows,
    event_membership_mismatch_rows,
    occurrence_mismatch_rows,
    zero_flag_mismatch_rows,
    partition_mismatch_rows,
    detection_incomplete_rows,
    ratio_missing_positive_rows,
    ratio_nonmissing_zero_rows,
    ratio_out_of_bounds_rows,
    rows_after_readiness_filter,
    rows_after_parse_filter,
    rows_after_ratio_filter,
    rows_after_cohort_filter,
    nrow(panel_data),
    uniqueN(panel_data$repo_id),
    uniqueN(panel_data[treated == 1, repo_id]),
    uniqueN(panel_data[treated == 0, repo_id]),
    sum(panel_data$zero_npr_scored_function_event_month == 1, na.rm = TRUE),
    sum(panel_data$has_parse_exclusion == 1, na.rm = TRUE),
    sum(is.na(panel_data[, ..outcome_vars])),
    sum(is.na(panel_data[, ..covariates])),
    paste(unique(panel_raw$npr_agc_threshold), collapse = ";"),
    paste(unique(panel_raw$npr_algorithm_version), collapse = ";"),
    paste(unique(panel_raw$npr_decision_rule), collapse = ";"),
    paste(unique(panel_raw$npr_window_policy), collapse = ";"),
    paste(unique(panel_raw$npr_function_aggregation), collapse = ";"),
    paste(unique(panel_raw$npr_partial_body_policy), collapse = ";"),
    paste(unique(panel_raw$npr_scoring_model), collapse = ";"),
    paste(unique(panel_raw$npr_window_size_literal_space_tokens), collapse = ";"),
    paste(unique(panel_raw$npr_perturbations_per_window), collapse = ";"),
    paste(unique(panel_raw$npr_random_seed), collapse = ";")
  ),
  stringsAsFactors = FALSE
)

print(panel_checks)
fwrite(
  panel_checks,
  file.path(out_dir, "borusyak_agc_commit_function_npr_panel_checks.csv")
)

input_summary <- panel_data[, .(
  rows = .N,
  repositories = uniqueN(repo_id),
  mean_has_npr_scored_function_change_event = mean(
    has_npr_scored_function_change_event,
    na.rm = TRUE
  ),
  mean_log1p_npr_scored_function_change_events = mean(
    log1p_npr_scored_function_change_events,
    na.rm = TRUE
  ),
  mean_log1p_npr_agc_function_change_events = mean(
    log1p_npr_agc_function_change_events,
    na.rm = TRUE
  ),
  mean_log1p_npr_hwc_function_change_events = mean(
    log1p_npr_hwc_function_change_events,
    na.rm = TRUE
  ),
  mean_npr_agc_function_change_event_ratio = mean(
    npr_agc_function_change_event_ratio,
    na.rm = TRUE
  ),
  mean_ncloc = mean(get(ncloc_column), na.rm = TRUE)
), by = dataset_source]

print(input_summary)
fwrite(
  input_summary,
  file.path(out_dir, "borusyak_agc_commit_function_npr_input_summary.csv")
)
```

# Outcomes and First Stage

```{r outcomes}
print(data.frame(outcome = outcome_vars, label = outcome_names))
cat("NCLOC column:", ncloc_column, "\n")
cat("Readiness column:", readiness_column, "\n")
print(first_stage_formula)
```

# Static Borusyak Effects

```{r static-effects}
static_results <- list()
static_errors <- list()

for (var in outcome_vars) {
  cat("Running static Borusyak model for:", var, "\n")
  static_results[[var]] <- tryCatch(
    run_borusyak_static(
      data = panel_data,
      outcome_var = var,
      first_stage_formula = first_stage_formula,
      idname = "repo_id",
      tname = "time_id",
      gname = "event_id"
    ),
    error = function(e) {
      static_errors[[var]] <<- conditionMessage(e)
      NULL
    }
  )
}

static_df <- bind_rows(lapply(outcome_vars, function(v) {
  extract_static_result(static_results[[v]], v)
}))
static_df$outcome_label <- outcome_names[match(static_df$outcome, outcome_vars)]
static_df$panel <- panel_label
static_df$specification <- specification_name
static_df$sample_type <- sample_type
static_df$ncloc_spec <- ncloc_spec
static_df$time_mode <- time_mode
static_df$parse_exclusion_mode <- parse_exclusion_mode

print(static_df)
fwrite(
  static_df,
  file.path(out_dir, "borusyak_agc_commit_function_npr_static_effects.csv")
)
write_error_table(
  static_errors,
  "static",
  file.path(out_dir, "borusyak_agc_commit_function_npr_static_errors.csv")
)
```

# Dynamic Borusyak Effects

```{r dynamic-effects}
dynamic_results <- list()
dynamic_errors <- list()

for (var in outcome_vars) {
  cat("Running dynamic Borusyak model for:", var, "\n")
  dynamic_results[[var]] <- tryCatch(
    run_borusyak_dynamic(
      data = panel_data,
      outcome_var = var,
      first_stage_formula = first_stage_formula,
      horizon = -6:6,
      pretrends = -6:-2,
      idname = "repo_id",
      tname = "time_id",
      gname = "event_id"
    ),
    error = function(e) {
      dynamic_errors[[var]] <<- conditionMessage(e)
      NULL
    }
  )
}

dynamic_df <- bind_rows(lapply(seq_along(outcome_vars), function(i) {
  v <- outcome_vars[i]
  extract_dynamic_result(
    dynamic_results[[v]],
    outcome = v,
    outcome_label = outcome_names[i],
    min_horizon = -6,
    max_horizon = 6
  )
}))

if (nrow(dynamic_df) > 0) {
  dynamic_df$panel <- panel_label
  dynamic_df$specification <- specification_name
  dynamic_df$sample_type <- sample_type
  dynamic_df$ncloc_spec <- ncloc_spec
  dynamic_df$time_mode <- time_mode
  dynamic_df$parse_exclusion_mode <- parse_exclusion_mode
}

print(dynamic_df)
fwrite(
  dynamic_df,
  file.path(out_dir, "borusyak_agc_commit_function_npr_dynamic_effects.csv")
)
write_error_table(
  dynamic_errors,
  "dynamic",
  file.path(out_dir, "borusyak_agc_commit_function_npr_dynamic_errors.csv")
)
```

# Dynamic Plot

```{r dynamic-plot, fig.width=11, fig.height=3.5}
if (nrow(dynamic_df) > 0) {
  dynamic_df$outcome_label <- factor(
    dynamic_df$outcome_label,
    levels = outcome_names
  )

  plot_object <- ggplot(dynamic_df, aes(x = time, y = estimate)) +
    geom_errorbar(
      data = subset(dynamic_df, significant %in% TRUE),
      aes(ymin = conf_low, ymax = conf_high),
      width = 0.4,
      linetype = "solid"
    ) +
    geom_errorbar(
      data = subset(dynamic_df, !(significant %in% TRUE)),
      aes(ymin = conf_low, ymax = conf_high),
      width = 0.4,
      linetype = "dotted"
    ) +
    geom_point(
      data = subset(dynamic_df, significant %in% TRUE),
      shape = 19,
      size = 1.7
    ) +
    geom_point(
      data = subset(dynamic_df, !(significant %in% TRUE)),
      shape = 21,
      fill = "transparent",
      size = 1.7
    ) +
    geom_hline(yintercept = 0, linetype = "dashed") +
    geom_vline(xintercept = -0.5, linetype = "dashed") +
    scale_x_continuous(breaks = -6:6) +
    coord_cartesian(xlim = c(-6.5, 6.5)) +
    facet_wrap(~ outcome_label, scales = "free_y", nrow = 1) +
    labs(
      title = paste("Borusyak NPR Commit-Function AGC DiD:", panel_label),
      subtitle = paste(
        "Specification:", specification_name,
        "| Sample:", sample_type,
        "| NCLOC:", ncloc_spec,
        "| Time:", time_encoding_used,
        "| Parse:", parse_exclusion_mode
      ),
      x = "Months Relative to Cursor Adoption",
      y = "Treatment Effect",
      caption = paste(
        "Filled dots: CI excludes 0. Hollow dots: CI includes 0.",
        if (sample_type == "ratio") {
          paste(
            "Ratio is conditional on at least one NPR-scored",
            "function-change event."
          )
        } else {
          "Zero NPR-event repository-months are retained."
        }
      )
    ) +
    theme_minimal() +
    theme(
      panel.grid.minor = element_blank(),
      plot.caption = element_text(hjust = 0.5, size = 8)
    )

  print(plot_object)
  ggsave(
    filename = file.path(
      out_dir,
      "dynamic_effects_borusyak_agc_commit_function_npr.pdf"
    ),
    plot = plot_object,
    width = 11,
    height = 3.5
  )
} else {
  cat("No dynamic effects to plot.\n")
}
```

# Final Model Validation (Hard Fail)

```{r final-model-validation}
static_model_error_count <- length(static_errors)
dynamic_model_error_count <- length(dynamic_errors)

static_effects_complete <- all(outcome_vars %in% static_df$outcome) &&
  all(!is.na(static_df$estimate[match(outcome_vars, static_df$outcome)]))

dynamic_effects_nonempty <- nrow(dynamic_df) > 0 &&
  all(outcome_vars %in% dynamic_df$outcome)

dynamic_pre_period_present <- if (dynamic_effects_nonempty) {
  all(sapply(outcome_vars, function(v) {
    any(dynamic_df$outcome == v & dynamic_df$time < 0)
  }))
} else {
  FALSE
}

dynamic_post_period_present <- if (dynamic_effects_nonempty) {
  all(sapply(outcome_vars, function(v) {
    any(dynamic_df$outcome == v & dynamic_df$time >= 0)
  }))
} else {
  FALSE
}

final_model_validation <- data.frame(
  check = c(
    "static_model_error_count",
    "dynamic_model_error_count",
    "static_effects_complete",
    "dynamic_effects_nonempty",
    "dynamic_pre_period_present",
    "dynamic_post_period_present"
  ),
  value = c(
    static_model_error_count,
    dynamic_model_error_count,
    static_effects_complete,
    dynamic_effects_nonempty,
    dynamic_pre_period_present,
    dynamic_post_period_present
  ),
  stringsAsFactors = FALSE
)

print(final_model_validation)
fwrite(
  final_model_validation,
  file.path(
    out_dir,
    "borusyak_agc_commit_function_npr_final_model_validation.csv"
  )
)

if (static_model_error_count > 0) {
  stop("Static model failures: ", paste(names(static_errors), collapse = ", "))
}
if (dynamic_model_error_count > 0) {
  stop("Dynamic model failures: ", paste(names(dynamic_errors), collapse = ", "))
}
if (!static_effects_complete) {
  stop("Static effects are incomplete or contain missing estimates.")
}
if (!dynamic_effects_nonempty) {
  stop("Dynamic effects are empty or missing one or more outcomes.")
}
if (!dynamic_pre_period_present || !dynamic_post_period_present) {
  stop("Dynamic effects do not contain both pre- and post-treatment periods.")
}
```

# Metadata

```{r metadata}
metadata <- data.frame(
  key = c(
    "script",
    "helper_file",
    "panel_label",
    "panel_path",
    "out_dir",
    "specification_name",
    "sample_type",
    "ncloc_specification",
    "ncloc_column",
    "readiness_column",
    "parse_exclusion_mode",
    "outcomes",
    "covariates",
    "first_stage_formula",
    "rows_after_readiness_filter",
    "rows_after_parse_filter",
    "rows_after_ratio_filter",
    "rows_after_cohort_filter",
    "rows_used_by_models",
    "repositories_used_by_models",
    "estimator",
    "time_encoding",
    "horizon",
    "pretrends",
    "static_model_error_count",
    "dynamic_model_error_count",
    "npr_agc_threshold",
    "npr_algorithm_version",
    "npr_decision_rule",
    "npr_window_policy",
    "npr_function_aggregation",
    "npr_partial_body_policy",
    "npr_scoring_model",
    "npr_window_size_literal_space_tokens",
    "npr_perturbations_per_window",
    "npr_random_seed",
    "input_source",
    "interpretation_note"
  ),
  value = c(
    "proc_r/DiffInDiffBorusyak_agc_commit_function_npr.Rmd",
    helper_path,
    panel_label,
    panel_path,
    out_dir,
    specification_name,
    sample_type,
    ncloc_spec,
    ncloc_column,
    readiness_column,
    parse_exclusion_mode,
    paste(outcome_vars, collapse = ", "),
    paste(covariates, collapse = " + "),
    paste(deparse(first_stage_formula), collapse = " "),
    rows_after_readiness_filter,
    rows_after_parse_filter,
    rows_after_ratio_filter,
    rows_after_cohort_filter,
    nrow(panel_data),
    uniqueN(panel_data$repo_id),
    "Borusyak imputation via didimputation::did_imputation",
    time_encoding_used,
    "-6:6",
    "-6:-2",
    static_model_error_count,
    dynamic_model_error_count,
    paste(unique(panel_raw$npr_agc_threshold), collapse = ";"),
    paste(unique(panel_raw$npr_algorithm_version), collapse = ";"),
    paste(unique(panel_raw$npr_decision_rule), collapse = ";"),
    paste(unique(panel_raw$npr_window_policy), collapse = ";"),
    paste(unique(panel_raw$npr_function_aggregation), collapse = ";"),
    paste(unique(panel_raw$npr_partial_body_policy), collapse = ";"),
    paste(unique(panel_raw$npr_scoring_model), collapse = ";"),
    paste(unique(panel_raw$npr_window_size_literal_space_tokens), collapse = ";"),
    paste(unique(panel_raw$npr_perturbations_per_window), collapse = ";"),
    paste(unique(panel_raw$npr_random_seed), collapse = ";"),
    paste(
      "run-py-7b NPR covariate-complete panel derived from run-py-7a",
      "repository-month aggregation of frozen DetectCodeGPT body scores"
    ),
    if (sample_type == "ratio") {
      paste(
        "Conditional composition effect among repository-months with at",
        "least one NPR-scored function-change event. It is not an",
        "unconditional total effect and may be subject to post-treatment",
        "selection if treatment affects the occurrence of NPR-scored events."
      )
    } else {
      paste(
        "Occurrence and count outcomes use the full zero-inclusive",
        "repository-month panel for the specified NPR token range."
      )
    }
  ),
  stringsAsFactors = FALSE
)

print(metadata)
fwrite(
  metadata,
  file.path(out_dir, "borusyak_agc_commit_function_npr_metadata.csv")
)
```

# Session Info

```{r session-info}
sessionInfo()
```
