---
title: "Borusyak DiD Activity Check: Commits and Lines Added"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
params:
  panel_file: "repo_python/run-py-4a/strict/panel_event_monthly_agc_changed_block_py.csv"
  output_dir: "repo_python/run-py-4c/strict/activity-check"
  apply_original_event_filter: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  dev = "CairoPNG",
  dpi = 160
)
options(bitmapType = "cairo")
utils::globalVariables(c(
  "term", "estimate", "conf.low", "conf.high", "outcome",
  "outcome_label", "event_time", "percent_change",
  "percent_conf_low", "percent_conf_high", "is_significant"
))
```

# Purpose

This debugging report checks whether the validated AGC changed-block panel can
also reproduce the original development-activity outcomes using only:

- monthly commits; and
- monthly lines added.

The AGC changed-block columns are not used as outcomes in this report. The
input panel is used because it preserves the strict matched repository-month
sample and its original activity variables.

# Packages

```{r packages}
library(didimputation)
library(data.table)
library(dplyr)
library(ggplot2)
library(Cairo)
```

# Helper Functions

```{r helpers}
normalize_yyyymm <- function(x) {
  text <- gsub("-", "", trimws(as.character(x)))
  text[text %in% c("", "NA", "NaN")] <- NA_character_
  suppressWarnings(as.integer(text))
}

yyyymm_to_month_id <- function(x) {
  year <- x %/% 100L
  month <- x %% 100L
  invalid <- is.na(x) | month < 1L | month > 12L
  result <- year * 12L + month
  result[invalid] <- NA_integer_
  result
}

require_columns <- function(data, columns, label) {
  missing <- setdiff(columns, names(data))
  if (length(missing) > 0L) {
    stop(label, " is missing required columns: ", paste(missing, collapse = ", "))
  }
}

extract_static_effect <- function(result, outcome_name, outcome_label, n_rows) {
  row <- result[result$term == "treat", , drop = FALSE]
  if (nrow(row) != 1L) {
    stop("Expected exactly one static treatment-effect row for ", outcome_name)
  }

  data.frame(
    outcome = outcome_name,
    outcome_label = outcome_label,
    term = "treat",
    estimate_log = row$estimate,
    std_error = row$std.error,
    conf_low_log = row$conf.low,
    conf_high_log = row$conf.high,
    percent_change = (exp(row$estimate) - 1) * 100,
    percent_conf_low = (exp(row$conf.low) - 1) * 100,
    percent_conf_high = (exp(row$conf.high) - 1) * 100,
    model_rows = n_rows,
    stringsAsFactors = FALSE
  )
}

extract_dynamic_effects <- function(result, outcome_name, outcome_label, n_rows) {
  rows <- result[result$term != "treat", , drop = FALSE]
  rows$event_time <- suppressWarnings(as.integer(as.character(rows$term)))
  rows <- rows[!is.na(rows$event_time) & rows$event_time >= -6L & rows$event_time <= 6L, ]

  data.frame(
    outcome = outcome_name,
    outcome_label = outcome_label,
    event_time = rows$event_time,
    estimate_log = rows$estimate,
    std_error = rows$std.error,
    conf_low_log = rows$conf.low,
    conf_high_log = rows$conf.high,
    percent_change = (exp(rows$estimate) - 1) * 100,
    percent_conf_low = (exp(rows$conf.low) - 1) * 100,
    percent_conf_high = (exp(rows$conf.high) - 1) * 100,
    is_significant = rows$conf.low > 0 | rows$conf.high < 0,
    model_rows = n_rows,
    stringsAsFactors = FALSE
  )
}
```

# Load and Validate the Panel

```{r load-panel}
panel_path <- normalizePath(params$panel_file, mustWork = TRUE)
out_dir <- params$output_dir
dir.create(out_dir, recursive = TRUE, showWarnings = FALSE)

panel <- fread(panel_path)

ncloc_column <- if ("ncloc_paper" %in% names(panel)) {
  "ncloc_paper"
} else if ("ncloc" %in% names(panel)) {
  "ncloc"
} else {
  stop("The panel must contain either ncloc_paper or ncloc.")
}

required_columns <- c(
  "repo_name",
  "time",
  "event",
  "dataset_source",
  "commits",
  "lines_added",
  "age",
  "contributors",
  "stars",
  "issues",
  ncloc_column
)
require_columns(panel, required_columns, "Input panel")

rows_before_filter <- nrow(panel)
repos_before_filter <- uniqueN(panel$repo_name)

panel[, time_yyyymm := normalize_yyyymm(time)]
panel[, event_yyyymm := normalize_yyyymm(event)]
panel[dataset_source == "control", event_yyyymm := 0L]

if (isTRUE(params$apply_original_event_filter)) {
  panel <- panel[
    dataset_source == "control" |
      (event_yyyymm > 202407L & event_yyyymm <= 202503L)
  ]
}

panel[, time_id := yyyymm_to_month_id(time_yyyymm)]
panel[, event_id := fifelse(
  dataset_source == "control",
  0L,
  yyyymm_to_month_id(event_yyyymm)
)]
panel[, repo_id := as.integer(factor(repo_name))]

numeric_columns <- c(
  "commits", "lines_added", "age", "contributors", "stars", "issues",
  ncloc_column
)
for (column_name in numeric_columns) {
  panel[, (column_name) := suppressWarnings(as.numeric(get(column_name)))]
}

negative_counts <- data.frame(
  variable = c("commits", "lines_added"),
  negative_rows = c(
    sum(panel$commits < 0, na.rm = TRUE),
    sum(panel$lines_added < 0, na.rm = TRUE)
  )
)
if (any(negative_counts$negative_rows > 0L)) {
  stop("Negative activity values were found; see negative_counts.")
}

panel[, commits_log := fifelse(!is.na(commits), log1p(commits), NA_real_)]
panel[, lines_added_log := fifelse(!is.na(lines_added), log1p(lines_added), NA_real_)]
panel[, age_log := fifelse(!is.na(age) & age >= 0, log1p(age), NA_real_)]
panel[, contributors_log := fifelse(
  !is.na(contributors) & contributors >= 0,
  log1p(contributors),
  NA_real_
)]
panel[, stars_log := fifelse(!is.na(stars) & stars >= 0, log1p(stars), NA_real_)]
panel[, issues_log := fifelse(!is.na(issues) & issues >= 0, log1p(issues), NA_real_)]
panel[, ncloc_model := get(ncloc_column)]

if (any(is.na(panel$time_id))) {
  stop("Some repository-month rows have invalid time values.")
}
if (any(panel$dataset_source == "treatment" & is.na(panel$event_id))) {
  stop("Some treatment rows have invalid event values.")
}
if (any(panel$dataset_source == "control" & panel$event_id != 0L)) {
  stop("Control rows must have event_id equal to zero.")
}

input_summary <- data.frame(
  metric = c(
    "panel_path",
    "ncloc_column",
    "original_event_filter",
    "rows_before_filter",
    "rows_after_filter",
    "repositories_before_filter",
    "repositories_after_filter",
    "treatment_repositories",
    "control_repositories",
    "commits_nonmissing",
    "lines_added_nonmissing"
  ),
  value = c(
    panel_path,
    ncloc_column,
    as.character(params$apply_original_event_filter),
    rows_before_filter,
    nrow(panel),
    repos_before_filter,
    uniqueN(panel$repo_name),
    uniqueN(panel[dataset_source == "treatment", repo_name]),
    uniqueN(panel[dataset_source == "control", repo_name]),
    sum(!is.na(panel$commits)),
    sum(!is.na(panel$lines_added))
  ),
  stringsAsFactors = FALSE
)

print(input_summary)
print(negative_counts)

fwrite(input_summary, file.path(out_dir, "borusyak_activity_input_summary.csv"))
fwrite(negative_counts, file.path(out_dir, "borusyak_activity_negative_value_checks.csv"))
```

# Outcomes and Common Model Sample

```{r outcomes-and-sample}
outcome_definitions <- data.frame(
  outcome = c("commits_log", "lines_added_log"),
  outcome_label = c("Commits", "Lines Added"),
  source_column = c("commits", "lines_added"),
  stringsAsFactors = FALSE
)

model_required_columns <- c(
  "repo_id",
  "time_id",
  "event_id",
  "commits_log",
  "lines_added_log",
  "age_log",
  "contributors_log",
  "stars_log",
  "issues_log",
  "ncloc_model"
)

model_data <- copy(panel[complete.cases(panel[, ..model_required_columns])])
if (nrow(model_data) == 0L) {
  stop("No complete-case rows remain for the activity models.")
}

sample_summary <- data.frame(
  metric = c(
    "model_rows",
    "model_repositories",
    "treatment_repositories",
    "control_repositories",
    "treated_post_rows"
  ),
  value = c(
    nrow(model_data),
    uniqueN(model_data$repo_name),
    uniqueN(model_data[dataset_source == "treatment", repo_name]),
    uniqueN(model_data[dataset_source == "control", repo_name]),
    sum(model_data$dataset_source == "treatment" & model_data$time_id >= model_data$event_id)
  ),
  stringsAsFactors = FALSE
)

print(outcome_definitions)
print(sample_summary)
fwrite(sample_summary, file.path(out_dir, "borusyak_activity_sample_summary.csv"))
```

# Static Treatment Effects

```{r static-effects}
first_stage_formula <- ~ age_log + ncloc_model + contributors_log +
  stars_log + issues_log | repo_id + time_id

static_results <- list()
static_rows <- list()

for (i in seq_len(nrow(outcome_definitions))) {
  outcome_var <- outcome_definitions$outcome[i]
  outcome_label <- outcome_definitions$outcome_label[i]

  cat("Running static activity model:", outcome_var, "| rows =", nrow(model_data), "\n")

  result <- did_imputation(
    data = model_data,
    yname = outcome_var,
    gname = "event_id",
    tname = "time_id",
    idname = "repo_id",
    first_stage = first_stage_formula
  )

  static_results[[outcome_var]] <- result
  static_rows[[length(static_rows) + 1L]] <- extract_static_effect(
    result,
    outcome_var,
    outcome_label,
    nrow(model_data)
  )
}

static_df <- bind_rows(static_rows)
print(static_df)
fwrite(static_df, file.path(out_dir, "borusyak_activity_static_effects.csv"))

knitr::kable(
  static_df[, c(
    "outcome_label", "estimate_log", "std_error", "conf_low_log",
    "conf_high_log", "percent_change", "percent_conf_low",
    "percent_conf_high", "model_rows"
  )],
  digits = 3,
  caption = "Static Treatment Effects for Commits and Lines Added"
)
```

# Dynamic Treatment Effects

```{r dynamic-effects}
dynamic_results <- list()
dynamic_rows <- list()

for (i in seq_len(nrow(outcome_definitions))) {
  outcome_var <- outcome_definitions$outcome[i]
  outcome_label <- outcome_definitions$outcome_label[i]

  cat("Running dynamic activity model:", outcome_var, "| rows =", nrow(model_data), "\n")

  result <- did_imputation(
    data = model_data,
    yname = outcome_var,
    gname = "event_id",
    tname = "time_id",
    idname = "repo_id",
    first_stage = first_stage_formula,
    horizon = -6:6,
    pretrends = -6:-2
  )

  dynamic_results[[outcome_var]] <- result
  dynamic_rows[[length(dynamic_rows) + 1L]] <- extract_dynamic_effects(
    result,
    outcome_var,
    outcome_label,
    nrow(model_data)
  )
}

dynamic_df <- bind_rows(dynamic_rows)
print(dynamic_df)
fwrite(dynamic_df, file.path(out_dir, "borusyak_activity_dynamic_effects.csv"))
```

# Activity Event-Study Plot

```{r activity-event-study, fig.width=11, fig.height=3.4}
dynamic_df$outcome_label <- factor(
  dynamic_df$outcome_label,
  levels = outcome_definitions$outcome_label
)

activity_plot <- ggplot(
  dynamic_df,
  aes(x = event_time, y = percent_change)
) +
  geom_point(
    data = subset(dynamic_df, is_significant),
    size = 1.8,
    shape = 19
  ) +
  geom_point(
    data = subset(dynamic_df, !is_significant),
    size = 1.8,
    shape = 21,
    fill = "transparent"
  ) +
  geom_errorbar(
    aes(ymin = percent_conf_low, ymax = percent_conf_high),
    width = 0.35
  ) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = -0.5, linetype = "dashed") +
  scale_x_continuous(breaks = -6:6) +
  coord_cartesian(xlim = c(-6.5, 6.5)) +
  facet_wrap(~ outcome_label, scales = "free_y", nrow = 1) +
  labs(
    title = "Borusyak DiD Activity Check",
    subtitle = "Strict AGC changed-block panel; outcomes limited to commits and lines added",
    x = "Months Relative to First Observed Cursor Adoption",
    y = "Estimated Change (%)",
    caption = paste(
      "Outcomes are log1p transformed. Percent effects use exp(beta) - 1.",
      "Filled points indicate that the confidence interval excludes zero."
    )
  ) +
  theme_minimal() +
  theme(
    panel.grid.minor = element_blank(),
    plot.caption = element_text(hjust = 0.5, size = 8)
  )

print(activity_plot)

ggsave(
  filename = file.path(
    out_dir,
    "dynamic_effects_borusyak_activity_commits_lines_added.pdf"
  ),
  plot = activity_plot,
  width = 11,
  height = 3.4,
  device = CairoPDF,
  family = "DejaVu Sans"
)
```

# Interpretation

The activity outcomes are retained from the strict matched repository-month
panel. They are separate from the AGC changed-block outcome:

- commits measure monthly repository activity;
- lines added measure monthly code-production volume; and
- the AGC changed-block ratio measures the structural classification share
  among newly added or structurally modified top-level blocks.

A successful activity check does not validate the AGC treatment effect by
itself. It verifies that the same strict panel still produces interpretable
Cursor-adoption estimates for the original velocity outcomes.

# Session Information

```{r session-info}
sessionInfo()
```
