---
title: "Diff-in-Diff Borusyak: SonarQube Quality Outcomes"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = TRUE, message = TRUE)
options(bitmapType = "cairo")

project_root <- Sys.getenv("PROJECT_ROOT", unset = normalizePath(".", mustWork = TRUE))
panel_path <- Sys.getenv("PANEL_PATH", unset = "")
out_dir <- Sys.getenv("OUT_DIR", unset = "")
panel_label <- Sys.getenv("PANEL_LABEL", unset = "panel")

if (panel_path == "") {
  stop("PANEL_PATH environment variable is required.")
}

if (out_dir == "") {
  out_dir <- file.path(project_root, "tmp_jsts_test/data/jsts_did_final/quality_did_borusyak", panel_label)
}

dir.create(out_dir, recursive = TRUE, showWarnings = FALSE)
````

# Purpose

This notebook runs Borusyak imputation DiD analysis for SonarQube quality outcomes using the JS/TS run9 quality DiD input files.

The input is expected to come from:

```text
run9c: merge SonarQube metrics into DiD panels
run9d: check merged SonarQube panels
run9e: prepare quality DiD input and complete-case files
run9f: run Borusyak quality DiD analysis
```

The main quality outcomes are:

```text
log_static_analysis_warnings
log_duplicate_line_density
log_code_complexity
```

# Load Packages and Helper Functions

```{r load-packages}
library(data.table)
library(dplyr)
library(ggplot2)
library(didimputation)

helper_path <- file.path(project_root, "proc_r/diff_in_diff_borusyak_helpers.R")

if (!file.exists(helper_path)) {
  stop("Helper file not found: ", helper_path)
}

source(helper_path)
```

# Load Quality Panel

```{r load-panel}
cat("Project root:", project_root, "\n")
cat("Panel label:", panel_label, "\n")
cat("Panel path:", panel_path, "\n")
cat("Output dir:", out_dir, "\n")

if (!file.exists(panel_path)) {
  stop("Panel file not found: ", panel_path)
}

panel_raw <- fread(panel_path)

required_cols <- c(
  "repo_name",
  "time",
  "event",
  "dataset_source",
  "ever_treated",
  "post_event",
  "time_to_event",
  "is_treatment",
  "analysis_ready_quality_did",
  "static_analysis_warnings",
  "log_static_analysis_warnings",
  "duplicate_line_density",
  "code_complexity",
  "log_code_complexity",
  "ncloc",
  "log_ncloc"
)

missing_cols <- setdiff(required_cols, names(panel_raw))
if (length(missing_cols) > 0) {
  stop("Missing required columns: ", paste(missing_cols, collapse = ", "))
}

cat("Loaded rows:", nrow(panel_raw), "\n")
cat("Loaded repos:", uniqueN(panel_raw$repo_name), "\n")
cat("Months:", min(panel_raw$time), "to", max(panel_raw$time), "\n")
```

# Panel Sanity Checks

```{r panel-checks}
panel_checks <- data.frame(
  check = c(
    "panel_label",
    "rows",
    "repos",
    "treatment_rows",
    "control_rows",
    "treated_repos",
    "control_repos",
    "control_post_event_sum",
    "treated_post_rows",
    "post_event_mismatch_rows",
    "analysis_ready_quality_did_rows",
    "static_analysis_warnings_nonmissing",
    "duplicate_line_density_nonmissing",
    "code_complexity_nonmissing",
    "sonarqube_latest_commit_missing",
    "sonarqube_any_raw_metric_missing_sum",
    "sonarqube_all_raw_metrics_missing_sum",
    "sonarqube_ncloc_zero_sum",
    "sonarqube_quality_outcomes_complete_sum"
  ),
  value = c(
    panel_label,
    nrow(panel_raw),
    uniqueN(panel_raw$repo_name),
    sum(panel_raw$dataset_source == "treatment", na.rm = TRUE),
    sum(panel_raw$dataset_source == "control", na.rm = TRUE),
    uniqueN(panel_raw[ever_treated == 1, repo_name]),
    uniqueN(panel_raw[ever_treated == 0, repo_name]),
    sum(panel_raw[ever_treated == 0, post_event], na.rm = TRUE),
    sum(panel_raw[ever_treated == 1, post_event], na.rm = TRUE),
    sum(
      panel_raw$ever_treated == 1 &
        !is.na(panel_raw$time_to_event) &
        ((panel_raw$time_to_event >= 0) != (panel_raw$post_event == 1)),
      na.rm = TRUE
    ),
    sum(panel_raw$analysis_ready_quality_did, na.rm = TRUE),
    sum(!is.na(panel_raw$static_analysis_warnings)),
    sum(!is.na(panel_raw$duplicate_line_density)),
    sum(!is.na(panel_raw$code_complexity)),
    if ("sonarqube_latest_commit" %in% names(panel_raw)) sum(is.na(panel_raw$sonarqube_latest_commit)) else NA,
    if ("sonarqube_any_raw_metric_missing" %in% names(panel_raw)) sum(panel_raw$sonarqube_any_raw_metric_missing, na.rm = TRUE) else NA,
    if ("sonarqube_all_raw_metrics_missing" %in% names(panel_raw)) sum(panel_raw$sonarqube_all_raw_metrics_missing, na.rm = TRUE) else NA,
    if ("sonarqube_ncloc_zero" %in% names(panel_raw)) sum(panel_raw$sonarqube_ncloc_zero, na.rm = TRUE) else NA,
    if ("sonarqube_quality_outcomes_complete" %in% names(panel_raw)) sum(panel_raw$sonarqube_quality_outcomes_complete, na.rm = TRUE) else NA
  )
)

print(panel_checks)

fwrite(
  panel_checks,
  file.path(out_dir, "borusyak_quality_panel_checks.csv")
)
```

# Prepare Data for Borusyak Estimator

```{r prepare-data}
panel_data <- copy(panel_raw)

panel_data <- panel_data[analysis_ready_quality_did == 1]

panel_data[, repo_name_str := repo_name]
panel_data[, repo_name := as.numeric(factor(repo_name))]

panel_data[, time := as.integer(gsub("-", "", as.character(time)))]

event_chr <- as.character(panel_data$event)
event_chr[event_chr %in% c("", "NA", "NaN", "NULL", "None")] <- NA_character_

panel_data[, event := suppressWarnings(as.integer(gsub("-", "", event_chr)))]
panel_data[is.na(event), event := 0L]

# Keep the same major adoption cohort window used in the Cursor study:
# Controls have event = 0. Treated cohorts are retained from 2024-08 to 2025-03.
panel_data <- panel_data[
  event < 202401 |
    (event > 202407 & event <= 202503)
]

panel_data[, event := as.integer(event)]
panel_data[, treated := ifelse(event > 0, 1, 0)]

# Create log outcome for duplicate line density.
panel_data[, log_duplicate_line_density := log1p(duplicate_line_density)]

# Create first-stage covariates.
if ("contributors" %in% names(panel_data)) {
  panel_data[, contributors_log := log1p(contributors)]
}

if (!"log_ncloc" %in% names(panel_data)) {
  panel_data[, log_ncloc := log1p(ncloc)]
}

cat("Rows after readiness and cohort filtering:", nrow(panel_data), "\n")
cat("Treated repos:", uniqueN(panel_data[treated == 1, repo_name]), "\n")
cat("Control repos:", uniqueN(panel_data[treated == 0, repo_name]), "\n")

quality_summary <- panel_data[, .(
  rows = .N,
  repos = uniqueN(repo_name),
  mean_log_static_warnings = mean(log_static_analysis_warnings, na.rm = TRUE),
  mean_log_duplicate_line_density = mean(log_duplicate_line_density, na.rm = TRUE),
  mean_log_code_complexity = mean(log_code_complexity, na.rm = TRUE),
  mean_log_ncloc = mean(log_ncloc, na.rm = TRUE)
), by = dataset_source]

print(quality_summary)

fwrite(
  quality_summary,
  file.path(out_dir, "borusyak_quality_input_summary.csv")
)
```

# Outcomes and First Stage

```{r outcomes}
outcome_vars <- c(
  "log_static_analysis_warnings",
  "log_duplicate_line_density",
  "log_code_complexity"
)

outcome_names <- c(
  "Static Analysis Warnings",
  "Duplicate Line Density",
  "Code Complexity"
)

covariates <- c()

if ("contributors_log" %in% names(panel_data)) {
  covariates <- c(covariates, "contributors_log")
}

if ("log_ncloc" %in% names(panel_data)) {
  covariates <- c(covariates, "log_ncloc")
}

if (length(covariates) == 0) {
  first_stage_rhs <- "1"
} else {
  first_stage_rhs <- paste(covariates, collapse = " + ")
}

first_stage_formula <- as.formula(
  paste0("~ ", first_stage_rhs, " | repo_name + time")
)

cat("Outcomes:\n")
print(data.frame(outcome = outcome_vars, label = outcome_names))

cat("\nFirst-stage formula:\n")
print(first_stage_formula)
```

# Static Borusyak Effects

```{r static-effects}
static_results <- list()
static_errors <- list()

for (var in outcome_vars) {
  cat("Running static Borusyak model for:", var, "\n")

  static_results[[var]] <- tryCatch(
    run_borusyak_static(
      data = panel_data,
      outcome_var = var,
      first_stage_formula = first_stage_formula
    ),
    error = function(e) {
      static_errors[[var]] <<- conditionMessage(e)
      NULL
    }
  )
}

static_df <- bind_rows(lapply(outcome_vars, function(v) {
  if (is.null(static_results[[v]])) {
    return(data.frame(
      outcome = v,
      estimate = NA_real_,
      std_error = NA_real_,
      conf_low = NA_real_,
      conf_high = NA_real_,
      p_value = NA_real_
    ))
  }

  extract_static_result(static_results[[v]], v)
}))

static_df$outcome_label <- outcome_names[match(static_df$outcome, outcome_vars)]
static_df$panel <- panel_label

print(static_df)

fwrite(
  static_df,
  file.path(out_dir, "borusyak_quality_static_effects.csv")
)

if (length(static_errors) > 0) {
  static_error_df <- data.frame(
    panel = panel_label,
    outcome = names(static_errors),
    error = unlist(static_errors),
    row.names = NULL
  )

  print(static_error_df)

  fwrite(
    static_error_df,
    file.path(out_dir, "borusyak_quality_static_errors.csv")
  )
}
```

# Dynamic Borusyak Effects

```{r dynamic-effects}
dynamic_results <- list()
dynamic_errors <- list()

for (var in outcome_vars) {
  cat("Running dynamic Borusyak model for:", var, "\n")

  dynamic_results[[var]] <- tryCatch(
    run_borusyak_dynamic(
      data = panel_data,
      outcome_var = var,
      first_stage_formula = first_stage_formula,
      horizon = -6:6,
      pretrends = -6:-2
    ),
    error = function(e) {
      dynamic_errors[[var]] <<- conditionMessage(e)
      NULL
    }
  )
}

dynamic_df <- bind_rows(lapply(seq_along(outcome_vars), function(i) {
  v <- outcome_vars[i]

  if (is.null(dynamic_results[[v]])) {
    return(data.frame(
      outcome = v,
      outcome_label = outcome_names[i],
      time = integer(),
      estimate = numeric(),
      std_error = numeric(),
      conf_low = numeric(),
      conf_high = numeric(),
      p_value = numeric(),
      significant = logical()
    ))
  }

  extract_dynamic_result(
    dynamic_results[[v]],
    outcome = v,
    outcome_label = outcome_names[i]
  )
}))

if (nrow(dynamic_df) > 0) {
  dynamic_df$panel <- panel_label
}

print(dynamic_df)

fwrite(
  dynamic_df,
  file.path(out_dir, "borusyak_quality_dynamic_effects.csv")
)

if (length(dynamic_errors) > 0) {
  dynamic_error_df <- data.frame(
    panel = panel_label,
    outcome = names(dynamic_errors),
    error = unlist(dynamic_errors),
    row.names = NULL
  )

  print(dynamic_error_df)

  fwrite(
    dynamic_error_df,
    file.path(out_dir, "borusyak_quality_dynamic_errors.csv")
  )
}
```

# Dynamic Plot

```{r dynamic-plot, fig.width=9, fig.height=3.5}
if (nrow(dynamic_df) > 0) {
  dynamic_df$outcome_label <- factor(dynamic_df$outcome_label, levels = outcome_names)

  p <- ggplot(dynamic_df, aes(x = time, y = estimate)) +
    geom_errorbar(
      data = subset(dynamic_df, significant %in% TRUE),
      aes(ymin = conf_low, ymax = conf_high),
      width = 0.4,
      linetype = "solid"
    ) +
    geom_errorbar(
      data = subset(dynamic_df, !(significant %in% TRUE)),
      aes(ymin = conf_low, ymax = conf_high),
      width = 0.4,
      linetype = "dotted"
    ) +
    geom_point(
      data = subset(dynamic_df, significant %in% TRUE),
      shape = 19,
      size = 1.7
    ) +
    geom_point(
      data = subset(dynamic_df, !(significant %in% TRUE)),
      shape = 21,
      fill = "transparent",
      size = 1.7
    ) +
    geom_hline(yintercept = 0, linetype = "dashed") +
    geom_vline(xintercept = -0.5, linetype = "dashed") +
    scale_x_continuous(breaks = -6:6) +
    coord_cartesian(xlim = c(-6.5, 6.5)) +
    facet_wrap(~ outcome_label, scales = "free_y", nrow = 1) +
    labs(
      title = paste("Borusyak Quality DiD:", panel_label),
      subtitle = "JS/TS quality DiD input from run9e complete-case panel",
      x = "Months Relative to Cursor Adoption",
      y = "Treatment Effect",
      caption = "Filled dots: CI excludes 0. Hollow dots: CI includes 0."
    ) +
    theme_minimal() +
    theme(
      panel.grid.minor = element_blank(),
      plot.caption = element_text(hjust = 0.5, size = 8)
    )

  print(p)

  ggsave(
    filename = file.path(out_dir, "dynamic_effects_borusyak_quality.pdf"),
    plot = p,
    width = 9,
    height = 3.5
  )
} else {
  cat("No dynamic effects to plot.\n")
}
```

# Metadata

```{r metadata}
metadata <- data.frame(
  key = c(
    "script",
    "helper_file",
    "panel_label",
    "panel_path",
    "out_dir",
    "outcomes",
    "covariates",
    "estimator",
    "purpose",
    "input_source",
    "interpretation_note"
  ),
  value = c(
    "proc_r/DiffInDiffBorusyak_quality_v2.Rmd",
    "proc_r/diff_in_diff_borusyak_helpers.R",
    panel_label,
    panel_path,
    out_dir,
    paste(outcome_vars, collapse = ", "),
    first_stage_rhs,
    "Borusyak imputation via didimputation::did_imputation",
    "Run Borusyak DiD for JS/TS SonarQube quality outcomes",
    "run9e complete-case quality DiD input",
    "Use main panel as primary analysis and other panels as robustness checks"
  )
)

print(metadata)

fwrite(
  metadata,
  file.path(out_dir, "borusyak_quality_metadata.csv")
)
```

# Session Info

```{r session-info}
sessionInfo()
```

