---
title: "Diff-in-Diff Borusyak: AGC Changed-Block Outcomes"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
params:
  panel_file: "repo_python/run-py-4a/strict/panel_event_monthly_agc_changed_block_py.csv"
  validation_summary_file: "repo_python/tmp/run-py-4b/strict/agc_changed_block_panel_validation_summary.json"
  helper_file: "proc_r/diff_in_diff_borusyak_helpers.R"
  out_dir: "repo_python/run-py-4c/strict"
  panel_label: "strict"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = TRUE, message = TRUE)
options(bitmapType = "cairo")

project_root <- Sys.getenv("PROJECT_ROOT", unset = normalizePath(".", mustWork = TRUE))
project_root <- normalizePath(project_root, mustWork = TRUE)

resolve_project_path <- function(path_value) {
  if (is.null(path_value) || identical(path_value, "")) {
    return("")
  }

  if (grepl("^/", path_value)) {
    return(normalizePath(path_value, mustWork = FALSE))
  }

  normalizePath(file.path(project_root, path_value), mustWork = FALSE)
}

panel_path <- resolve_project_path(params$panel_file)
validation_summary_path <- resolve_project_path(params$validation_summary_file)
helper_path <- resolve_project_path(params$helper_file)
out_dir <- resolve_project_path(params$out_dir)
panel_label <- as.character(params$panel_label)

dir.create(out_dir, recursive = TRUE, showWarnings = FALSE)
```

# Purpose

This notebook estimates the effect of observed Cursor adoption on the repository-month share of AI-generated-like code among newly added or structurally modified top-level Python function and class blocks. It uses the Borusyak et al. imputation difference-in-differences estimator.

The primary flow-based outcome is:

\[
\text{AGC changed-block ratio}_{it}
=
\frac{\text{changed AGC blocks}_{it}}
{\text{changed AGC blocks}_{it}+\text{changed HWC blocks}_{it}}
\]

where:

- **AGC** means AI likely generated code.
- **HWC** means Human likely written code.
- Changed blocks include only newly added or structurally modified current top-level blocks.
- Unchanged blocks, moved-but-structurally-unchanged blocks, and deleted blocks are excluded.

The stock-based analysis measures the accumulated structural composition of each repository snapshot and is retained as a baseline analysis. This changed-block analysis focuses on current-period code flow to reduce dilution from unchanged legacy code.

The detector outcome captures structural patterns associated with AI-generated code. It does not establish the actual provenance of individual blocks or identify which AI tool generated or assisted with them.

The primary estimand is the average change in the repository-month AGC changed-block ratio after first observed Cursor adoption, relative to contemporaneous changes in matched repositories with no observed Cursor adoption during the study period.

# Load Packages and Helper Functions

```{r load-packages}
library(data.table)
library(dplyr)
library(ggplot2)
library(didimputation)
library(jsonlite)

if (!file.exists(helper_path)) {
  stop("Borusyak helper file not found: ", helper_path)
}

source(helper_path)
```

# Utility Functions

```{r utility-functions}
normalize_yyyymm <- function(x) {
  x <- as.character(x)
  x[x %in% c("", "NA", "NaN", "NULL", "None")] <- NA_character_
  x <- gsub("-", "", x)
  suppressWarnings(as.integer(x))
}

yyyymm_to_month_id <- function(x) {
  x <- as.integer(x)
  year <- x %/% 100L
  month <- x %% 100L

  out <- year * 12L + month
  out[is.na(x) | month < 1L | month > 12L] <- NA_integer_
  out
}

require_columns <- function(data, required, label) {
  missing <- setdiff(required, names(data))
  if (length(missing) > 0) {
    stop(label, " missing required columns: ", paste(missing, collapse = ", "))
  }
}

numeric_if_present <- function(data, columns) {
  for (column_name in intersect(columns, names(data))) {
    set(
      data,
      j = column_name,
      value = suppressWarnings(as.numeric(data[[column_name]]))
    )
  }

  invisible(data)
}

safe_ratio <- function(numerator, denominator) {
  out <- rep(NA_real_, length(denominator))
  valid <- !is.na(numerator) & !is.na(denominator) & denominator > 0
  out[valid] <- numerator[valid] / denominator[valid]
  out
}

count_mismatch <- function(left, right, tolerance = 1e-12) {
  comparable <- !is.na(left) & !is.na(right)
  sum(comparable & abs(left - right) > tolerance)
}

empty_model_error_table <- function() {
  data.frame(
    panel = character(),
    specification = character(),
    outcome = character(),
    model_type = character(),
    error = character(),
    stringsAsFactors = FALSE
  )
}

build_first_stage_formula <- function(specification) {
  if (identical(specification, "unadjusted")) {
    return(~ 1 | repo_id + time_id)
  }

  ~ age_log + ncloc_model + contributors_log + stars_log + issues_log |
    repo_id + time_id
}
```

# Validate the Upstream Input

```{r validate-upstream}
cat("Project root:", project_root, "\n")
cat("Panel path:", panel_path, "\n")
cat("Validation summary:", validation_summary_path, "\n")
cat("Output directory:", out_dir, "\n")
cat("Panel label:", panel_label, "\n")

if (!file.exists(panel_path)) {
  stop("AGC changed-block panel not found: ", panel_path)
}

if (!file.exists(validation_summary_path)) {
  stop("run-py-4b validation summary not found: ", validation_summary_path)
}

validation_summary <- jsonlite::fromJSON(validation_summary_path)

if (is.null(validation_summary$status) || validation_summary$status != "PASS") {
  stop(
    "run-py-4b validation status must be PASS. Found: ",
    validation_summary$status
  )
}

if (!is.null(validation_summary$checks_failed) &&
    as.integer(validation_summary$checks_failed) != 0L) {
  stop(
    "run-py-4b validation reports failed checks: ",
    validation_summary$checks_failed
  )
}

cat("Validated upstream rows:", validation_summary$panel_rows, "\n")
cat("Validated upstream repositories:", validation_summary$repositories, "\n")
cat("Validated changed blocks:", validation_summary$changed_top_level_blocks, "\n")
cat("Validated ratio rows:", validation_summary$repo_months_with_primary_ratio, "\n")
cat("Validated upstream checks:", validation_summary$checks_passed,
    "/", validation_summary$checks_total, "\n")
```

# Load and Normalize the Changed-Block Panel

```{r load-panel}
panel_raw <- fread(panel_path)

required_columns <- c(
  "repo_name",
  "time",
  "dataset_source",
  "event",
  "post_event",
  "time_to_event",
  "is_treatment",
  "contributors",
  "stars",
  "issues",
  "age",
  "ncloc_paper",
  "ncloc_python_snapshot",
  "changed_top_level_blocks",
  "changed_agc_top_level_blocks",
  "changed_hwc_top_level_blocks",
  "agc_changed_top_level_block_ratio",
  "added_top_level_blocks",
  "added_agc_top_level_blocks",
  "added_hwc_top_level_blocks",
  "agc_added_top_level_block_ratio",
  "modified_top_level_blocks",
  "modified_agc_top_level_blocks",
  "modified_hwc_top_level_blocks",
  "agc_modified_top_level_block_ratio",
  "changed_function_blocks",
  "changed_agc_function_blocks",
  "changed_hwc_function_blocks",
  "agc_changed_function_block_ratio",
  "changed_class_blocks",
  "changed_agc_class_blocks",
  "changed_hwc_class_blocks",
  "agc_changed_class_block_ratio"
)

require_columns(panel_raw, required_columns, "AGC changed-block panel")

numeric_columns <- setdiff(required_columns, c(
  "repo_name",
  "time",
  "dataset_source",
  "event"
))
numeric_if_present(panel_raw, numeric_columns)

panel_raw[, time_yyyymm := normalize_yyyymm(time)]
panel_raw[, event_yyyymm := normalize_yyyymm(event)]
panel_raw[dataset_source == "control", event_yyyymm := 0L]

panel_raw[, time_id := yyyymm_to_month_id(time_yyyymm)]
panel_raw[, event_id := fifelse(
  dataset_source == "control",
  0L,
  yyyymm_to_month_id(event_yyyymm)
)]

panel_raw[, repo_name_str := repo_name]
panel_raw[, repo_id := as.integer(factor(repo_name_str))]
panel_raw[, ever_treated := as.integer(dataset_source == "treatment")]
panel_raw[, analysis_group := fifelse(
  dataset_source == "control",
  "control",
  fifelse(post_event == 1, "treatment_post", "treatment_pre")
)]

panel_raw[, age_log := fifelse(!is.na(age) & age >= 0, log1p(age), NA_real_)]
panel_raw[, contributors_log := fifelse(
  !is.na(contributors) & contributors >= 0,
  log1p(contributors),
  NA_real_
)]
panel_raw[, stars_log := fifelse(
  !is.na(stars) & stars >= 0,
  log1p(stars),
  NA_real_
)]
panel_raw[, issues_log := fifelse(
  !is.na(issues) & issues >= 0,
  log1p(issues),
  NA_real_
)]

cat("Loaded rows:", nrow(panel_raw), "\n")
cat("Loaded repositories:", uniqueN(panel_raw$repo_name), "\n")
cat("Treatment rows:", sum(panel_raw$dataset_source == "treatment"), "\n")
cat("Control rows:", sum(panel_raw$dataset_source == "control"), "\n")
cat("Primary ratio rows:", sum(!is.na(panel_raw$agc_changed_top_level_block_ratio)), "\n")
cat("Calendar range:", min(panel_raw$time, na.rm = TRUE), "to",
    max(panel_raw$time, na.rm = TRUE), "\n")
```

# Panel and Outcome Sanity Checks

```{r panel-checks}
key_columns <- c("repo_name", "time", "dataset_source")
duplicate_keys <- duplicated(panel_raw, by = key_columns)

recomputed_time_to_event <- rep(NA_real_, nrow(panel_raw))
treated_idx <- panel_raw$dataset_source == "treatment"
recomputed_time_to_event[treated_idx] <-
  panel_raw$time_id[treated_idx] - panel_raw$event_id[treated_idx]

changed_count_mismatch <- count_mismatch(
  panel_raw$changed_top_level_blocks,
  panel_raw$changed_agc_top_level_blocks + panel_raw$changed_hwc_top_level_blocks
)
changed_scope_mismatch <- count_mismatch(
  panel_raw$changed_top_level_blocks,
  panel_raw$added_top_level_blocks + panel_raw$modified_top_level_blocks
)
changed_agc_scope_mismatch <- count_mismatch(
  panel_raw$changed_agc_top_level_blocks,
  panel_raw$added_agc_top_level_blocks + panel_raw$modified_agc_top_level_blocks
)
changed_hwc_scope_mismatch <- count_mismatch(
  panel_raw$changed_hwc_top_level_blocks,
  panel_raw$added_hwc_top_level_blocks + panel_raw$modified_hwc_top_level_blocks
)
changed_kind_mismatch <- count_mismatch(
  panel_raw$changed_top_level_blocks,
  panel_raw$changed_function_blocks + panel_raw$changed_class_blocks
)
changed_agc_kind_mismatch <- count_mismatch(
  panel_raw$changed_agc_top_level_blocks,
  panel_raw$changed_agc_function_blocks + panel_raw$changed_agc_class_blocks
)
changed_hwc_kind_mismatch <- count_mismatch(
  panel_raw$changed_hwc_top_level_blocks,
  panel_raw$changed_hwc_function_blocks + panel_raw$changed_hwc_class_blocks
)

primary_ratio_recomputed <- safe_ratio(
  panel_raw$changed_agc_top_level_blocks,
  panel_raw$changed_top_level_blocks
)
function_ratio_recomputed <- safe_ratio(
  panel_raw$changed_agc_function_blocks,
  panel_raw$changed_function_blocks
)
class_ratio_recomputed <- safe_ratio(
  panel_raw$changed_agc_class_blocks,
  panel_raw$changed_class_blocks
)

panel_checks <- data.frame(
  check = c(
    "panel_label",
    "rows",
    "repositories",
    "treatment_rows",
    "control_rows",
    "treatment_repositories",
    "control_repositories",
    "duplicate_keys",
    "time_id_missing",
    "treatment_event_id_missing",
    "control_event_id_nonzero",
    "is_treatment_post_event_mismatch",
    "time_to_event_mismatch",
    "changed_agc_plus_hwc_mismatch",
    "changed_added_plus_modified_mismatch",
    "changed_agc_added_plus_modified_mismatch",
    "changed_hwc_added_plus_modified_mismatch",
    "changed_function_plus_class_mismatch",
    "changed_agc_function_plus_class_mismatch",
    "changed_hwc_function_plus_class_mismatch",
    "primary_ratio_mismatch",
    "function_ratio_mismatch",
    "class_ratio_mismatch",
    "primary_ratio_outside_unit_interval",
    "function_ratio_outside_unit_interval",
    "class_ratio_outside_unit_interval",
    "primary_ratio_rows",
    "ncloc_paper_nonmissing",
    "ncloc_python_snapshot_nonmissing",
    "upstream_validation_status",
    "upstream_checks_failed"
  ),
  value = c(
    panel_label,
    nrow(panel_raw),
    uniqueN(panel_raw$repo_name),
    sum(panel_raw$dataset_source == "treatment"),
    sum(panel_raw$dataset_source == "control"),
    uniqueN(panel_raw[dataset_source == "treatment", repo_name]),
    uniqueN(panel_raw[dataset_source == "control", repo_name]),
    sum(duplicate_keys),
    sum(is.na(panel_raw$time_id)),
    sum(panel_raw$dataset_source == "treatment" & is.na(panel_raw$event_id)),
    sum(panel_raw$dataset_source == "control" & panel_raw$event_id != 0L),
    sum(panel_raw$is_treatment != panel_raw$post_event, na.rm = TRUE),
    sum(
      panel_raw$dataset_source == "treatment" &
        !is.na(panel_raw$time_to_event) &
        panel_raw$time_to_event != recomputed_time_to_event,
      na.rm = TRUE
    ),
    changed_count_mismatch,
    changed_scope_mismatch,
    changed_agc_scope_mismatch,
    changed_hwc_scope_mismatch,
    changed_kind_mismatch,
    changed_agc_kind_mismatch,
    changed_hwc_kind_mismatch,
    count_mismatch(panel_raw$agc_changed_top_level_block_ratio, primary_ratio_recomputed),
    count_mismatch(panel_raw$agc_changed_function_block_ratio, function_ratio_recomputed),
    count_mismatch(panel_raw$agc_changed_class_block_ratio, class_ratio_recomputed),
    sum(
      !is.na(panel_raw$agc_changed_top_level_block_ratio) &
        (panel_raw$agc_changed_top_level_block_ratio < 0 |
           panel_raw$agc_changed_top_level_block_ratio > 1)
    ),
    sum(
      !is.na(panel_raw$agc_changed_function_block_ratio) &
        (panel_raw$agc_changed_function_block_ratio < 0 |
           panel_raw$agc_changed_function_block_ratio > 1)
    ),
    sum(
      !is.na(panel_raw$agc_changed_class_block_ratio) &
        (panel_raw$agc_changed_class_block_ratio < 0 |
           panel_raw$agc_changed_class_block_ratio > 1)
    ),
    sum(!is.na(panel_raw$agc_changed_top_level_block_ratio)),
    sum(!is.na(panel_raw$ncloc_paper)),
    sum(!is.na(panel_raw$ncloc_python_snapshot)),
    validation_summary$status,
    validation_summary$checks_failed
  ),
  stringsAsFactors = FALSE
)

print(panel_checks)

fwrite(
  panel_checks,
  file.path(out_dir, "borusyak_agc_changed_block_panel_checks.csv")
)

hard_failure_checks <- c(
  sum(duplicate_keys),
  sum(is.na(panel_raw$time_id)),
  sum(panel_raw$dataset_source == "treatment" & is.na(panel_raw$event_id)),
  sum(panel_raw$dataset_source == "control" & panel_raw$event_id != 0L),
  sum(panel_raw$is_treatment != panel_raw$post_event, na.rm = TRUE),
  changed_count_mismatch,
  changed_scope_mismatch,
  changed_agc_scope_mismatch,
  changed_hwc_scope_mismatch,
  changed_kind_mismatch,
  changed_agc_kind_mismatch,
  changed_hwc_kind_mismatch,
  count_mismatch(panel_raw$agc_changed_top_level_block_ratio, primary_ratio_recomputed),
  count_mismatch(panel_raw$agc_changed_function_block_ratio, function_ratio_recomputed),
  count_mismatch(panel_raw$agc_changed_class_block_ratio, class_ratio_recomputed)
)

if (any(hard_failure_checks != 0)) {
  stop(
    "AGC changed-block panel sanity checks failed. See ",
    "borusyak_agc_changed_block_panel_checks.csv."
  )
}

if (!is.null(validation_summary$panel_rows) &&
    nrow(panel_raw) != as.integer(validation_summary$panel_rows)) {
  stop("Panel row count differs from the run-py-4b validation summary.")
}

if (!is.null(validation_summary$repo_months_with_primary_ratio) &&
    sum(!is.na(panel_raw$agc_changed_top_level_block_ratio)) !=
      as.integer(validation_summary$repo_months_with_primary_ratio)) {
  stop("Primary ratio row count differs from the run-py-4b validation summary.")
}
```

# Ratio Coverage Diagnostics

```{r coverage-diagnostics}
outcome_definitions <- data.frame(
  outcome = c(
    "agc_changed_top_level_block_ratio",
    "agc_changed_function_block_ratio",
    "agc_changed_class_block_ratio"
  ),
  outcome_label = c(
    "AGC-Like Changed Top-Level Block Share",
    "AGC-Like Changed Function Block Share",
    "AGC-Like Changed Class Block Share"
  ),
  denominator = c(
    "changed_top_level_blocks",
    "changed_function_blocks",
    "changed_class_blocks"
  ),
  role = c("primary", "robustness", "robustness"),
  stringsAsFactors = FALSE
)

coverage_rows <- list()
for (outcome_index in seq_len(nrow(outcome_definitions))) {
  outcome_var <- outcome_definitions$outcome[outcome_index]
  outcome_label <- outcome_definitions$outcome_label[outcome_index]
  denominator_var <- outcome_definitions$denominator[outcome_index]

  coverage_part <- panel_raw[, .(
    total_rows = .N,
    ratio_rows = sum(!is.na(get(outcome_var))),
    missing_ratio_rows = sum(is.na(get(outcome_var))),
    positive_denominator_rows = sum(get(denominator_var) > 0, na.rm = TRUE),
    zero_denominator_rows = sum(get(denominator_var) == 0, na.rm = TRUE),
    denominator_sum = sum(get(denominator_var), na.rm = TRUE)
  ), by = analysis_group]

  coverage_part[, availability_rate := ratio_rows / total_rows]
  coverage_part[, outcome := outcome_var]
  coverage_part[, outcome_label := outcome_label]
  coverage_rows[[length(coverage_rows) + 1]] <- coverage_part
}

coverage_by_group <- rbindlist(coverage_rows, fill = TRUE)
setcolorder(
  coverage_by_group,
  c(
    "outcome",
    "outcome_label",
    "analysis_group",
    "total_rows",
    "ratio_rows",
    "missing_ratio_rows",
    "availability_rate",
    "positive_denominator_rows",
    "zero_denominator_rows",
    "denominator_sum"
  )
)

print(coverage_by_group)
fwrite(
  coverage_by_group,
  file.path(out_dir, "borusyak_agc_changed_block_ratio_coverage_by_group.csv")
)

coverage_by_event_time <- panel_raw[dataset_source == "treatment", .(
  total_rows = .N,
  primary_ratio_rows = sum(!is.na(agc_changed_top_level_block_ratio)),
  primary_ratio_missing_rows = sum(is.na(agc_changed_top_level_block_ratio)),
  primary_ratio_availability_rate = mean(!is.na(agc_changed_top_level_block_ratio)),
  changed_top_level_blocks = sum(changed_top_level_blocks, na.rm = TRUE)
), by = time_to_event][order(time_to_event)]

print(coverage_by_event_time)
fwrite(
  coverage_by_event_time,
  file.path(out_dir, "borusyak_agc_changed_block_ratio_coverage_by_event_time.csv")
)
```

# Outcomes and Model Specifications

```{r outcomes-and-specifications}
specification_definitions <- data.frame(
  specification = c(
    "unadjusted",
    "paper_ncloc",
    "python_snapshot_ncloc"
  ),
  specification_label = c(
    "Unadjusted",
    "Paper NCLOC",
    "Python Snapshot NCLOC"
  ),
  ncloc_column = c(
    NA_character_,
    "ncloc_paper",
    "ncloc_python_snapshot"
  ),
  stringsAsFactors = FALSE
)

print(outcome_definitions)
print(specification_definitions)
```

# Prepare Common Outcome-Specific Samples

```{r prepare-common-samples}
common_covariates <- c(
  "age_log",
  "contributors_log",
  "stars_log",
  "issues_log",
  "ncloc_paper",
  "ncloc_python_snapshot"
)

common_samples <- list()
sample_summary_rows <- list()

for (outcome_index in seq_len(nrow(outcome_definitions))) {
  outcome_var <- outcome_definitions$outcome[outcome_index]
  outcome_label <- outcome_definitions$outcome_label[outcome_index]
  denominator_var <- outcome_definitions$denominator[outcome_index]
  outcome_role <- outcome_definitions$role[outcome_index]

  available_data <- copy(panel_raw[!is.na(get(outcome_var))])
  required <- c(
    "repo_id",
    "time_id",
    "event_id",
    "dataset_source",
    outcome_var,
    common_covariates
  )

  sample_data <- copy(panel_raw)
  sample_data <- sample_data[complete.cases(sample_data[, ..required])]

  if (nrow(sample_data) == 0) {
    stop("No complete rows remain for outcome: ", outcome_var)
  }

  sample_data[, sample_key := paste(repo_name, time, dataset_source, sep = "|")]
  common_samples[[outcome_var]] <- sample_data

  sample_summary_rows[[length(sample_summary_rows) + 1]] <- data.frame(
    outcome = outcome_var,
    outcome_label = outcome_label,
    role = outcome_role,
    denominator = denominator_var,
    panel_rows = nrow(panel_raw),
    outcome_available_rows = nrow(available_data),
    model_common_sample_rows = nrow(sample_data),
    rows_removed_for_common_covariates = nrow(available_data) - nrow(sample_data),
    repositories = uniqueN(sample_data$repo_id),
    treatment_rows = sum(sample_data$dataset_source == "treatment"),
    control_rows = sum(sample_data$dataset_source == "control"),
    treatment_pre_rows = sum(
      sample_data$dataset_source == "treatment" & sample_data$post_event == 0
    ),
    treatment_post_rows = sum(
      sample_data$dataset_source == "treatment" & sample_data$post_event == 1
    ),
    treatment_repositories = uniqueN(
      sample_data[dataset_source == "treatment", repo_id]
    ),
    control_repositories = uniqueN(
      sample_data[dataset_source == "control", repo_id]
    ),
    min_time = min(sample_data$time),
    max_time = max(sample_data$time),
    changed_blocks_in_sample = sum(sample_data[[denominator_var]], na.rm = TRUE),
    stringsAsFactors = FALSE
  )
}

sample_summary <- bind_rows(sample_summary_rows)
print(sample_summary)

fwrite(
  sample_summary,
  file.path(out_dir, "borusyak_agc_changed_block_sample_by_outcome.csv")
)
```

# Static Borusyak Effects

```{r static-effects}
static_rows <- list()
model_error_rows <- list()

for (outcome_index in seq_len(nrow(outcome_definitions))) {
  outcome_var <- outcome_definitions$outcome[outcome_index]
  outcome_label <- outcome_definitions$outcome_label[outcome_index]
  outcome_role <- outcome_definitions$role[outcome_index]
  base_sample <- common_samples[[outcome_var]]

  for (spec_index in seq_len(nrow(specification_definitions))) {
    specification <- specification_definitions$specification[spec_index]
    specification_label <- specification_definitions$specification_label[spec_index]
    ncloc_column <- specification_definitions$ncloc_column[spec_index]
    first_stage_formula <- build_first_stage_formula(specification)

    model_data <- copy(base_sample)
    if (!is.na(ncloc_column)) {
      model_data[, ncloc_model := get(ncloc_column)]
    }

    cat(
      "Running static Borusyak model:",
      specification,
      "|",
      outcome_var,
      "| rows =",
      nrow(model_data),
      "\n"
    )

    result <- tryCatch(
      run_borusyak_static(
        data = model_data,
        outcome_var = outcome_var,
        first_stage_formula = first_stage_formula,
        idname = "repo_id",
        tname = "time_id",
        gname = "event_id"
      ),
      error = function(e) {
        model_error_rows[[length(model_error_rows) + 1]] <<- data.frame(
          panel = panel_label,
          specification = specification,
          outcome = outcome_var,
          model_type = "static",
          error = conditionMessage(e),
          stringsAsFactors = FALSE
        )
        NULL
      }
    )

    extracted <- extract_static_result(result, outcome_var)
    extracted$panel <- panel_label
    extracted$specification <- specification
    extracted$specification_label <- specification_label
    extracted$ncloc_column <- ifelse(is.na(ncloc_column), "none", ncloc_column)
    extracted$outcome_label <- outcome_label
    extracted$role <- outcome_role
    extracted$sample_rows <- nrow(model_data)
    extracted$sample_repositories <- uniqueN(model_data$repo_id)
    extracted$first_stage_formula <- paste(deparse(first_stage_formula), collapse = " ")
    extracted$estimate_percentage_points <- extracted$estimate * 100
    extracted$conf_low_percentage_points <- extracted$conf_low * 100
    extracted$conf_high_percentage_points <- extracted$conf_high * 100

    static_rows[[length(static_rows) + 1]] <- extracted
  }
}

static_df <- bind_rows(static_rows)
print(static_df)

fwrite(
  static_df,
  file.path(out_dir, "borusyak_agc_changed_block_static_effects.csv")
)
```

# Dynamic Borusyak Effects

```{r dynamic-effects}
dynamic_rows <- list()

for (outcome_index in seq_len(nrow(outcome_definitions))) {
  outcome_var <- outcome_definitions$outcome[outcome_index]
  outcome_label <- outcome_definitions$outcome_label[outcome_index]
  outcome_role <- outcome_definitions$role[outcome_index]
  base_sample <- common_samples[[outcome_var]]

  for (spec_index in seq_len(nrow(specification_definitions))) {
    specification <- specification_definitions$specification[spec_index]
    specification_label <- specification_definitions$specification_label[spec_index]
    ncloc_column <- specification_definitions$ncloc_column[spec_index]
    first_stage_formula <- build_first_stage_formula(specification)

    model_data <- copy(base_sample)
    if (!is.na(ncloc_column)) {
      model_data[, ncloc_model := get(ncloc_column)]
    }

    cat(
      "Running dynamic Borusyak model:",
      specification,
      "|",
      outcome_var,
      "| rows =",
      nrow(model_data),
      "\n"
    )

    result <- tryCatch(
      run_borusyak_dynamic(
        data = model_data,
        outcome_var = outcome_var,
        first_stage_formula = first_stage_formula,
        horizon = -6:6,
        pretrends = -6:-2,
        idname = "repo_id",
        tname = "time_id",
        gname = "event_id"
      ),
      error = function(e) {
        model_error_rows[[length(model_error_rows) + 1]] <<- data.frame(
          panel = panel_label,
          specification = specification,
          outcome = outcome_var,
          model_type = "dynamic",
          error = conditionMessage(e),
          stringsAsFactors = FALSE
        )
        NULL
      }
    )

    extracted <- extract_dynamic_result(
      result,
      outcome = outcome_var,
      outcome_label = outcome_label,
      min_horizon = -6,
      max_horizon = 6
    )

    if (nrow(extracted) > 0) {
      extracted$panel <- panel_label
      extracted$specification <- specification
      extracted$specification_label <- specification_label
      extracted$ncloc_column <- ifelse(is.na(ncloc_column), "none", ncloc_column)
      extracted$role <- outcome_role
      extracted$sample_rows <- nrow(model_data)
      extracted$sample_repositories <- uniqueN(model_data$repo_id)
      extracted$first_stage_formula <- paste(deparse(first_stage_formula), collapse = " ")
      extracted$estimate_percentage_points <- extracted$estimate * 100
      extracted$conf_low_percentage_points <- extracted$conf_low * 100
      extracted$conf_high_percentage_points <- extracted$conf_high * 100

      dynamic_rows[[length(dynamic_rows) + 1]] <- extracted
    }
  }
}

dynamic_df <- bind_rows(dynamic_rows)
print(dynamic_df)

fwrite(
  dynamic_df,
  file.path(out_dir, "borusyak_agc_changed_block_dynamic_effects.csv")
)

model_errors <- if (length(model_error_rows) > 0) {
  bind_rows(model_error_rows)
} else {
  empty_model_error_table()
}

fwrite(
  model_errors,
  file.path(out_dir, "borusyak_agc_changed_block_model_errors.csv")
)

primary_outcome <- "agc_changed_top_level_block_ratio"
primary_errors <- model_errors %>% filter(outcome == primary_outcome)
if (nrow(primary_errors) > 0) {
  print(primary_errors)
  stop(
    "One or more primary changed-block Borusyak models failed. See ",
    "borusyak_agc_changed_block_model_errors.csv."
  )
}

primary_static_success <- static_df %>%
  filter(outcome == primary_outcome, is.finite(estimate)) %>%
  distinct(specification) %>%
  nrow()

primary_dynamic_success <- dynamic_df %>%
  filter(outcome == primary_outcome, is.finite(estimate)) %>%
  distinct(specification) %>%
  nrow()

if (primary_static_success != nrow(specification_definitions)) {
  stop("Not all primary static specifications produced finite estimates.")
}

if (primary_dynamic_success != nrow(specification_definitions)) {
  stop("Not all primary dynamic specifications produced finite estimates.")
}

if (nrow(model_errors) > 0) {
  cat("Robustness-model errors were recorded but primary models succeeded.\n")
  print(model_errors)
}
```

# Pre-Treatment Diagnostics

```{r pretrend-diagnostics}
if (nrow(dynamic_df) > 0) {
  pretrend_summary <- dynamic_df %>%
    filter(time >= -6, time <= -2) %>%
    group_by(
      panel,
      specification,
      specification_label,
      outcome,
      outcome_label,
      role
    ) %>%
    summarise(
      pre_periods_available = n(),
      pre_periods_ci_excludes_zero = sum(significant %in% TRUE, na.rm = TRUE),
      all_preperiod_cis_include_zero = all(!(significant %in% TRUE)),
      max_absolute_pretrend_estimate = max(abs(estimate), na.rm = TRUE),
      max_absolute_pretrend_percentage_points =
        max(abs(estimate_percentage_points), na.rm = TRUE),
      .groups = "drop"
    )
} else {
  pretrend_summary <- data.frame()
}

print(pretrend_summary)

fwrite(
  pretrend_summary,
  file.path(out_dir, "borusyak_agc_changed_block_pretrend_summary.csv")
)
```

# Static Effect Table

```{r static-table}
static_display <- static_df %>%
  select(
    role,
    specification_label,
    outcome_label,
    estimate_percentage_points,
    conf_low_percentage_points,
    conf_high_percentage_points,
    sample_rows,
    sample_repositories,
    note
  ) %>%
  arrange(match(role, c("primary", "robustness")), outcome_label, specification_label)

knitr::kable(
  static_display,
  digits = 3,
  caption = paste(
    "Static Borusyak Effects on AGC Changed-Block Shares",
    "(percentage points)"
  )
)
```

# Coverage Table

```{r coverage-table}
coverage_display <- coverage_by_group %>%
  filter(outcome == "agc_changed_top_level_block_ratio") %>%
  select(
    analysis_group,
    total_rows,
    ratio_rows,
    missing_ratio_rows,
    availability_rate,
    denominator_sum
  ) %>%
  arrange(match(analysis_group, c("control", "treatment_pre", "treatment_post")))

knitr::kable(
  coverage_display,
  digits = 3,
  caption = "Primary Changed-Block Ratio Coverage by Analysis Group"
)
```

# Dynamic Event-Study Plot

```{r dynamic-plot, fig.width=12, fig.height=7}
if (nrow(dynamic_df) > 0) {
  dynamic_plot_data <- copy(as.data.table(dynamic_df))
  dynamic_plot_data[, outcome_label := factor(
    outcome_label,
    levels = outcome_definitions$outcome_label
  )]
  dynamic_plot_data[, specification_label := factor(
    specification_label,
    levels = specification_definitions$specification_label
  )]

  position <- position_dodge(width = 0.45)

  dynamic_plot <- ggplot(
    dynamic_plot_data,
    aes(
      x = time,
      y = estimate_percentage_points,
      color = specification_label,
      group = specification_label
    )
  ) +
    geom_errorbar(
      aes(
        ymin = conf_low_percentage_points,
        ymax = conf_high_percentage_points,
        linetype = significant
      ),
      position = position,
      width = 0.3
    ) +
    geom_point(
      aes(shape = significant),
      position = position,
      size = 1.8
    ) +
    geom_hline(yintercept = 0, linetype = "dashed") +
    geom_vline(xintercept = -0.5, linetype = "dashed") +
    scale_x_continuous(breaks = -6:6) +
    scale_shape_manual(
      values = c("TRUE" = 19, "FALSE" = 1),
      name = "CI excludes zero"
    ) +
    scale_linetype_manual(
      values = c("TRUE" = "solid", "FALSE" = "dotted"),
      name = "CI excludes zero"
    ) +
    facet_wrap(~ outcome_label, scales = "free_y", ncol = 1) +
    labs(
      title = paste("Borusyak AGC Changed-Block DiD:", panel_label),
      subtitle = paste(
        "Common outcome-specific samples;",
        "unadjusted, paper NCLOC, and exact Python snapshot NCLOC"
      ),
      x = "Months Relative to First Observed Cursor Adoption",
      y = "Treatment Effect (percentage points)",
      color = "Specification",
      caption = paste(
        "Outcomes use only newly added or structurally modified current blocks.",
        "Filled points indicate that the confidence interval excludes zero."
      )
    ) +
    theme_minimal() +
    theme(
      panel.grid.minor = element_blank(),
      legend.position = "bottom",
      plot.caption = element_text(hjust = 0.5, size = 8)
    )

  print(dynamic_plot)

  ggsave(
    filename = file.path(
      out_dir,
      "dynamic_effects_borusyak_agc_changed_block.pdf"
    ),
    plot = dynamic_plot,
    width = 12,
    height = 7
  )
} else {
  stop("No dynamic effects are available to plot.")
}
```

# Model Metadata

```{r metadata}
metadata <- data.frame(
  key = c(
    "script",
    "source_notebook",
    "helper_file",
    "panel_label",
    "panel_path",
    "validation_summary_path",
    "validation_status",
    "validation_checks_passed",
    "validation_checks_total",
    "out_dir",
    "outcomes",
    "primary_outcome",
    "specifications",
    "common_model_sample",
    "common_covariates",
    "adjusted_first_stage_formula",
    "unadjusted_first_stage_formula",
    "time_encoding",
    "dynamic_horizon",
    "pretrend_horizon",
    "weighting",
    "outcome_scale",
    "agc_definition",
    "hwc_definition",
    "changed_block_definition",
    "interpretation",
    "stock_baseline",
    "limitation"
  ),
  value = c(
    "proc_r/DiffInDiffBorusyak_AGC_ChangedBlock.Rmd",
    "DiffInDiffBorusyak_AGC.Rmd",
    params$helper_file,
    panel_label,
    panel_path,
    validation_summary_path,
    validation_summary$status,
    validation_summary$checks_passed,
    validation_summary$checks_total,
    out_dir,
    paste(outcome_definitions$outcome, collapse = ", "),
    "agc_changed_top_level_block_ratio",
    paste(specification_definitions$specification, collapse = ", "),
    paste(
      "Each outcome uses one common complete-case sample across all three",
      "specifications so estimates are directly comparable."
    ),
    paste(common_covariates, collapse = ", "),
    paste(
      deparse(build_first_stage_formula("paper_ncloc")),
      collapse = " "
    ),
    paste(
      deparse(build_first_stage_formula("unadjusted")),
      collapse = " "
    ),
    "sequential calendar-month id",
    "-6 through +6 months",
    "-6 through -2 months",
    "unweighted repository-month analysis",
    "proportion; reported as percentage points",
    "AGC = AI likely generated code",
    "HWC = Human likely written code",
    paste(
      "Current top-level functions/classes classified as added or",
      "structurally modified relative to the preceding monthly snapshot;",
      "unchanged, moved-unchanged, and deleted blocks are excluded."
    ),
    paste(
      "Change in the repository-month AGC-like share among newly added or",
      "structurally modified top-level Python function and class blocks",
      "after observed Cursor adoption."
    ),
    paste(
      "The stock-based analysis of accumulated repository snapshots is",
      "retained as a separate baseline estimand."
    ),
    paste(
      "The detector outcome captures structural similarity to AI-generated",
      "code and does not establish block provenance or tool identity."
    )
  ),
  stringsAsFactors = FALSE
)

print(metadata)

fwrite(
  metadata,
  file.path(out_dir, "borusyak_agc_changed_block_model_metadata.csv")
)
```

# Session Info

```{r session-info}
sessionInfo()
```
