---
title: "Diff-in-Diff Borusyak v2: SonarQube Quality Outcomes"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = TRUE, message = TRUE)
options(bitmapType = "cairo")

project_root <- Sys.getenv("PROJECT_ROOT", unset = normalizePath(".", mustWork = TRUE))

panel_path <- file.path(
  project_root,
  "tmp_adoption_test/data/python_did_test/panel_event_monthly_matched_v2_balanced_quality_did_input.csv"
)

out_dir <- file.path(
  project_root,
  "tmp_adoption_test/data/python_did_test/quality_did_borusyak_v2"
)

dir.create(out_dir, recursive = TRUE, showWarnings = FALSE)
```

# Purpose

This notebook runs a small-scale Borusyak imputation DiD analysis for SonarQube quality outcomes.

It uses the balanced repository-month quality panel created from:

```text
Git history activity outcomes
+ SonarQube static-analysis quality metrics
+ treatment/control event-study variables
```

This is a small Python-panel pipeline validation analysis, not the final full-scale causal result.

# Load Packages and Helper Functions

```{r load-packages}
library(data.table)
library(dplyr)
library(ggplot2)
library(didimputation)

source(file.path(project_root, "proc_r/diff_in_diff_borusyak_helpers.R"))
```

# Load Quality Panel

```{r load-panel}
cat("Project root:", project_root, "\n")
cat("Panel path:", panel_path, "\n")
cat("Output dir:", out_dir, "\n")

if (!file.exists(panel_path)) {
  stop("Panel file not found: ", panel_path)
}

panel_raw <- fread(panel_path)

required_cols <- c(
  "repo_name",
  "time",
  "event",
  "dataset_source",
  "ever_treated",
  "post_event",
  "time_to_event",
  "is_treatment",
  "is_treatment_dynamic",
  "contributors",
  "ncloc",
  "log_ncloc",
  "static_analysis_warnings",
  "log_static_analysis_warnings",
  "duplicated_lines_density",
  "cognitive_complexity",
  "log_cognitive_complexity",
  "technical_debt",
  "log_technical_debt",
  "sonarqube_source_less_commit",
  "sonarqube_any_raw_metric_missing"
)

missing_cols <- setdiff(required_cols, names(panel_raw))
if (length(missing_cols) > 0) {
  stop("Missing required columns: ", paste(missing_cols, collapse = ", "))
}

cat("Loaded rows:", nrow(panel_raw), "\n")
cat("Loaded repos:", uniqueN(panel_raw$repo_name), "\n")
cat("Months:", min(panel_raw$time), "to", max(panel_raw$time), "\n")
```

# Panel Sanity Checks

```{r panel-checks}
panel_checks <- data.frame(
  check = c(
    "rows",
    "treated_repos",
    "control_repos",
    "control_post_event_sum",
    "control_dynamic_sum",
    "treated_post_rows",
    "post_event_mismatch_rows",
    "source_less_commit_rows",
    "raw_metric_missing_rows",
    "static_analysis_warnings_nonmissing",
    "duplicated_lines_density_nonmissing",
    "cognitive_complexity_nonmissing"
  ),
  value = c(
    nrow(panel_raw),
    uniqueN(panel_raw[ever_treated == 1, repo_name]),
    uniqueN(panel_raw[ever_treated == 0, repo_name]),
    sum(panel_raw[ever_treated == 0, post_event], na.rm = TRUE),
    sum(panel_raw[ever_treated == 0, is_treatment_dynamic], na.rm = TRUE),
    sum(panel_raw[ever_treated == 1, post_event], na.rm = TRUE),
    sum(
      panel_raw$ever_treated == 1 &
        ((panel_raw$time_to_event >= 0) != (panel_raw$post_event == 1)),
      na.rm = TRUE
    ),
    sum(panel_raw$sonarqube_source_less_commit, na.rm = TRUE),
    sum(panel_raw$sonarqube_any_raw_metric_missing, na.rm = TRUE),
    sum(!is.na(panel_raw$static_analysis_warnings)),
    sum(!is.na(panel_raw$duplicated_lines_density)),
    sum(!is.na(panel_raw$cognitive_complexity))
  )
)

print(panel_checks)

fwrite(
  panel_checks,
  file.path(out_dir, "borusyak_quality_v2_panel_checks.csv")
)
```

# Prepare Data for Borusyak Estimator

```{r prepare-data}
panel_data <- copy(panel_raw)

panel_data[, repo_name_str := repo_name]
panel_data[, repo_name := as.numeric(factor(repo_name))]

panel_data[, time := as.integer(gsub("-", "", as.character(time)))]

event_chr <- as.character(panel_data$event)
event_chr[event_chr %in% c("", "NA", "NaN", "NULL", "None")] <- NA_character_

panel_data[, event := suppressWarnings(as.integer(gsub("-", "", event_chr)))]
panel_data[is.na(event), event := 0L]

# Match the original Borusyak notebook cohort-window logic.
# Controls are event = 0. Treatment cohorts are retained from 2024-08 to 2025-03.
panel_data <- panel_data[
  event < 202401 |
    (event > 202407 & event <= 202503)
]

panel_data[, event := as.integer(event)]

# Quality outcomes.
# run6i already created:
#   log_static_analysis_warnings
#   log_cognitive_complexity
#   log_technical_debt
#   log_ncloc
#
# For paper-style log handling, create a log version of duplicated line density.
panel_data[, log_duplicated_lines_density := log(duplicated_lines_density + 1)]

# First-stage covariates.
# contributors comes from Git history. Use log1p as in the activity smoke test.
panel_data[, contributors := log(contributors + 1)]

panel_data[, treated := ifelse(event > 0, 1, 0)]

cat("Rows after cohort filtering:", nrow(panel_data), "\n")
cat("Treated repos:", uniqueN(panel_data[treated == 1, repo_name]), "\n")
cat("Control repos:", uniqueN(panel_data[treated == 0, repo_name]), "\n")

quality_summary <- panel_data[, .(
  rows = .N,
  repos = uniqueN(repo_name),
  mean_log_static_warnings = mean(log_static_analysis_warnings, na.rm = TRUE),
  mean_log_dup_density = mean(log_duplicated_lines_density, na.rm = TRUE),
  mean_log_complexity = mean(log_cognitive_complexity, na.rm = TRUE),
  source_less_rows = sum(sonarqube_source_less_commit, na.rm = TRUE)
), by = dataset_source]

print(quality_summary)

fwrite(
  quality_summary,
  file.path(out_dir, "borusyak_quality_v2_input_summary.csv")
)
```

# Outcomes and First Stage

```{r outcomes}
outcome_vars <- c(
  "log_static_analysis_warnings",
  "log_duplicated_lines_density",
  "log_cognitive_complexity"
)

outcome_names <- c(
  "Static Analysis Warnings",
  "Duplicated Lines Density",
  "Code Complexity"
)

# Small-panel quality first stage.
# This controls for contributor activity and codebase size.
# Full-paper covariates such as age, stars, and issues are not yet included.
first_stage_formula <- ~ contributors + log_ncloc | repo_name + time

cat("Outcomes:\n")
print(data.frame(outcome = outcome_vars, label = outcome_names))

cat("\nFirst-stage formula:\n")
print(first_stage_formula)
```

# Static Borusyak Effects

```{r static-effects}
static_results <- list()
static_errors <- list()

for (var in outcome_vars) {
  cat("Running static Borusyak model for:", var, "\n")

  static_results[[var]] <- tryCatch(
    run_borusyak_static(
      data = panel_data,
      outcome_var = var,
      first_stage_formula = first_stage_formula
    ),
    error = function(e) {
      static_errors[[var]] <<- conditionMessage(e)
      NULL
    }
  )
}

static_df <- bind_rows(lapply(outcome_vars, function(v) {
  extract_static_result(static_results[[v]], v)
}))

static_df$outcome_label <- outcome_names[match(static_df$outcome, outcome_vars)]

print(static_df)

fwrite(
  static_df,
  file.path(out_dir, "borusyak_quality_v2_static_effects.csv")
)

if (length(static_errors) > 0) {
  static_error_df <- data.frame(
    outcome = names(static_errors),
    error = unlist(static_errors),
    row.names = NULL
  )

  print(static_error_df)

  fwrite(
    static_error_df,
    file.path(out_dir, "borusyak_quality_v2_static_errors.csv")
  )
}
```

# Dynamic Borusyak Effects

```{r dynamic-effects}
dynamic_results <- list()
dynamic_errors <- list()

for (var in outcome_vars) {
  cat("Running dynamic Borusyak model for:", var, "\n")

  dynamic_results[[var]] <- tryCatch(
    run_borusyak_dynamic(
      data = panel_data,
      outcome_var = var,
      first_stage_formula = first_stage_formula,
      horizon = -6:6,
      pretrends = -6:-2
    ),
    error = function(e) {
      dynamic_errors[[var]] <<- conditionMessage(e)
      NULL
    }
  )
}

dynamic_df <- bind_rows(lapply(seq_along(outcome_vars), function(i) {
  extract_dynamic_result(
    dynamic_results[[outcome_vars[i]]],
    outcome = outcome_vars[i],
    outcome_label = outcome_names[i]
  )
}))

print(dynamic_df)

fwrite(
  dynamic_df,
  file.path(out_dir, "borusyak_quality_v2_dynamic_effects.csv")
)

if (length(dynamic_errors) > 0) {
  dynamic_error_df <- data.frame(
    outcome = names(dynamic_errors),
    error = unlist(dynamic_errors),
    row.names = NULL
  )

  print(dynamic_error_df)

  fwrite(
    dynamic_error_df,
    file.path(out_dir, "borusyak_quality_v2_dynamic_errors.csv")
  )
}
```

# Dynamic Plot

```{r dynamic-plot, fig.width=9, fig.height=3.5}
if (nrow(dynamic_df) > 0) {
  dynamic_df$outcome_label <- factor(dynamic_df$outcome_label, levels = outcome_names)

  p <- ggplot(dynamic_df, aes(x = time, y = estimate)) +
    geom_errorbar(
      data = subset(dynamic_df, significant %in% TRUE),
      aes(ymin = conf_low, ymax = conf_high),
      width = 0.4,
      linetype = "solid"
    ) +
    geom_errorbar(
      data = subset(dynamic_df, !(significant %in% TRUE)),
      aes(ymin = conf_low, ymax = conf_high),
      width = 0.4,
      linetype = "dotted"
    ) +
    geom_point(
      data = subset(dynamic_df, significant %in% TRUE),
      shape = 19,
      size = 1.7
    ) +
    geom_point(
      data = subset(dynamic_df, !(significant %in% TRUE)),
      shape = 21,
      fill = "transparent",
      size = 1.7
    ) +
    geom_hline(yintercept = 0, linetype = "dashed") +
    geom_vline(xintercept = -0.5, linetype = "dashed") +
    scale_x_continuous(breaks = -6:6) +
    coord_cartesian(xlim = c(-6.5, 6.5)) +
    facet_wrap(~ outcome_label, scales = "free_y", nrow = 1) +
    labs(
      title = "Borusyak Quality DiD: SonarQube Outcomes",
      subtitle = "Balanced Python panel; small-N pipeline validation only",
      x = "Months Relative to Cursor Adoption",
      y = "Treatment Effect",
      caption = "Filled dots: CI excludes 0. Hollow dots: CI includes 0. Small-N estimates are not final empirical findings."
    ) +
    theme_minimal() +
    theme(
      panel.grid.minor = element_blank(),
      plot.caption = element_text(hjust = 0.5, size = 8)
    )

  print(p)

  ggsave(
    filename = file.path(out_dir, "dynamic_effects_borusyak_v2_quality.pdf"),
    plot = p,
    width = 9,
    height = 3.5
  )
} else {
  cat("No dynamic effects to plot.\n")
}
```

# Metadata

```{r metadata}
metadata <- data.frame(
  key = c(
    "script",
    "derived_from",
    "helper_file",
    "panel_path",
    "out_dir",
    "panel_type",
    "outcomes",
    "covariates",
    "estimator",
    "purpose",
    "full_paper_covariates_not_yet_included",
    "interpretation_warning"
  ),
  value = c(
    "proc_r/DiffInDiffBorusyak_quality_v2.Rmd",
    "proc_r/DiffInDiffBorusyak_v2.Rmd and notebooks/DiffInDiffBorusyak.Rmd",
    "proc_r/diff_in_diff_borusyak_helpers.R",
    panel_path,
    out_dir,
    "balanced SonarQube quality panel with zero-commit months",
    paste(outcome_vars, collapse = ", "),
    "contributors + log_ncloc",
    "Borusyak imputation via didimputation::did_imputation",
    "Small-scale quality DiD validation for the Python treatment/control panel",
    "age, stars, and issues will be added later from GHArchive/BigQuery or GitHub-derived covariate tables",
    "Small-N pipeline validation only; estimates and p-values are not final empirical findings"
  )
)

print(metadata)

fwrite(
  metadata,
  file.path(out_dir, "borusyak_quality_v2_metadata.csv")
)
```

# Session Info

```{r session-info}
sessionInfo()
```
