---
title: "Diff-in-Diff Borusyak: Class-Method Role Groups"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = TRUE, message = TRUE)
options(bitmapType = "cairo")

project_root <- normalizePath(
  Sys.getenv("PROJECT_ROOT", unset = "."),
  mustWork = TRUE
)

resolve_project_path <- function(path_value) {
  if (is.null(path_value) || path_value == "") return("")
  if (grepl("^/", path_value)) {
    return(normalizePath(path_value, mustWork = FALSE))
  }
  normalizePath(file.path(project_root, path_value), mustWork = FALSE)
}

panel_path <- resolve_project_path(Sys.getenv("PANEL_PATH", unset = ""))
out_dir <- resolve_project_path(Sys.getenv("OUT_DIR", unset = ""))
panel_label <- Sys.getenv("PANEL_LABEL", unset = "panel")
outcome_group <- tolower(Sys.getenv("OUTCOME_GROUP", unset = ""))
specification_name <- Sys.getenv("SPECIFICATION_NAME", unset = "range100_200")
ncloc_spec <- tolower(Sys.getenv("NCLOC_SPEC", unset = "python_snapshot"))
time_mode <- tolower(Sys.getenv("TIME_MODE", unset = "calendar_month"))
parse_exclusion_mode <- tolower(
  Sys.getenv("PARSE_EXCLUSION_MODE", unset = "parse_clean")
)
allow_model_failure <- Sys.getenv("ALLOW_MODEL_FAILURE", unset = "0") == "1"
rmd_script_label <- Sys.getenv(
  "RMD_SCRIPT_LABEL",
  unset = "proc_r/DiffInDiffBorusyak_class_method_role_groups.Rmd"
)
helper_path <- resolve_project_path(
  Sys.getenv(
    "HELPER_FILE",
    unset = "proc_r/diff_in_diff_borusyak_helpers.R"
  )
)

valid_groups <- c(
  "all_class_methods",
  "testing_class_methods",
  "boilerplate_class_methods",
  "other_class_methods"
)
if (!(outcome_group %in% valid_groups)) {
  stop("OUTCOME_GROUP must be one of: ", paste(valid_groups, collapse = ", "))
}
if (ncloc_spec != "python_snapshot") {
  stop("run-py-7f15 locks NCLOC_SPEC to python_snapshot.")
}
if (time_mode != "calendar_month") {
  stop("run-py-7f15 locks TIME_MODE to calendar_month.")
}
if (parse_exclusion_mode != "parse_clean") {
  stop("run-py-7f15 locks PARSE_EXCLUSION_MODE to parse_clean.")
}
if (panel_path == "" || out_dir == "") {
  stop("PANEL_PATH and OUT_DIR environment variables are required.")
}

dir.create(out_dir, recursive = TRUE, showWarnings = FALSE)
```

# Purpose

This notebook applies the locked Borusyak imputation DiD model to one of the
four zero-inclusive `run-py-7f14` class-method outcomes. Categories 5, 6, and 7
form a mutually exclusive partition of Category 4 at the raw-count level.

The model outcome is `log1p` of the distinct AGC-like class-method body count.
The raw count is retained for input validation and partition checks. Category 6
is explicitly exploratory because it has only 28 bodies in 11 positive
repository-months. Estimator failures are recorded in machine-readable outputs
instead of preventing the other categories from running.

# Load Packages and Helper Functions

```{r load-packages}
library(data.table)
library(dplyr)
library(ggplot2)
library(didimputation)

if (!file.exists(helper_path)) stop("Helper file not found: ", helper_path)
source(helper_path)
```

# Utility Functions

```{r utility-functions}
normalize_yyyymm <- function(x) {
  x <- as.character(x)
  x[x %in% c("", "NA", "NaN", "NULL", "None")] <- NA_character_
  x <- gsub("-", "", x)
  suppressWarnings(as.integer(x))
}

yyyymm_to_month_id <- function(x) {
  x <- as.integer(x)
  year <- x %/% 100L
  month <- x %% 100L
  out <- year * 12L + month
  out[is.na(x) | month < 1L | month > 12L] <- NA_integer_
  out
}

as_logical_flag <- function(x) {
  tolower(as.character(x)) %in% c("true", "1", "1.0")
}

require_columns <- function(data, required, label) {
  missing <- setdiff(required, names(data))
  if (length(missing) > 0) {
    stop(label, " missing required columns: ", paste(missing, collapse = ", "))
  }
}

write_error_table <- function(errors, stage, output_path) {
  if (length(errors) == 0) {
    fwrite(
      data.frame(
        stage = character(),
        outcome_group = character(),
        outcome = character(),
        error = character()
      ),
      output_path
    )
    return(invisible(NULL))
  }
  fwrite(
    data.frame(
      stage = stage,
      outcome_group = outcome_group,
      outcome = names(errors),
      error = unlist(errors),
      row.names = NULL,
      stringsAsFactors = FALSE
    ),
    output_path
  )
}

add_normal_p_value <- function(data) {
  data$p_value <- ifelse(
    !is.na(data$estimate) & !is.na(data$std_error) & data$std_error > 0,
    2 * pnorm(abs(data$estimate / data$std_error), lower.tail = FALSE),
    NA_real_
  )
  data
}

empty_dynamic_table <- function() {
  data.frame(
    outcome = character(), outcome_label = character(), time = numeric(),
    estimate = numeric(), conf_low = numeric(), conf_high = numeric(),
    std_error = numeric(), p_value = numeric(), significant = logical(),
    stringsAsFactors = FALSE
  )
}

safe_percent <- function(x) {
  ifelse(is.na(x), NA_real_, 100 * expm1(x))
}
```

# Outcome Configuration

```{r outcome-configuration}
group_config <- data.frame(
  outcome_group = valid_groups,
  outcome_category = c(4L, 5L, 6L, 7L),
  outcome_label = c(
    "All AGC-like synchronous class-method unique bodies",
    "AGC-like testing-related synchronous class-method unique bodies",
    "AGC-like boilerplate synchronous class-method unique bodies",
    "AGC-like other synchronous class-method unique bodies"
  ),
  expected_total = c(3925L, 1201L, 28L, 2696L),
  expected_positive_rows = c(497L, 162L, 11L, 455L),
  expected_zero_rows = c(1024L, 1359L, 1510L, 1066L),
  exploratory = c(FALSE, FALSE, TRUE, FALSE),
  stringsAsFactors = FALSE
)

selected_config <- group_config[group_config$outcome_group == outcome_group, ]
outcome_category <- selected_config$outcome_category[[1]]
outcome_label <- selected_config$outcome_label[[1]]
expected_total <- selected_config$expected_total[[1]]
expected_positive_rows <- selected_config$expected_positive_rows[[1]]
expected_zero_rows <- selected_config$expected_zero_rows[[1]]
exploratory_outcome <- selected_config$exploratory[[1]]

if (allow_model_failure != exploratory_outcome) {
  stop(
    "ALLOW_MODEL_FAILURE must be 1 only for boilerplate_class_methods and 0 ",
    "for the three required outcomes."
  )
}

raw_count_var <- "npr_agc_class_method_unique_bodies"
outcome_var <- "log1p_npr_agc_class_method_unique_bodies"
occurrence_var <- "has_npr_agc_class_method_unique_body"
zero_var <- "zero_npr_agc_class_method_unique_body_month"
output_prefix <- paste0("borusyak_class_method_role_group_", outcome_group)
```

# Load and Validate Input Panel

```{r load-panel}
cat("Project root:", project_root, "\n")
cat("Panel path:", panel_path, "\n")
cat("Outcome group:", outcome_group, "\n")
cat("Outcome category:", outcome_category, "\n")
cat("Exploratory outcome:", exploratory_outcome, "\n")
cat("Model outcome:", outcome_var, "\n")

if (!file.exists(panel_path)) stop("Panel file not found: ", panel_path)
panel_raw <- fread(panel_path)

covariates <- c(
  "log1p_age",
  "ncloc_python_snapshot",
  "log1p_contributors",
  "log1p_stars",
  "log1p_issues"
)
readiness_column <-
  "analysis_ready_regular_module_function_agc_unique_body_python_snapshot_ncloc"

base_required <- c(
  "dataset_source", "repo_name", "time", "event", "time_to_event",
  raw_count_var, outcome_var, occurrence_var, zero_var, covariates,
  readiness_column, "has_parse_exclusion", "npr_detection_complete",
  "npr_specification", "treatment_group", "class_method_outcome_category",
  "class_method_outcome_group", "class_method_outcome_schema_version",
  "class_method_taxonomy_status", "class_method_taxonomy_version",
  "class_method_scope", "class_method_count_unit", "class_method_outcome_scale"
)
require_columns(panel_raw, base_required, "Input panel")

if (nrow(panel_raw) != 1521L) stop("Expected 1,521 input rows.")
if (uniqueN(panel_raw$repo_name) != 218L) stop("Expected 218 repositories.")
if (anyDuplicated(panel_raw[, .(dataset_source, repo_name, time)]) > 0) {
  stop("Input panel has duplicate repository-month keys.")
}
if (!all(panel_raw$dataset_source %in% c("control", "treatment"))) {
  stop("dataset_source contains unexpected values.")
}
if (!all(as.character(panel_raw$class_method_outcome_group) == outcome_group)) {
  stop("class_method_outcome_group does not match OUTCOME_GROUP.")
}
if (!all(as.integer(panel_raw$class_method_outcome_category) == outcome_category)) {
  stop("class_method_outcome_category does not match the locked mapping.")
}
if (!all(panel_raw$class_method_outcome_schema_version == "run-py-7f14-v2")) {
  stop("Unexpected run-py-7f14 outcome schema version.")
}
if (!all(panel_raw$class_method_taxonomy_status == "FROZEN_PARTITION")) {
  stop("Class-method taxonomy is not uniformly frozen.")
}
if (!all(
  panel_raw$class_method_taxonomy_version ==
    "class-method-testing-boilerplate-other-v1"
)) {
  stop("Unexpected class-method taxonomy version.")
}
if (!all(panel_raw$class_method_scope ==
  "synchronous_direct_class_scope_method_excluding_lexically_nested")) {
  stop("Unexpected class-method scope.")
}
if (!all(panel_raw$class_method_outcome_scale == "raw_count")) {
  stop("The source panel raw-count contract is not uniform.")
}
if (!all(panel_raw$npr_specification == specification_name)) {
  stop("npr_specification does not match the requested specification.")
}
if (!all(panel_raw$treatment_group == panel_raw$dataset_source)) {
  stop("treatment_group does not match dataset_source.")
}
if (!all(as_logical_flag(panel_raw$npr_detection_complete))) {
  stop("npr_detection_complete is not uniformly true.")
}

raw_values <- suppressWarnings(as.numeric(panel_raw[[raw_count_var]]))
log_values <- suppressWarnings(as.numeric(panel_raw[[outcome_var]]))
outcome_missing_rows <- sum(is.na(raw_values) | is.na(log_values))
outcome_negative_rows <- sum(raw_values < 0, na.rm = TRUE)
outcome_noninteger_rows <- sum(
  !is.na(raw_values) & abs(raw_values - round(raw_values)) > 1e-12
)
log1p_mismatch_rows <- sum(
  is.na(raw_values) | is.na(log_values) |
    abs(log_values - log1p(raw_values)) > 1e-12
)
occurrence_mismatch_rows <- sum(
  as.integer(panel_raw[[occurrence_var]]) != as.integer(raw_values > 0),
  na.rm = TRUE
)
zero_flag_mismatch_rows <- sum(
  as.integer(panel_raw[[zero_var]]) != as.integer(raw_values == 0),
  na.rm = TRUE
)

if (
  outcome_missing_rows > 0 || outcome_negative_rows > 0 ||
    outcome_noninteger_rows > 0 || log1p_mismatch_rows > 0 ||
    occurrence_mismatch_rows > 0 || zero_flag_mismatch_rows > 0
) {
  stop("Raw-count/log1p outcome contract failed.")
}

observed_total <- sum(raw_values)
observed_positive_rows <- sum(raw_values > 0)
observed_zero_rows <- sum(raw_values == 0)
if (observed_total != expected_total) stop("Outcome total mismatch.")
if (observed_positive_rows != expected_positive_rows) {
  stop("Positive-row mismatch.")
}
if (observed_zero_rows != expected_zero_rows) stop("Zero-row mismatch.")

cat("Loaded rows:", nrow(panel_raw), "\n")
cat("Loaded repositories:", uniqueN(panel_raw$repo_name), "\n")
cat("Positive rows:", observed_positive_rows, "\n")
cat("Zero rows:", observed_zero_rows, "\n")
cat("Total raw-count bodies:", observed_total, "\n")
```

# Configure Locked Borusyak Model

```{r configure-model}
panel_data <- copy(panel_raw)
panel_data <- panel_data[get(readiness_column) == 1]
rows_after_readiness_filter <- nrow(panel_data)
panel_data <- panel_data[has_parse_exclusion == 0]
rows_after_parse_filter <- nrow(panel_data)

model_required <- c(outcome_var, covariates)
implicit_missing_rows <- sum(!complete.cases(panel_data[, ..model_required]))
if (implicit_missing_rows > 0) {
  stop("Analysis-ready rows contain missing model variables.")
}

panel_data[, time_yyyymm := normalize_yyyymm(time)]
event_yyyymm_raw <- normalize_yyyymm(panel_data$event)
event_yyyymm_raw[is.na(event_yyyymm_raw)] <- 0L
panel_data[, event_yyyymm := event_yyyymm_raw]

event_membership_mismatch_rows <- panel_data[
  , sum((dataset_source == "treatment") != (event_yyyymm > 0L))
]
if (event_membership_mismatch_rows > 0) {
  stop("Event encoding disagrees with dataset_source.")
}

panel_data <- panel_data[
  event_yyyymm == 0L |
    (event_yyyymm > 202407L & event_yyyymm <= 202503L)
]
rows_after_cohort_filter <- nrow(panel_data)

panel_data[, repo_id := as.integer(factor(as.character(repo_name)))]
panel_data[, time_id := yyyymm_to_month_id(time_yyyymm)]
panel_data[, event_id := fifelse(
  event_yyyymm == 0L,
  0L,
  yyyymm_to_month_id(event_yyyymm)
)]
panel_data <- panel_data[!is.na(time_id)]
panel_data <- panel_data[event_id == 0L | !is.na(event_id)]
panel_data[, treated := as.integer(event_id > 0L)]

first_stage_rhs <- paste(covariates, collapse = " + ")
first_stage_formula <- as.formula(
  paste0("~ ", first_stage_rhs, " | repo_id + time_id")
)

cat("Rows used by models:", nrow(panel_data), "\n")
cat("Repositories used:", uniqueN(panel_data$repo_id), "\n")
cat("First-stage formula:\n")
print(first_stage_formula)
```

# Panel Checks and Input Summary

```{r panel-checks}
panel_checks <- data.frame(
  check = c(
    "schema_version", "panel_label", "outcome_category", "outcome_group",
    "model_outcome", "model_outcome_scale", "input_rows",
    "input_repositories", "rows_after_readiness_filter",
    "rows_after_parse_filter", "rows_after_cohort_filter",
    "rows_used_by_models", "repositories_used_by_models",
    "treated_repositories", "control_repositories",
    "raw_count_total", "positive_outcome_rows", "zero_outcome_rows",
    "outcome_missing_rows", "outcome_negative_rows",
    "outcome_noninteger_rows", "log1p_arithmetic_mismatch_rows",
    "occurrence_arithmetic_mismatch_rows", "zero_flag_arithmetic_mismatch_rows",
    "event_membership_mismatch_rows", "covariate_missing_sum",
    "first_stage_covariates", "fixed_effects", "cluster_variable",
    "exploratory_outcome", "allow_model_failure"
  ),
  value = c(
    "run-py-7f15-v1", panel_label, outcome_category, outcome_group,
    outcome_var, "log1p(raw_count)", nrow(panel_raw),
    uniqueN(panel_raw$repo_name), rows_after_readiness_filter,
    rows_after_parse_filter, rows_after_cohort_filter,
    nrow(panel_data), uniqueN(panel_data$repo_id),
    uniqueN(panel_data[treated == 1, repo_id]),
    uniqueN(panel_data[treated == 0, repo_id]),
    sum(panel_data[[raw_count_var]]), sum(panel_data[[raw_count_var]] > 0),
    sum(panel_data[[raw_count_var]] == 0), outcome_missing_rows,
    outcome_negative_rows, outcome_noninteger_rows, log1p_mismatch_rows,
    occurrence_mismatch_rows, zero_flag_mismatch_rows,
    event_membership_mismatch_rows, sum(is.na(panel_data[, ..covariates])),
    first_stage_rhs, "repo_id + time_id", "repo_id (idname default)",
    exploratory_outcome, allow_model_failure
  ),
  stringsAsFactors = FALSE
)
fwrite(panel_checks, file.path(out_dir, paste0(output_prefix, "_panel_checks.csv")))

input_summary <- panel_data[, .(
  rows = .N,
  repositories = uniqueN(repo_id),
  total_raw_count = sum(get(raw_count_var)),
  mean_raw_count = mean(get(raw_count_var)),
  median_raw_count = as.numeric(median(get(raw_count_var))),
  maximum_raw_count = max(get(raw_count_var)),
  mean_log1p_count = mean(get(outcome_var)),
  positive_month_share = mean(get(raw_count_var) > 0),
  zero_month_share = mean(get(raw_count_var) == 0)
), by = dataset_source]
input_summary$outcome_category <- outcome_category
input_summary$outcome_group <- outcome_group
input_summary$outcome_label <- outcome_label
fwrite(input_summary, file.path(out_dir, paste0(output_prefix, "_input_summary.csv")))
```

# Static ATT

```{r static-effect}
static_errors <- list()
static_result <- tryCatch(
  run_borusyak_static(
    data = panel_data,
    outcome_var = outcome_var,
    first_stage_formula = first_stage_formula,
    idname = "repo_id", tname = "time_id", gname = "event_id"
  ),
  error = function(e) {
    static_errors[[outcome_var]] <<- conditionMessage(e)
    NULL
  }
)

static_df <- add_normal_p_value(extract_static_result(static_result, outcome_var))
static_df$estimate_percent_yplus1 <- safe_percent(static_df$estimate)
static_df$conf_low_percent_yplus1 <- safe_percent(static_df$conf_low)
static_df$conf_high_percent_yplus1 <- safe_percent(static_df$conf_high)
static_df$outcome_category <- outcome_category
static_df$outcome_group <- outcome_group
static_df$outcome_label <- outcome_label
static_df$outcome_scale <- "log1p_raw_count"
static_df$outcome_unit <- "log(1 + distinct bodies per repository-month)"
static_df$exploratory <- exploratory_outcome
static_df$panel <- panel_label
static_df$specification <- specification_name
static_df$cluster_variable <- "repo_id"
static_df$confidence_level <- 0.95

fwrite(static_df, file.path(out_dir, paste0(output_prefix, "_static_effects.csv")))
write_error_table(
  static_errors, "static",
  file.path(out_dir, paste0(output_prefix, "_static_errors.csv"))
)
```

# Dynamic Effects

```{r dynamic-effects}
dynamic_errors <- list()
dynamic_result <- tryCatch(
  run_borusyak_dynamic(
    data = panel_data,
    outcome_var = outcome_var,
    first_stage_formula = first_stage_formula,
    horizon = -6:6,
    pretrends = -6:-2,
    idname = "repo_id", tname = "time_id", gname = "event_id"
  ),
  error = function(e) {
    dynamic_errors[[outcome_var]] <<- conditionMessage(e)
    NULL
  }
)

dynamic_df <- extract_dynamic_result(
  dynamic_result,
  outcome = outcome_var,
  outcome_label = outcome_label,
  min_horizon = -6,
  max_horizon = 6
)
if (nrow(dynamic_df) == 0) dynamic_df <- empty_dynamic_table()
dynamic_df <- add_normal_p_value(dynamic_df)
dynamic_df$estimate_percent_yplus1 <- safe_percent(dynamic_df$estimate)
dynamic_df$conf_low_percent_yplus1 <- safe_percent(dynamic_df$conf_low)
dynamic_df$conf_high_percent_yplus1 <- safe_percent(dynamic_df$conf_high)
dynamic_df$outcome_category <- rep(outcome_category, nrow(dynamic_df))
dynamic_df$outcome_group <- rep(outcome_group, nrow(dynamic_df))
dynamic_df$outcome_scale <- rep("log1p_raw_count", nrow(dynamic_df))
dynamic_df$outcome_unit <- rep(
  "log(1 + distinct bodies per repository-month)", nrow(dynamic_df)
)
dynamic_df$exploratory <- rep(exploratory_outcome, nrow(dynamic_df))
dynamic_df$panel <- rep(panel_label, nrow(dynamic_df))
dynamic_df$specification <- rep(specification_name, nrow(dynamic_df))
dynamic_df$cluster_variable <- rep("repo_id", nrow(dynamic_df))
dynamic_df$confidence_level <- rep(0.95, nrow(dynamic_df))

fwrite(dynamic_df, file.path(out_dir, paste0(output_prefix, "_dynamic_effects.csv")))
write_error_table(
  dynamic_errors, "dynamic",
  file.path(out_dir, paste0(output_prefix, "_dynamic_errors.csv"))
)
```

# Uncertainty and Pre-Trend Results

```{r uncertainty-and-pretrend}
static_uncertainty <- data.frame(
  outcome_category = outcome_category,
  outcome_group = outcome_group,
  outcome_label = outcome_label,
  effect_type = "static_att",
  event_time = NA_real_,
  estimate = static_df$estimate,
  std_error = static_df$std_error,
  conf_low = static_df$conf_low,
  conf_high = static_df$conf_high,
  p_value = static_df$p_value,
  estimate_percent_yplus1 = static_df$estimate_percent_yplus1,
  significant_05 = !is.na(static_df$conf_low) &
    !is.na(static_df$conf_high) &
    (static_df$conf_low > 0 | static_df$conf_high < 0),
  exploratory = exploratory_outcome,
  confidence_level = 0.95,
  cluster_variable = "repo_id",
  stringsAsFactors = FALSE
)

if (nrow(dynamic_df) > 0) {
  dynamic_uncertainty <- data.frame(
    outcome_category = dynamic_df$outcome_category,
    outcome_group = dynamic_df$outcome_group,
    outcome_label = dynamic_df$outcome_label,
    effect_type = "dynamic_event_time",
    event_time = dynamic_df$time,
    estimate = dynamic_df$estimate,
    std_error = dynamic_df$std_error,
    conf_low = dynamic_df$conf_low,
    conf_high = dynamic_df$conf_high,
    p_value = dynamic_df$p_value,
    estimate_percent_yplus1 = dynamic_df$estimate_percent_yplus1,
    significant_05 = dynamic_df$significant,
    exploratory = exploratory_outcome,
    confidence_level = 0.95,
    cluster_variable = "repo_id",
    stringsAsFactors = FALSE
  )
} else {
  dynamic_uncertainty <- static_uncertainty[0, ]
}

uncertainty_df <- bind_rows(static_uncertainty, dynamic_uncertainty)
fwrite(uncertainty_df, file.path(out_dir, paste0(output_prefix, "_uncertainty.csv")))

pretrend_df <- dynamic_df[dynamic_df$time %in% -6:-2, , drop = FALSE]
pretrend_period_count <- nrow(pretrend_df)
if (pretrend_period_count > 0) {
  pretrend_df$p_value_unadjusted <- pretrend_df$p_value
  pretrend_df$p_value_bonferroni <- pmin(
    1, pretrend_period_count * pretrend_df$p_value_unadjusted
  )
  pretrend_df$significant_unadjusted_05 <-
    !is.na(pretrend_df$p_value_unadjusted) &
    pretrend_df$p_value_unadjusted < 0.05
  pretrend_df$significant_bonferroni_05 <-
    !is.na(pretrend_df$p_value_bonferroni) &
    pretrend_df$p_value_bonferroni < 0.05
} else {
  pretrend_df$p_value_unadjusted <- numeric()
  pretrend_df$p_value_bonferroni <- numeric()
  pretrend_df$significant_unadjusted_05 <- logical()
  pretrend_df$significant_bonferroni_05 <- logical()
}

valid_pretrend_p <- pretrend_df$p_value_unadjusted[
  !is.na(pretrend_df$p_value_unadjusted)
]
minimum_pretrend_p <- if (length(valid_pretrend_p) > 0) {
  min(valid_pretrend_p)
} else {
  NA_real_
}
global_bonferroni_p <- if (!is.na(minimum_pretrend_p)) {
  min(1, pretrend_period_count * minimum_pretrend_p)
} else {
  NA_real_
}
pretrend_conclusion <- if (is.na(global_bonferroni_p)) {
  "UNAVAILABLE"
} else if (global_bonferroni_p < 0.05) {
  "EVIDENCE_OF_NONZERO_PRETREND"
} else {
  "NO_EVIDENCE_OF_NONZERO_PRETREND"
}

pretrend_summary <- data.frame(
  outcome_category = outcome_category,
  outcome_group = outcome_group,
  outcome_label = outcome_label,
  exploratory = exploratory_outcome,
  expected_pretrend_periods = 5L,
  available_pretrend_periods = pretrend_period_count,
  significant_unadjusted_periods = if (pretrend_period_count > 0) {
    sum(pretrend_df$significant_unadjusted_05)
  } else NA_integer_,
  significant_bonferroni_periods = if (pretrend_period_count > 0) {
    sum(pretrend_df$significant_bonferroni_05)
  } else NA_integer_,
  minimum_unadjusted_p_value = minimum_pretrend_p,
  global_bonferroni_p_value = global_bonferroni_p,
  family_wise_alpha = 0.05,
  pretrend_conclusion = pretrend_conclusion,
  diagnostic_method = paste(
    "Five marginal lead tests (-6:-2) with a conservative",
    "Bonferroni family-wise diagnostic"
  ),
  stringsAsFactors = FALSE
)

fwrite(pretrend_df, file.path(out_dir, paste0(output_prefix, "_pretrend_effects.csv")))
fwrite(
  pretrend_summary,
  file.path(out_dir, paste0(output_prefix, "_pretrend_summary.csv"))
)
```

# Dynamic Plot

```{r dynamic-plot, fig.width=10, fig.height=4.5}
if (nrow(dynamic_df) > 0) {
  plot_object <- ggplot(dynamic_df, aes(x = time, y = estimate)) +
    geom_errorbar(
      aes(ymin = conf_low, ymax = conf_high, linetype = !significant),
      width = 0.4
    ) +
    geom_point(aes(shape = significant), size = 2) +
    geom_hline(yintercept = 0, linetype = "dashed") +
    geom_vline(xintercept = -0.5, linetype = "dashed") +
    scale_x_continuous(breaks = -6:6) +
    scale_linetype_manual(values = c("solid", "dotted"), guide = "none") +
    scale_shape_manual(values = c(`TRUE` = 19, `FALSE` = 1), guide = "none") +
    coord_cartesian(xlim = c(-6.5, 6.5)) +
    labs(
      title = paste("Borusyak DiD:", outcome_label),
      subtitle = paste(
        "log1p count | Python-snapshot NCLOC |",
        if (exploratory_outcome) "Exploratory sparse outcome" else "Primary outcome"
      ),
      x = "Months Relative to Cursor Adoption",
      y = "Estimated Change in log(1 + Distinct AGC-Like Bodies)",
      caption = paste(
        "Month -1 is omitted and normalized to zero.",
        "Zero-count repository-months are retained."
      )
    ) +
    theme_minimal() +
    theme(panel.grid.minor = element_blank())
} else {
  plot_object <- ggplot() +
    annotate(
      "text", x = 0, y = 0,
      label = paste(
        "Dynamic model unavailable for", outcome_group,
        "\nSee dynamic_errors.csv and final_model_validation.csv"
      )
    ) +
    xlim(-1, 1) + ylim(-1, 1) +
    labs(title = paste("Borusyak DiD:", outcome_label)) +
    theme_void()
}

print(plot_object)
ggsave(
  filename = file.path(
    out_dir,
    paste0("dynamic_effects_borusyak_class_method_role_group_", outcome_group, ".pdf")
  ),
  plot = plot_object,
  width = 10,
  height = 4.5
)
```

# Final Model Validation and Metadata

```{r final-model-validation}
static_model_error_count <- length(static_errors)
dynamic_model_error_count <- length(dynamic_errors)
expected_dynamic_times <- c(-6:-2, 0:6)

static_effect_complete <- nrow(static_df) == 1 &&
  all(complete.cases(static_df[, c(
    "estimate", "std_error", "conf_low", "conf_high", "p_value"
  )]))
dynamic_effects_complete <- nrow(dynamic_df) == 12L &&
  identical(sort(as.integer(dynamic_df$time)), expected_dynamic_times) &&
  all(complete.cases(dynamic_df[, c(
    "estimate", "std_error", "conf_low", "conf_high", "p_value"
  )]))
pretrend_effects_complete <- nrow(pretrend_df) == 5L &&
  identical(sort(as.integer(pretrend_df$time)), -6:-2)
uncertainty_rows_complete <- nrow(uncertainty_df) == 13L
model_complete <-
  static_model_error_count == 0 && dynamic_model_error_count == 0 &&
  static_effect_complete && dynamic_effects_complete &&
  pretrend_effects_complete && uncertainty_rows_complete

model_status <- if (model_complete && exploratory_outcome) {
  "EXPLORATORY_PASS"
} else if (model_complete) {
  "PASS"
} else if (allow_model_failure) {
  "EXPLORATORY_INCOMPLETE"
} else {
  "FAIL"
}

final_model_validation <- data.frame(
  check = c(
    "schema_version", "outcome_category", "outcome_group",
    "exploratory_outcome", "allow_model_failure",
    "static_model_error_count", "dynamic_model_error_count",
    "static_effect_complete", "dynamic_effects_complete_12_estimated_periods",
    "pretrend_effects_complete_5_periods",
    "uncertainty_rows_complete_13_rows", "rows_used_by_models",
    "repositories_used_by_models", "covariate_missing_sum", "status"
  ),
  value = c(
    "run-py-7f15-v1", outcome_category, outcome_group,
    exploratory_outcome, allow_model_failure,
    static_model_error_count, dynamic_model_error_count,
    static_effect_complete, dynamic_effects_complete,
    pretrend_effects_complete, uncertainty_rows_complete,
    nrow(panel_data), uniqueN(panel_data$repo_id),
    sum(is.na(panel_data[, ..covariates])), model_status
  ),
  stringsAsFactors = FALSE
)
fwrite(
  final_model_validation,
  file.path(out_dir, paste0(output_prefix, "_final_model_validation.csv"))
)

interpretation_note <- if (exploratory_outcome) {
  paste(
    "Category 6 is exploratory because only 28 bodies occur in 11 positive",
    "repository-months; absence of significance is not evidence of no effect."
  )
} else if (outcome_group == "all_class_methods") {
  paste(
    "Category 4 is the aggregate raw-count benchmark. Categories 5, 6, and 7",
    "partition it before log1p transformation."
  )
} else {
  paste(
    "Separate category significance levels do not establish a significant",
    "difference between category-specific ATTs."
  )
}

metadata <- data.frame(
  key = c(
    "schema_version", "script", "helper_file", "panel_label", "panel_path",
    "out_dir", "outcome_category", "outcome_group", "outcome_label",
    "raw_count_outcome", "model_outcome", "model_outcome_scale",
    "percent_transform", "zero_inclusive", "specification_name",
    "taxonomy_status", "taxonomy_version", "ncloc_specification",
    "time_mode", "parse_exclusion_mode", "covariates", "covariate_scaling",
    "fixed_effects", "first_stage_formula", "cohort_restriction",
    "rows_used_by_models", "repositories_used_by_models", "estimator",
    "time_encoding", "horizon", "reference_period",
    "estimated_dynamic_periods", "pretrends", "cluster_variable",
    "uncertainty_method", "confidence_level", "pretrend_diagnostic",
    "global_bonferroni_p_value", "pretrend_conclusion",
    "exploratory_outcome", "allow_model_failure", "model_status",
    "interpretation_note"
  ),
  value = c(
    "run-py-7f15-v1", rmd_script_label, helper_path, panel_label, panel_path,
    out_dir, outcome_category, outcome_group, outcome_label,
    raw_count_var, outcome_var, "log1p(raw_count)",
    "100 * (exp(ATT) - 1), interpreted on count+1 scale", "true",
    specification_name, "FROZEN_PARTITION",
    "class-method-testing-boilerplate-other-v1", "python_snapshot",
    "calendar_month", "parse_clean", first_stage_rhs,
    "log1p(age, contributors, stars, issues); raw ncloc_python_snapshot",
    "repo_id + time_id", paste(deparse(first_stage_formula), collapse = " "),
    "controls plus treatment cohorts 2024-08 through 2025-03",
    nrow(panel_data), uniqueN(panel_data$repo_id),
    "Borusyak imputation via didimputation::did_imputation",
    "sequential_calendar_month_id", "-6:6",
    "-1 (omitted and normalized to zero; not estimated)",
    "-6:-2 and 0:6 (12 estimated periods)", "-6:-2", "repo_id",
    paste(
      "didimputation analytic standard errors and 95% confidence intervals;",
      "repository clustering through idname default"
    ),
    "0.95",
    "five marginal leads with conservative Bonferroni family-wise diagnostic",
    global_bonferroni_p, pretrend_conclusion, exploratory_outcome,
    allow_model_failure, model_status, interpretation_note
  ),
  stringsAsFactors = FALSE
)
fwrite(metadata, file.path(out_dir, paste0(output_prefix, "_metadata.csv")))

print(final_model_validation)
print(metadata)
```

# Session Info

```{r session-info}
sessionInfo()
```
