---
title: "Borusyak DiD for JS/TS Development Velocity"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
params:
  panel_label: "main_unbalanced"
  panel_path: "tmp_jsts_test/data/jsts_did_final/panel_event_monthly_matched_final_clean.csv"
  out_dir: "tmp_jsts_test/data/jsts_did_final/velocity_did_borusyak/main_unbalanced"
  helpers_path: "diff_in_diff_borusyak_helpers.R"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = TRUE,
  warning = TRUE,
  error = FALSE
)
```

# Purpose

This report estimates Borusyak imputation-based Difference-in-Differences models for JS/TS development velocity outcomes.

The velocity outcomes are:

* `commits`
* `lines_added`

The analysis uses the same four-panel structure as the quality DiD analysis:

* `main_unbalanced`
* `main_balanced`
* `strict_1to3_unbalanced`
* `strict_1to3_balanced`

Model runners and result extractors are shared with the other Borusyak reports
via `diff_in_diff_borusyak_helpers.R`.

# Load Packages

```{r packages}
required_packages <- c(
  "data.table",
  "dplyr",
  "ggplot2",
  "knitr",
  "didimputation"
)

for (pkg in required_packages) {
  if (!requireNamespace(pkg, quietly = TRUE)) {
    stop("Required package is not installed: ", pkg)
  }
}

library(data.table)
library(dplyr)
library(ggplot2)
library(knitr)
library(didimputation)
```

# Parameters

```{r params}
panel_label <- params$panel_label
panel_path <- params$panel_path
out_dir <- params$out_dir

dir.create(out_dir, recursive = TRUE, showWarnings = FALSE)

cat("Panel label:", panel_label, "\n")
cat("Panel path:", panel_path, "\n")
cat("Output dir:", out_dir, "\n")
```

# Shared Borusyak Helpers

```{r source-helpers}
# Shared functions (sourced, not redefined here):
#   run_borusyak_static(), run_borusyak_dynamic(),
#   extract_static_result(), extract_dynamic_result(),
#   extract_event_time_from_term(),
#   get_col_or_na(), get_first_available_col_or_na()

resolve_helpers_path <- function(configured_path) {
  rmd_dir <- tryCatch(
    dirname(normalizePath(knitr::current_input())),
    error = function(e) NA_character_
  )

  candidates <- c(
    configured_path,
    if (!is.na(rmd_dir)) file.path(rmd_dir, basename(configured_path)),
    file.path("proc_r", basename(configured_path)),
    basename(configured_path)
  )

  candidates <- unique(candidates[!is.na(candidates)])
  hits <- candidates[file.exists(candidates)]

  if (length(hits) == 0) {
    stop(
      "Borusyak helper script not found. Tried: ",
      paste(candidates, collapse = ", ")
    )
  }

  normalizePath(hits[1])
}

helpers_path <- resolve_helpers_path(params$helpers_path)
cat("Sourcing shared helpers from:", helpers_path, "\n")
source(helpers_path)
```

# Report-Local Helper Functions

```{r helper-functions}
# These helpers are specific to this report's panel encoding and output
# post-processing, so they intentionally stay local rather than moving to
# diff_in_diff_borusyak_helpers.R.

normalize_yyyymm <- function(x) {
  x_chr <- as.character(x)
  out <- rep(NA_integer_, length(x_chr))

  is_missing <- is.na(x_chr) | x_chr == "" | x_chr == "NA" | x_chr == "NaN"
  x_chr[is_missing] <- NA_character_

  dash_format <- !is.na(x_chr) & grepl("^\\d{4}-\\d{2}$", x_chr)
  out[dash_format] <- as.integer(gsub("-", "", x_chr[dash_format]))

  numeric_format <- !is.na(x_chr) & grepl("^\\d{6}$", x_chr)
  out[numeric_format] <- as.integer(x_chr[numeric_format])

  out
}

yyyymm_to_month_id <- function(yyyymm) {
  yyyymm <- as.integer(yyyymm)
  year <- yyyymm %/% 100L
  month <- yyyymm %% 100L

  out <- year * 12L + month
  out[is.na(yyyymm) | month < 1L | month > 12L] <- NA_integer_
  out
}

calc_p_value <- function(estimate, std_error) {
  ifelse(
    is.na(estimate) | is.na(std_error) | std_error <= 0,
    NA_real_,
    2 * pnorm(-abs(estimate / std_error))
  )
}

# didimputation::did_imputation() does not return a p-value column, so the
# shared extractors leave p_value as NA. Recover it from estimate / std_error
# with a normal approximation, preserving this report's previous output.
fill_missing_p_values <- function(df) {
  if (nrow(df) == 0 || !all(c("p_value", "estimate", "std_error") %in% names(df))) {
    return(df)
  }

  missing_p <- is.na(df$p_value)
  df$p_value[missing_p] <- calc_p_value(
    df$estimate[missing_p],
    df$std_error[missing_p]
  )

  df
}
```

# Load Velocity Panel

```{r load-panel}
if (!file.exists(panel_path)) {
  stop("Panel file not found: ", panel_path)
}

panel_raw <- fread(panel_path)

cat("Rows:", nrow(panel_raw), "\n")
cat("Repos:", uniqueN(panel_raw$repo_name), "\n")
cat("Columns:", ncol(panel_raw), "\n")

required_cols <- c("repo_name", "time", "event", "dataset_source", "post_event", "commits", "lines_added")
missing_cols <- setdiff(required_cols, names(panel_raw))

if (length(missing_cols) > 0) {
  stop("Missing required columns: ", paste(missing_cols, collapse = ", "))
}

cat("Months:", min(panel_raw$time, na.rm = TRUE), "to", max(panel_raw$time, na.rm = TRUE), "\n")
```

# Panel Sanity Checks Before Estimation

```{r panel-checks}
panel_checks <- data.frame(
  check = c(
    "panel_label",
    "rows",
    "repos",
    "treatment_rows",
    "control_rows",
    "treated_repos",
    "control_repos",
    "commits_nonmissing",
    "lines_added_nonmissing",
    "duplicate_repo_time_source_rows"
  ),
  value = c(
    panel_label,
    nrow(panel_raw),
    uniqueN(panel_raw$repo_name),
    sum(panel_raw$dataset_source == "treatment", na.rm = TRUE),
    sum(panel_raw$dataset_source == "control", na.rm = TRUE),
    uniqueN(panel_raw[dataset_source == "treatment"]$repo_name),
    uniqueN(panel_raw[dataset_source == "control"]$repo_name),
    sum(!is.na(panel_raw$commits)),
    sum(!is.na(panel_raw$lines_added)),
    sum(duplicated(panel_raw[, .(repo_name, time, dataset_source)]))
  )
)

print(panel_checks)

fwrite(
  panel_checks,
  file.path(out_dir, "borusyak_velocity_panel_checks_pre_filter.csv")
)
```

# Prepare Data for Borusyak Estimator

```{r prepare-data}
panel_data <- copy(panel_raw)

panel_data[, time_yyyymm := normalize_yyyymm(time)]


event_yyyymm_raw <- normalize_yyyymm(panel_data$event)
event_yyyymm_raw[is.na(event_yyyymm_raw)] <- 0L
panel_data[, event_yyyymm := event_yyyymm_raw]

# Safety rule:
# Controls are never-treated in the Borusyak estimator.
# Even if a control row carries a pseudo-event month for matching provenance,
# it should not be treated as an adoption event.
panel_data[, dataset_source := as.character(dataset_source)]
panel_data[dataset_source != "treatment", event_yyyymm := 0L]

if ("post_event" %in% names(panel_data)) {
  panel_data[dataset_source != "treatment", post_event := 0L]
}

# Match the cohort restriction used in the quality Borusyak pipeline.
panel_data <- panel_data[
  event_yyyymm == 0L |
    (event_yyyymm > 202407L & event_yyyymm <= 202503L)
]



panel_data[, time_id := yyyymm_to_month_id(time_yyyymm)]
panel_data[, event_id := ifelse(event_yyyymm == 0L, 0L, yyyymm_to_month_id(event_yyyymm))]

panel_data <- panel_data[!is.na(time_id)]
panel_data <- panel_data[event_id == 0L | !is.na(event_id)]

panel_data[, repo_name_str := repo_name]
panel_data[, repo_id := as.integer(factor(repo_name_str))]
panel_data[, treated := ifelse(event_id > 0L, 1L, 0L)]
panel_data[, time_to_event_calc := ifelse(treated == 1L, time_id - event_id, NA_integer_)]

panel_data[, commits := as.numeric(commits)]
panel_data[, lines_added := as.numeric(lines_added)]

panel_data[commits < 0, commits := NA_real_]
panel_data[lines_added < 0, lines_added := NA_real_]

panel_data[, log_commits := log1p(commits)]
panel_data[, log_lines_added := log1p(lines_added)]




add_log_covariate <- function(dt, raw_col, log_col) {
  if (!(raw_col %in% names(dt))) {
    return(NULL)
  }

  dt[, (log_col) := log1p(as.numeric(get(raw_col)))]

  if (sum(!is.na(dt[[log_col]])) == nrow(dt)) {
    return(log_col)
  }

  return(NULL)
}

covariates <- c()

# Contributor count from version-control history.
if ("contributors" %in% names(panel_data)) {
  covariates <- c(covariates, add_log_covariate(panel_data, "contributors", "contributors_log"))
} else if ("users_involved" %in% names(panel_data)) {
  covariates <- c(covariates, add_log_covariate(panel_data, "users_involved", "contributors_log"))
}

# Original-paper-aligned time-varying covariates when available.
covariates <- c(covariates, add_log_covariate(panel_data, "age", "age_log"))
covariates <- c(covariates, add_log_covariate(panel_data, "stars", "stars_log"))
covariates <- c(covariates, add_log_covariate(panel_data, "issues", "issues_log"))

# Include ncloc only if available and complete.
# This may be missing in non-SonarQube velocity panels, so keep it optional.
covariates <- c(covariates, add_log_covariate(panel_data, "ncloc", "log_ncloc"))

covariates <- unique(covariates[!is.na(covariates) & nzchar(covariates)])

model_required_cols <- c("log_commits", "log_lines_added")
complete_cols <- c(model_required_cols, covariates)

panel_data <- panel_data[complete.cases(panel_data[, ..complete_cols])]

covariate_availability <- data.frame(
  covariate = c("contributors_log", "age_log", "stars_log", "issues_log", "log_ncloc"),
  included = c("contributors_log", "age_log", "stars_log", "issues_log", "log_ncloc") %in% covariates
)

print(covariate_availability)

fwrite(
  covariate_availability,
  file.path(out_dir, "borusyak_velocity_covariate_availability.csv")
)

cat("Rows after readiness and cohort filtering:", nrow(panel_data), "\n")
cat("Repos after filtering:", uniqueN(panel_data$repo_id), "\n")
cat("Treated repos:", uniqueN(panel_data[treated == 1, repo_id]), "\n")
cat("Control repos:", uniqueN(panel_data[treated == 0, repo_id]), "\n")
cat("Time id range:", min(panel_data$time_id), "to", max(panel_data$time_id), "\n")
cat("Covariates:", ifelse(length(covariates) == 0, "none", paste(covariates, collapse = ", ")), "\n")
```

# Estimation Input Summary

```{r input-summary}
input_summary <- panel_data[, .(
  rows = .N,
  repos = uniqueN(repo_id),
  mean_commits = mean(commits, na.rm = TRUE),
  mean_lines_added = mean(lines_added, na.rm = TRUE),
  mean_log_commits = mean(log_commits, na.rm = TRUE),
  mean_log_lines_added = mean(log_lines_added, na.rm = TRUE),
  mean_contributors_log = if ("contributors_log" %in% names(panel_data)) mean(contributors_log, na.rm = TRUE) else NA_real_
), by = dataset_source]

print(input_summary)

fwrite(
  input_summary,
  file.path(out_dir, "borusyak_velocity_input_summary.csv")
)

event_time_counts <- panel_data[treated == 1, .N, by = time_to_event_calc][order(time_to_event_calc)]
print(event_time_counts)

fwrite(
  event_time_counts,
  file.path(out_dir, "borusyak_velocity_event_time_counts.csv")
)
```

# Panel Checks After Filtering

```{r panel-checks-after-filter}
control_post_event_sum <- if ("post_event" %in% names(panel_data)) {
  sum(panel_data[treated == 0]$post_event, na.rm = TRUE)
} else {
  NA_integer_
}

treated_post_rows <- panel_data[treated == 1 & time_id >= event_id, .N]

post_event_mismatch_rows <- if ("post_event" %in% names(panel_data)) {
  expected_post <- ifelse(panel_data$treated == 1L & panel_data$time_id >= panel_data$event_id, 1L, 0L)
  sum(as.integer(panel_data$post_event) != expected_post, na.rm = TRUE)
} else {
  NA_integer_
}

panel_checks_filtered <- data.frame(
  check = c(
    "panel_label",
    "rows",
    "repos",
    "treatment_rows",
    "control_rows",
    "treated_repos",
    "control_repos",
    "control_post_event_sum",
    "treated_post_rows",
    "post_event_mismatch_rows",
    "analysis_ready_velocity_did_rows",
    "commits_nonmissing",
    "lines_added_nonmissing",
    "log_commits_nonmissing",
    "log_lines_added_nonmissing",
    "min_time",
    "max_time"
  ),
  value = c(
    panel_label,
    nrow(panel_data),
    uniqueN(panel_data$repo_id),
    sum(panel_data$dataset_source == "treatment", na.rm = TRUE),
    sum(panel_data$dataset_source == "control", na.rm = TRUE),
    uniqueN(panel_data[treated == 1]$repo_id),
    uniqueN(panel_data[treated == 0]$repo_id),
    control_post_event_sum,
    treated_post_rows,
    post_event_mismatch_rows,
    nrow(panel_data),
    sum(!is.na(panel_data$commits)),
    sum(!is.na(panel_data$lines_added)),
    sum(!is.na(panel_data$log_commits)),
    sum(!is.na(panel_data$log_lines_added)),
    min(panel_data$time, na.rm = TRUE),
    max(panel_data$time, na.rm = TRUE)
  )
)

print(panel_checks_filtered)

fwrite(
  panel_checks_filtered,
  file.path(out_dir, "borusyak_velocity_panel_checks.csv")
)
```

# Outcomes and First Stage

```{r outcomes-first-stage}
outcome_vars <- c(
  "log_commits",
  "log_lines_added"
)

outcome_names <- c(
  "Commits",
  "Lines Added"
)

if (length(covariates) == 0) {
  first_stage_rhs <- "1"
} else {
  first_stage_rhs <- paste(covariates, collapse = " + ")
}

first_stage_formula <- as.formula(
  paste0("~ ", first_stage_rhs, " | repo_id + time_id")
)

# The shared runners pass `data` straight to didimputation::did_imputation(),
# so convert the data.table once here (the previous inline runners converted
# inside the function).
panel_data_df <- as.data.frame(panel_data)

cat("Outcomes:\n")
print(data.frame(outcome = outcome_vars, label = outcome_names))

cat("\nFirst-stage formula:\n")
print(first_stage_formula)
```

# Static Borusyak Effects

```{r static-effects}
static_results <- list()
static_errors <- list()

for (var in outcome_vars) {
  cat("Running static Borusyak model for:", var, "\n")

  static_results[[var]] <- tryCatch(
    run_borusyak_static(
      data = panel_data_df,
      outcome_var = var,
      first_stage_formula = first_stage_formula,
      idname = "repo_id",
      tname = "time_id",
      gname = "event_id"
    ),
    error = function(e) {
      static_errors[[var]] <<- conditionMessage(e)
      NULL
    }
  )
}

static_df <- dplyr::bind_rows(lapply(outcome_vars, function(v) {
  extract_static_result(static_results[[v]], v)
}))

static_df <- fill_missing_p_values(static_df)

static_df$outcome_label <- outcome_names[match(static_df$outcome, outcome_vars)]
static_df$panel <- panel_label

static_df$estimate_pct <- (exp(static_df$estimate) - 1) * 100
static_df$conf_low_pct <- (exp(static_df$conf_low) - 1) * 100
static_df$conf_high_pct <- (exp(static_df$conf_high) - 1) * 100

print(static_df)

fwrite(
  static_df,
  file.path(out_dir, "borusyak_velocity_static_effects.csv")
)

if (length(static_errors) > 0) {
  static_error_df <- data.frame(
    panel = panel_label,
    outcome = names(static_errors),
    error = unlist(static_errors),
    row.names = NULL
  )

  print(static_error_df)

  fwrite(
    static_error_df,
    file.path(out_dir, "borusyak_velocity_static_errors.csv")
  )
}
```

# Dynamic Borusyak Effects

```{r dynamic-effects}
dynamic_results <- list()
dynamic_errors <- list()

for (var in outcome_vars) {
  cat("Running dynamic Borusyak model for:", var, "\n")

  dynamic_results[[var]] <- tryCatch(
    run_borusyak_dynamic(
      data = panel_data_df,
      outcome_var = var,
      first_stage_formula = first_stage_formula,
      horizon = -6:6,
      pretrends = -6:-2,
      idname = "repo_id",
      tname = "time_id",
      gname = "event_id"
    ),
    error = function(e) {
      dynamic_errors[[var]] <<- conditionMessage(e)
      NULL
    }
  )
}

dynamic_df <- dplyr::bind_rows(lapply(seq_along(outcome_vars), function(i) {
  v <- outcome_vars[i]

  extract_dynamic_result(
    dynamic_results[[v]],
    outcome = v,
    outcome_label = outcome_names[i],
    min_horizon = -6,
    max_horizon = 6
  )
}))

dynamic_df <- fill_missing_p_values(dynamic_df)

if (nrow(dynamic_df) > 0) {
  dynamic_df$panel <- panel_label
  dynamic_df$estimate_pct <- (exp(dynamic_df$estimate) - 1) * 100
  dynamic_df$conf_low_pct <- (exp(dynamic_df$conf_low) - 1) * 100
  dynamic_df$conf_high_pct <- (exp(dynamic_df$conf_high) - 1) * 100
}

print(dynamic_df)

fwrite(
  dynamic_df,
  file.path(out_dir, "borusyak_velocity_dynamic_effects.csv")
)

if (length(dynamic_errors) > 0) {
  dynamic_error_df <- data.frame(
    panel = panel_label,
    outcome = names(dynamic_errors),
    error = unlist(dynamic_errors),
    row.names = NULL
  )

  print(dynamic_error_df)

  fwrite(
    dynamic_error_df,
    file.path(out_dir, "borusyak_velocity_dynamic_errors.csv")
  )
}
```

# Dynamic Plot

```{r dynamic-plot, fig.width=10, fig.height=5}
if (nrow(dynamic_df) > 0) {
  p <- ggplot(dynamic_df, aes(x = time, y = estimate)) +
    geom_hline(yintercept = 0, linetype = "dashed") +
    geom_vline(xintercept = -1, linetype = "dotted") +
    geom_errorbar(aes(ymin = conf_low, ymax = conf_high), width = 0.15) +
    geom_point() +
    geom_line() +
    facet_wrap(~ outcome_label, scales = "free_y") +
    labs(
      title = paste("Borusyak Dynamic Effects for Velocity Outcomes:", panel_label),
      x = "Months relative to Cursor adoption",
      y = "Estimate on log scale"
    ) +
    theme_minimal()

  print(p)

  ggsave(
    filename = file.path(out_dir, "dynamic_effects_borusyak_velocity.pdf"),
    plot = p,
    width = 10,
    height = 5
  )
} else {
  cat("No dynamic effects to plot.\n")
}
```

# Metadata

```{r metadata}
metadata <- data.frame(
  key = c(
    "script",
    "helpers",
    "panel_label",
    "panel_path",
    "out_dir",
    "outcomes",
    "covariates",
    "estimator",
    "time_encoding",
    "cohort_filter",
    "input_source",
    "interpretation_note"
  ),
  value = c(
    "proc_r/DiffInDiffBorusyak_velocity_v2.Rmd",
    helpers_path,
    panel_label,
    panel_path,
    out_dir,
    paste(outcome_vars, collapse = ", "),
    ifelse(length(covariates) == 0, "none", paste(covariates, collapse = " + ")),
    "Borusyak imputation via didimputation::did_imputation",
    "YYYY-MM converted to month_id = year * 12 + month",
    "controls kept with event_yyyymm == 0; treatment cohorts kept if 202407 < event_yyyymm <= 202503",
    "run8e final matched panel",
    "Use main panel as primary analysis and other panels as robustness checks"
  )
)

print(metadata)

fwrite(
  metadata,
  file.path(out_dir, "borusyak_velocity_metadata.csv")
)
```
