---
title: "Diff-in-Diff Borusyak: Python SonarQube Quality Outcomes"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = TRUE, message = TRUE)
options(bitmapType = "cairo")

project_root <- Sys.getenv("PROJECT_ROOT", unset = normalizePath(".", mustWork = TRUE))
project_root <- normalizePath(project_root, mustWork = TRUE)

resolve_project_path <- function(path_value) {
  if (is.null(path_value) || path_value == "") {
    return("")
  }

  if (grepl("^/", path_value)) {
    return(normalizePath(path_value, mustWork = FALSE))
  }

  normalizePath(file.path(project_root, path_value), mustWork = FALSE)
}

panel_path <- resolve_project_path(Sys.getenv("PANEL_PATH", unset = ""))
out_dir <- resolve_project_path(Sys.getenv("OUT_DIR", unset = ""))
panel_label <- Sys.getenv("PANEL_LABEL", unset = "panel")
covariate_mode_requested <- tolower(Sys.getenv("COVARIATE_MODE", unset = "auto"))
paper_time_mode_requested <- tolower(
  Sys.getenv("PAPER_TIME_MODE", unset = "original_yyyymm")
)

valid_covariate_modes <- c("auto", "paper", "python_v2")
if (!(covariate_mode_requested %in% valid_covariate_modes)) {
  stop(
    "COVARIATE_MODE must be one of: ",
    paste(valid_covariate_modes, collapse = ", "),
    ". Got: ",
    covariate_mode_requested
  )
}

valid_paper_time_modes <- c("original_yyyymm", "calendar_month")
if (!(paper_time_mode_requested %in% valid_paper_time_modes)) {
  stop(
    "PAPER_TIME_MODE must be one of: ",
    paste(valid_paper_time_modes, collapse = ", "),
    ". Got: ",
    paper_time_mode_requested
  )
}

if (panel_path == "") {
  stop("PANEL_PATH environment variable is required.")
}

if (out_dir == "") {
  out_dir <- file.path(
    project_root,
    "repo_python/did_final/quality_did_borusyak",
    panel_label
  )
}

dir.create(out_dir, recursive = TRUE, showWarnings = FALSE)
```

# Purpose

This notebook runs Borusyak imputation DiD analysis for Python SonarQube quality outcomes.

It supports both input structures:

1. The Python v2 complete-case quality panel.
2. The paper-compatible `panel_event_monthly_quality_py.csv` panel produced by run-py-2e.

When the paper-compatible columns are available, the default `auto` mode reproduces the original `DiffInDiffBorusyak.Rmd` preprocessing and estimator configuration:

- `age`, `contributors`, `stars`, and `issues` are transformed with `log1p()`.
- `ncloc` remains on its original scale.
- `time` and `event` use numeric `YYYYMM` encoding, matching the original notebook.
- The first-stage covariates are `age + ncloc + contributors + stars + issues`.

For paper mode, `PAPER_TIME_MODE=original_yyyymm` reproduces the original notebook exactly. `PAPER_TIME_MODE=calendar_month` keeps the same paper covariate scaling but uses a sequential calendar-month index for a corrected sensitivity check.

The `python_v2` mode retains the sequential calendar-month encoding and the existing `contributors_log + log_ncloc` first stage.

# Load Packages and Helper Functions

```{r load-packages}
library(data.table)
library(dplyr)
library(ggplot2)
library(didimputation)

helper_path <- file.path(project_root, "proc_r/diff_in_diff_borusyak_helpers.R")

if (!file.exists(helper_path)) {
  stop("Helper file not found: ", helper_path)
}

source(helper_path)
```

# Utility Functions

```{r utility-functions}
normalize_yyyymm <- function(x) {
  x <- as.character(x)
  x[x %in% c("", "NA", "NaN", "NULL", "None")] <- NA_character_
  x <- gsub("-", "", x)
  suppressWarnings(as.integer(x))
}

yyyymm_to_month_id <- function(x) {
  x <- as.integer(x)
  year <- x %/% 100L
  month <- x %% 100L

  out <- year * 12L + month
  out[is.na(x) | month < 1L | month > 12L] <- NA_integer_

  out
}

require_columns <- function(data, required, label) {
  missing <- setdiff(required, names(data))
  if (length(missing) > 0) {
    stop(label, " missing required columns: ", paste(missing, collapse = ", "))
  }
}

numeric_if_present <- function(data, columns) {
  for (column_name in intersect(columns, names(data))) {
    set(data, j = column_name, value = suppressWarnings(as.numeric(data[[column_name]])))
  }

  invisible(data)
}

count_nonmissing <- function(data, column_name) {
  if (!(column_name %in% names(data))) {
    return(NA_integer_)
  }

  sum(!is.na(data[[column_name]]))
}

sum_if_present <- function(data, column_name) {
  if (!(column_name %in% names(data))) {
    return(NA_real_)
  }

  sum(as.numeric(data[[column_name]]), na.rm = TRUE)
}
```

# Load and Normalize Quality Panel

```{r load-panel}
cat("Project root:", project_root, "\n")
cat("Panel label:", panel_label, "\n")
cat("Panel path:", panel_path, "\n")
cat("Output dir:", out_dir, "\n")
cat("Requested covariate mode:", covariate_mode_requested, "\n")
cat("Requested paper time mode:", paper_time_mode_requested, "\n")

if (!file.exists(panel_path)) {
  stop("Panel file not found: ", panel_path)
}

panel_raw <- fread(panel_path)
original_column_names <- names(panel_raw)

base_required_cols <- c(
  "repo_name",
  "time",
  "event",
  "dataset_source",
  "post_event",
  "time_to_event",
  "is_treatment",
  "ncloc"
)

require_columns(panel_raw, base_required_cols, "Input panel")

paper_schema_markers <- c(
  "bugs",
  "vulnerabilities",
  "code_smells",
  "duplicated_lines_density",
  "cognitive_complexity",
  "age",
  "contributors",
  "stars",
  "issues"
)

input_schema <- if (all(paper_schema_markers %in% original_column_names)) {
  "paper_same_column"
} else {
  "python_v2"
}

# Build the quality outcomes expected by this notebook when the input uses
# the paper's panel_event_monthly.csv column structure.
if (!("static_analysis_warnings" %in% names(panel_raw))) {
  require_columns(
    panel_raw,
    c("bugs", "vulnerabilities", "code_smells"),
    "Input panel for static analysis warnings"
  )

  numeric_if_present(panel_raw, c("bugs", "vulnerabilities", "code_smells"))
  panel_raw[, static_analysis_warnings :=
    bugs + vulnerabilities + code_smells]
}

if (!("duplicate_line_density" %in% names(panel_raw))) {
  require_columns(
    panel_raw,
    "duplicated_lines_density",
    "Input panel for duplicate line density"
  )

  panel_raw[, duplicate_line_density := duplicated_lines_density]
}

if (!("code_complexity" %in% names(panel_raw))) {
  require_columns(
    panel_raw,
    "cognitive_complexity",
    "Input panel for code complexity"
  )

  panel_raw[, code_complexity := cognitive_complexity]
}

numeric_if_present(
  panel_raw,
  c(
    "static_analysis_warnings",
    "duplicate_line_density",
    "code_complexity",
    "ncloc",
    "contributors",
    "age",
    "stars",
    "issues"
  )
)

if (!("log_static_analysis_warnings" %in% names(panel_raw))) {
  panel_raw[, log_static_analysis_warnings :=
    fifelse(
      !is.na(static_analysis_warnings) & static_analysis_warnings >= 0,
      log1p(static_analysis_warnings),
      NA_real_
    )]
}

if (!("log_duplicate_line_density" %in% names(panel_raw))) {
  panel_raw[, log_duplicate_line_density :=
    fifelse(
      !is.na(duplicate_line_density) & duplicate_line_density >= 0,
      log1p(duplicate_line_density),
      NA_real_
    )]
}

if (!("log_code_complexity" %in% names(panel_raw))) {
  panel_raw[, log_code_complexity :=
    fifelse(
      !is.na(code_complexity) & code_complexity >= 0,
      log1p(code_complexity),
      NA_real_
    )]
}

if (!("log_ncloc" %in% names(panel_raw))) {
  panel_raw[, log_ncloc :=
    fifelse(!is.na(ncloc) & ncloc >= 0, log1p(ncloc), NA_real_)]
}

if (!("contributors_log" %in% names(panel_raw)) &&
    "contributors" %in% names(panel_raw)) {
  panel_raw[, contributors_log :=
    fifelse(
      !is.na(contributors) & contributors >= 0,
      log1p(contributors),
      NA_real_
    )]
}

# In the paper panel, is_treatment is time-varying. A repository-level
# ever-treated indicator must therefore be derived from dataset_source.
if (!("ever_treated" %in% names(panel_raw))) {
  panel_raw[, ever_treated := as.integer(dataset_source == "treatment")]
}

panel_raw[, ever_treated := as.integer(as.numeric(ever_treated) > 0)]
panel_raw[, post_event := suppressWarnings(as.numeric(post_event))]
panel_raw[, time_to_event := suppressWarnings(as.numeric(time_to_event))]
panel_raw[, is_treatment := suppressWarnings(as.numeric(is_treatment))]

core_quality_columns <- c(
  "static_analysis_warnings",
  "duplicate_line_density",
  "code_complexity",
  "log_static_analysis_warnings",
  "log_duplicate_line_density",
  "log_code_complexity"
)

require_columns(panel_raw, core_quality_columns, "Normalized quality panel")

if (!("analysis_ready_quality_did" %in% names(panel_raw))) {
  duplicate_key <- duplicated(
    panel_raw,
    by = c("repo_name", "time", "dataset_source")
  )

  panel_raw[, analysis_ready_quality_did := as.integer(
    dataset_source %in% c("treatment", "control") &
      !duplicate_key &
      complete.cases(.SD)
  ), .SDcols = core_quality_columns]
}

panel_raw[, analysis_ready_quality_did :=
  as.integer(as.numeric(analysis_ready_quality_did) > 0)]

cat("Detected input schema:", input_schema, "\n")
cat("Loaded rows:", nrow(panel_raw), "\n")
cat("Loaded repos:", uniqueN(panel_raw$repo_name), "\n")
cat("Months:", min(panel_raw$time), "to", max(panel_raw$time), "\n")
```

# Panel Sanity Checks

```{r panel-checks}
panel_checks <- data.frame(
  check = c(
    "panel_label",
    "input_schema",
    "covariate_mode_requested",
    "rows",
    "repos",
    "treatment_rows",
    "control_rows",
    "treated_repos",
    "control_repos",
    "control_post_event_sum",
    "treated_post_rows",
    "post_event_mismatch_rows",
    "analysis_ready_quality_did_rows",
    "static_analysis_warnings_nonmissing",
    "duplicate_line_density_nonmissing",
    "code_complexity_nonmissing",
    "age_nonmissing",
    "ncloc_nonmissing",
    "contributors_nonmissing",
    "stars_nonmissing",
    "issues_nonmissing",
    "sonarqube_latest_commit_missing",
    "sonarqube_any_raw_metric_missing_sum",
    "sonarqube_all_raw_metrics_missing_sum",
    "sonarqube_ncloc_zero_sum",
    "sonarqube_quality_outcomes_complete_sum"
  ),
  value = c(
    panel_label,
    input_schema,
    covariate_mode_requested,
    nrow(panel_raw),
    uniqueN(panel_raw$repo_name),
    sum(panel_raw$dataset_source == "treatment", na.rm = TRUE),
    sum(panel_raw$dataset_source == "control", na.rm = TRUE),
    uniqueN(panel_raw[ever_treated == 1, repo_name]),
    uniqueN(panel_raw[ever_treated == 0, repo_name]),
    sum(panel_raw[ever_treated == 0, post_event], na.rm = TRUE),
    sum(panel_raw[ever_treated == 1, post_event], na.rm = TRUE),
    sum(
      panel_raw$ever_treated == 1 &
        !is.na(panel_raw$time_to_event) &
        ((panel_raw$time_to_event >= 0) != (panel_raw$post_event == 1)),
      na.rm = TRUE
    ),
    sum(panel_raw$analysis_ready_quality_did, na.rm = TRUE),
    count_nonmissing(panel_raw, "static_analysis_warnings"),
    count_nonmissing(panel_raw, "duplicate_line_density"),
    count_nonmissing(panel_raw, "code_complexity"),
    count_nonmissing(panel_raw, "age"),
    count_nonmissing(panel_raw, "ncloc"),
    count_nonmissing(panel_raw, "contributors"),
    count_nonmissing(panel_raw, "stars"),
    count_nonmissing(panel_raw, "issues"),
    if ("sonarqube_latest_commit" %in% names(panel_raw)) {
      sum(is.na(panel_raw$sonarqube_latest_commit))
    } else {
      NA
    },
    sum_if_present(panel_raw, "sonarqube_any_raw_metric_missing"),
    sum_if_present(panel_raw, "sonarqube_all_raw_metrics_missing"),
    sum_if_present(panel_raw, "sonarqube_ncloc_zero"),
    sum_if_present(panel_raw, "sonarqube_quality_outcomes_complete")
  ),
  stringsAsFactors = FALSE
)

print(panel_checks)

fwrite(
  panel_checks,
  file.path(out_dir, "borusyak_quality_panel_checks.csv")
)
```

# Prepare Data for Borusyak Estimator

```{r prepare-data}
panel_data <- copy(panel_raw)
panel_data <- panel_data[analysis_ready_quality_did == 1]

panel_data[, time_yyyymm := normalize_yyyymm(time)]

event_yyyymm_raw <- normalize_yyyymm(panel_data$event)
event_yyyymm_raw[is.na(event_yyyymm_raw)] <- 0L
panel_data[, event_yyyymm := event_yyyymm_raw]

# Match the original notebook's treatment-cohort restriction.
panel_data <- panel_data[
  event_yyyymm == 0L |
    (event_yyyymm > 202407L & event_yyyymm <= 202503L)
]

panel_data[, repo_name_str := repo_name]
panel_data[, repo_id := as.integer(factor(repo_name_str))]

numeric_if_present(
  panel_data,
  c(
    "static_analysis_warnings",
    "duplicate_line_density",
    "code_complexity",
    "log_static_analysis_warnings",
    "log_duplicate_line_density",
    "log_code_complexity",
    "age",
    "ncloc",
    "contributors",
    "stars",
    "issues",
    "issue_comments",
    "contributors_log",
    "log_ncloc"
  )
)

paper_covariates <- c("age", "ncloc", "contributors", "stars", "issues")
python_v2_covariates <- c("contributors_log", "log_ncloc")

paper_covariates_available <- all(paper_covariates %in% names(panel_data))
python_v2_covariates_available <- all(
  python_v2_covariates %in% names(panel_data)
)

if (covariate_mode_requested == "auto") {
  covariate_mode_used <- if (paper_covariates_available) {
    "paper"
  } else {
    "python_v2"
  }
} else {
  covariate_mode_used <- covariate_mode_requested
}

if (covariate_mode_used == "paper") {
  require_columns(
    panel_data,
    paper_covariates,
    "Paper covariate mode"
  )

  # Reproduce the original DiffInDiffBorusyak.Rmd covariate scaling.
  # The original notebook overwrites these four columns with log1p values,
  # while ncloc remains untransformed.
  paper_log_covariates <- c("age", "contributors", "stars", "issues")
  for (column_name in paper_log_covariates) {
    x <- panel_data[[column_name]]
    set(
      panel_data,
      j = column_name,
      value = fifelse(!is.na(x) & x >= 0, log1p(x), NA_real_)
    )
  }

  if ("issue_comments" %in% names(panel_data)) {
    x <- panel_data[["issue_comments"]]
    set(
      panel_data,
      j = "issue_comments",
      value = fifelse(!is.na(x) & x >= 0, log1p(x), NA_real_)
    )
  }

  if (paper_time_mode_requested == "original_yyyymm") {
    # Reproduce the original notebook's numeric YYYYMM encoding exactly.
    # This is intentionally different from a sequential calendar-month index.
    panel_data[, time_id := time_yyyymm]
    panel_data[, event_id := fifelse(event_yyyymm == 0L, 0L, event_yyyymm)]
    time_encoding_used <- "paper_original_numeric_yyyymm"
  } else {
    # Sensitivity mode with a true sequential calendar-month index.
    panel_data[, time_id := yyyymm_to_month_id(time_yyyymm)]
    panel_data[, event_id := fifelse(
      event_yyyymm == 0L,
      0L,
      yyyymm_to_month_id(event_yyyymm)
    )]
    time_encoding_used <- "sequential_calendar_month_id"
  }

  covariates <- paper_covariates
  covariate_scaling_used <- paste(
    "log1p(age, contributors, stars, issues);",
    "raw ncloc"
  )
} else {
  if (!python_v2_covariates_available) {
    stop(
      "Python v2 covariate mode requires: ",
      paste(python_v2_covariates, collapse = ", ")
    )
  }

  panel_data[, time_id := yyyymm_to_month_id(time_yyyymm)]
  panel_data[, event_id := fifelse(
    event_yyyymm == 0L,
    0L,
    yyyymm_to_month_id(event_yyyymm)
  )]

  covariates <- python_v2_covariates
  time_encoding_used <- "sequential_calendar_month_id"
  covariate_scaling_used <- "contributors_log + log_ncloc"
}

panel_data <- panel_data[!is.na(time_id)]
panel_data <- panel_data[event_id == 0L | !is.na(event_id)]
panel_data[, treated := as.integer(event_id > 0L)]

outcome_vars <- c(
  "log_static_analysis_warnings",
  "log_duplicate_line_density",
  "log_code_complexity"
)

outcome_names <- c(
  "Static Analysis Warnings",
  "Duplicate Line Density",
  "Code Complexity"
)

model_required_columns <- c(outcome_vars, covariates)
rows_before_model_complete_filter <- nrow(panel_data)
panel_data <- panel_data[complete.cases(panel_data[, ..model_required_columns])]
rows_removed_by_model_complete_filter <-
  rows_before_model_complete_filter - nrow(panel_data)

if (nrow(panel_data) == 0) {
  stop("No rows remain after outcome and covariate complete-case filtering.")
}

first_stage_rhs <- paste(covariates, collapse = " + ")
first_stage_formula <- as.formula(
  paste0("~ ", first_stage_rhs, " | repo_id + time_id")
)

cat("Detected input schema:", input_schema, "\n")
cat("Covariate mode used:", covariate_mode_used, "\n")
cat("Paper time mode requested:", paper_time_mode_requested, "\n")
cat("Covariate scaling:", covariate_scaling_used, "\n")
cat("Time encoding:", time_encoding_used, "\n")
cat("Rows before model complete-case filter:",
    rows_before_model_complete_filter, "\n")
cat("Rows removed by model complete-case filter:",
    rows_removed_by_model_complete_filter, "\n")
cat("Rows used by models:", nrow(panel_data), "\n")
cat("Treated repos:", uniqueN(panel_data[treated == 1, repo_id]), "\n")
cat("Control repos:", uniqueN(panel_data[treated == 0, repo_id]), "\n")
cat("Time id range:", min(panel_data$time_id), "to", max(panel_data$time_id), "\n")
cat("First-stage formula:\n")
print(first_stage_formula)

quality_summary <- panel_data[, .(
  rows = .N,
  repos = uniqueN(repo_id),
  mean_log_static_warnings = mean(log_static_analysis_warnings, na.rm = TRUE),
  mean_log_duplicate_line_density = mean(log_duplicate_line_density, na.rm = TRUE),
  mean_log_code_complexity = mean(log_code_complexity, na.rm = TRUE),
  mean_ncloc = mean(ncloc, na.rm = TRUE),
  mean_age = if ("age" %in% names(panel_data)) mean(age, na.rm = TRUE) else NA_real_,
  mean_contributors = if ("contributors" %in% names(panel_data)) mean(contributors, na.rm = TRUE) else NA_real_,
  mean_stars = if ("stars" %in% names(panel_data)) mean(stars, na.rm = TRUE) else NA_real_,
  mean_issues = if ("issues" %in% names(panel_data)) mean(issues, na.rm = TRUE) else NA_real_
), by = dataset_source]

print(quality_summary)

fwrite(
  quality_summary,
  file.path(out_dir, "borusyak_quality_input_summary.csv")
)

```

# Outcomes and First Stage

```{r outcomes}
cat("Outcomes:\n")
print(data.frame(outcome = outcome_vars, label = outcome_names))

cat("\nCovariate mode requested:", covariate_mode_requested, "\n")
cat("Covariate mode used:", covariate_mode_used, "\n")
cat("First-stage formula:\n")
print(first_stage_formula)
```

# Static Borusyak Effects

```{r static-effects}
static_results <- list()
static_errors <- list()

for (var in outcome_vars) {
  cat("Running static Borusyak model for:", var, "\n")

  static_results[[var]] <- tryCatch(
    run_borusyak_static(
      data = panel_data,
      outcome_var = var,
      first_stage_formula = first_stage_formula,
      idname = "repo_id",
      tname = "time_id",
      gname = "event_id"
    ),
    error = function(e) {
      static_errors[[var]] <<- conditionMessage(e)
      NULL
    }
  )
}

static_df <- bind_rows(lapply(outcome_vars, function(v) {
  if (is.null(static_results[[v]])) {
    return(data.frame(
      outcome = v,
      term = "treat",
      estimate = NA_real_,
      std_error = NA_real_,
      conf_low = NA_real_,
      conf_high = NA_real_,
      p_value = NA_real_,
      note = "model failed"
    ))
  }

  extract_static_result(static_results[[v]], v)
}))

static_df$outcome_label <- outcome_names[match(static_df$outcome, outcome_vars)]
static_df$panel <- panel_label
static_df$covariate_mode <- covariate_mode_used

print(static_df)

fwrite(
  static_df,
  file.path(out_dir, "borusyak_quality_static_effects.csv")
)

if (length(static_errors) > 0) {
  static_error_df <- data.frame(
    panel = panel_label,
    covariate_mode = covariate_mode_used,
    outcome = names(static_errors),
    error = unlist(static_errors),
    row.names = NULL
  )

  print(static_error_df)

  fwrite(
    static_error_df,
    file.path(out_dir, "borusyak_quality_static_errors.csv")
  )
}
```

# Dynamic Borusyak Effects

```{r dynamic-effects}
dynamic_results <- list()
dynamic_errors <- list()

for (var in outcome_vars) {
  cat("Running dynamic Borusyak model for:", var, "\n")

  dynamic_results[[var]] <- tryCatch(
    run_borusyak_dynamic(
      data = panel_data,
      outcome_var = var,
      first_stage_formula = first_stage_formula,
      horizon = -6:6,
      pretrends = -6:-2,
      idname = "repo_id",
      tname = "time_id",
      gname = "event_id"
    ),
    error = function(e) {
      dynamic_errors[[var]] <<- conditionMessage(e)
      NULL
    }
  )
}

dynamic_df <- bind_rows(lapply(seq_along(outcome_vars), function(i) {
  v <- outcome_vars[i]

  if (is.null(dynamic_results[[v]])) {
    return(data.frame())
  }

  extract_dynamic_result(
    dynamic_results[[v]],
    outcome = v,
    outcome_label = outcome_names[i],
    min_horizon = -6,
    max_horizon = 6
  )
}))

if (nrow(dynamic_df) > 0) {
  dynamic_df$panel <- panel_label
  dynamic_df$covariate_mode <- covariate_mode_used
}

print(dynamic_df)

fwrite(
  dynamic_df,
  file.path(out_dir, "borusyak_quality_dynamic_effects.csv")
)

if (length(dynamic_errors) > 0) {
  dynamic_error_df <- data.frame(
    panel = panel_label,
    covariate_mode = covariate_mode_used,
    outcome = names(dynamic_errors),
    error = unlist(dynamic_errors),
    row.names = NULL
  )

  print(dynamic_error_df)

  fwrite(
    dynamic_error_df,
    file.path(out_dir, "borusyak_quality_dynamic_errors.csv")
  )
}
```

# Dynamic Plot

```{r dynamic-plot, fig.width=9, fig.height=3.5}
if (nrow(dynamic_df) > 0) {
  dynamic_df$outcome_label <- factor(
    dynamic_df$outcome_label,
    levels = outcome_names
  )

  p <- ggplot(dynamic_df, aes(x = time, y = estimate)) +
    geom_errorbar(
      data = subset(dynamic_df, significant %in% TRUE),
      aes(ymin = conf_low, ymax = conf_high),
      width = 0.4,
      linetype = "solid"
    ) +
    geom_errorbar(
      data = subset(dynamic_df, !(significant %in% TRUE)),
      aes(ymin = conf_low, ymax = conf_high),
      width = 0.4,
      linetype = "dotted"
    ) +
    geom_point(
      data = subset(dynamic_df, significant %in% TRUE),
      shape = 19,
      size = 1.7
    ) +
    geom_point(
      data = subset(dynamic_df, !(significant %in% TRUE)),
      shape = 21,
      fill = "transparent",
      size = 1.7
    ) +
    geom_hline(yintercept = 0, linetype = "dashed") +
    geom_vline(xintercept = -0.5, linetype = "dashed") +
    scale_x_continuous(breaks = -6:6) +
    coord_cartesian(xlim = c(-6.5, 6.5)) +
    facet_wrap(~ outcome_label, scales = "free_y", nrow = 1) +
    labs(
      title = paste("Borusyak Quality DiD:", panel_label),
      subtitle = paste(
        "Mode:", covariate_mode_used,
        "| Time:", time_encoding_used,
        "| Covariates:", first_stage_rhs
      ),
      x = "Months Relative to Cursor Adoption",
      y = "Treatment Effect",
      caption = "Filled dots: CI excludes 0. Hollow dots: CI includes 0."
    ) +
    theme_minimal() +
    theme(
      panel.grid.minor = element_blank(),
      plot.caption = element_text(hjust = 0.5, size = 8)
    )

  print(p)

  ggsave(
    filename = file.path(out_dir, "dynamic_effects_borusyak_quality.pdf"),
    plot = p,
    width = 9,
    height = 3.5
  )
} else {
  cat("No dynamic effects to plot.\n")
}
```

# Metadata

```{r metadata}
metadata <- data.frame(
  key = c(
    "script",
    "helper_file",
    "panel_label",
    "panel_path",
    "out_dir",
    "input_schema",
    "covariate_mode_requested",
    "covariate_mode_used",
    "paper_time_mode_requested",
    "outcomes",
    "covariates",
    "first_stage_formula",
    "rows_before_model_complete_filter",
    "rows_removed_by_model_complete_filter",
    "rows_used_by_models",
    "estimator",
    "time_encoding",
    "covariate_scaling",
    "input_source",
    "interpretation_note"
  ),
  value = c(
    "proc_r/DiffInDiffBorusyak_quality_python_v2.Rmd",
    "proc_r/diff_in_diff_borusyak_helpers.R",
    panel_label,
    panel_path,
    out_dir,
    input_schema,
    covariate_mode_requested,
    covariate_mode_used,
    paper_time_mode_requested,
    paste(outcome_vars, collapse = ", "),
    first_stage_rhs,
    paste(deparse(first_stage_formula), collapse = " "),
    rows_before_model_complete_filter,
    rows_removed_by_model_complete_filter,
    nrow(panel_data),
    "Borusyak imputation via didimputation::did_imputation",
    time_encoding_used,
    covariate_scaling_used,
    if (input_schema == "paper_same_column") {
      "run-py-2e paper-compatible overlap panel with regenerated SonarQube outcomes"
    } else {
      "run-py-2e complete-case quality DiD input"
    },
    if (covariate_mode_used == "paper") {
      paste(
        "Original-Rmd-compatible first stage:",
        "log1p(age, contributors, stars, issues) + raw ncloc;",
        time_encoding_used
      )
    } else {
      "Python v2 first stage: contributors_log + log_ncloc"
    }
  ),
  stringsAsFactors = FALSE
)

print(metadata)

fwrite(
  metadata,
  file.path(out_dir, "borusyak_quality_metadata.csv")
)
```

# Session Info

```{r session-info}
sessionInfo()
```
