---
title: "Diff-in-Diff Borusyak: AGC-Like Regular-Function Unique Bodies"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = TRUE, message = TRUE)
options(bitmapType = "cairo")

project_root <- Sys.getenv(
  "PROJECT_ROOT",
  unset = normalizePath(".", mustWork = TRUE)
)
project_root <- normalizePath(project_root, mustWork = TRUE)

resolve_project_path <- function(path_value) {
  if (is.null(path_value) || path_value == "") {
    return("")
  }
  if (grepl("^/", path_value)) {
    return(normalizePath(path_value, mustWork = FALSE))
  }
  normalizePath(file.path(project_root, path_value), mustWork = FALSE)
}

panel_path <- resolve_project_path(Sys.getenv("PANEL_PATH", unset = ""))
out_dir <- resolve_project_path(Sys.getenv("OUT_DIR", unset = ""))
panel_label <- Sys.getenv("PANEL_LABEL", unset = "panel")
specification_name <- Sys.getenv(
  "SPECIFICATION_NAME",
  unset = "range100_200"
)
ncloc_spec <- tolower(Sys.getenv("NCLOC_SPEC", unset = "python_snapshot"))
time_mode <- tolower(Sys.getenv("TIME_MODE", unset = "calendar_month"))
parse_exclusion_mode <- tolower(
  Sys.getenv("PARSE_EXCLUSION_MODE", unset = "parse_clean")
)
helper_path <- resolve_project_path(
  Sys.getenv(
    "HELPER_FILE",
    unset = "proc_r/diff_in_diff_borusyak_helpers.R"
  )
)

valid_ncloc_specs <- c("paper", "python_snapshot")
valid_time_modes <- c("original_yyyymm", "calendar_month")
valid_parse_exclusion_modes <- c("all", "parse_clean")

if (!(ncloc_spec %in% valid_ncloc_specs)) {
  stop("NCLOC_SPEC must be paper or python_snapshot. Got: ", ncloc_spec)
}
if (!(time_mode %in% valid_time_modes)) {
  stop(
    "TIME_MODE must be original_yyyymm or calendar_month. Got: ",
    time_mode
  )
}
if (!(parse_exclusion_mode %in% valid_parse_exclusion_modes)) {
  stop(
    "PARSE_EXCLUSION_MODE must be all or parse_clean. Got: ",
    parse_exclusion_mode
  )
}
if (panel_path == "") {
  stop("PANEL_PATH environment variable is required.")
}
if (out_dir == "") {
  out_dir <- file.path(
    project_root,
    "repo_python/run-py-7f/strict/specifications",
    specification_name,
    paste0(ncloc_spec, "_ncloc"),
    time_mode,
    parse_exclusion_mode
  )
}

dir.create(out_dir, recursive = TRUE, showWarnings = FALSE)
```

# Purpose

This notebook estimates the effect of Cursor adoption on the monthly number of
**distinct AGC-like regular-function implementation bodies**.

The focused estimand is intentionally narrow:

1. Only synchronous module-level Python functions are included
   (`function_kind == "module_function"`).
2. Only bodies classified as AGC-like by the frozen NPR detector are counted.
3. The counting unit is a distinct `function_body_sha256` within a
   repository-month.
4. Zero-count repository-months are retained.
5. HWC outcomes and AGC/HWC ratios are excluded.

The dynamic coefficient at event month `X` is interpreted in raw count units:
the estimated average change in AGC-like regular-function unique bodies per
repository-month at month `X` relative to Cursor adoption.

# Load Packages and Helper Functions

```{r load-packages}
library(data.table)
library(dplyr)
library(ggplot2)
library(didimputation)

if (!file.exists(helper_path)) {
  stop("Helper file not found: ", helper_path)
}
source(helper_path)
```

# Utility Functions

```{r utility-functions}
normalize_yyyymm <- function(x) {
  x <- as.character(x)
  x[x %in% c("", "NA", "NaN", "NULL", "None")] <- NA_character_
  x <- gsub("-", "", x)
  suppressWarnings(as.integer(x))
}

yyyymm_to_month_id <- function(x) {
  x <- as.integer(x)
  year <- x %/% 100L
  month <- x %% 100L
  out <- year * 12L + month
  out[is.na(x) | month < 1L | month > 12L] <- NA_integer_
  out
}

require_columns <- function(data, required, label) {
  missing <- setdiff(required, names(data))
  if (length(missing) > 0) {
    stop(label, " missing required columns: ", paste(missing, collapse = ", "))
  }
}

write_error_table <- function(errors, stage, output_path) {
  if (length(errors) == 0) {
    fwrite(
      data.frame(
        stage = character(),
        outcome = character(),
        error = character()
      ),
      output_path
    )
    return(invisible(NULL))
  }

  fwrite(
    data.frame(
      stage = stage,
      outcome = names(errors),
      error = unlist(errors),
      row.names = NULL,
      stringsAsFactors = FALSE
    ),
    output_path
  )
}
```

# Load and Validate Input Panel

```{r load-panel}
cat("Project root:", project_root, "\n")
cat("Panel path:", panel_path, "\n")
cat("Panel label:", panel_label, "\n")
cat("Specification:", specification_name, "\n")
cat("Output directory:", out_dir, "\n")
cat("NCLOC specification:", ncloc_spec, "\n")
cat("Time mode:", time_mode, "\n")
cat("Parse-exclusion mode:", parse_exclusion_mode, "\n")

if (!file.exists(panel_path)) {
  stop("Panel file not found: ", panel_path)
}

panel_raw <- fread(panel_path)

outcome_var <- "npr_agc_regular_module_function_unique_bodies"
outcome_label <- "AGC-Like Regular-Function Unique Bodies"
occurrence_var <- "has_npr_agc_regular_module_function_unique_body"
zero_var <- "zero_npr_agc_regular_module_function_unique_body_month"

base_required <- c(
  "dataset_source",
  "repo_name",
  "time",
  "event",
  "time_to_event",
  outcome_var,
  occurrence_var,
  zero_var,
  "log1p_age",
  "log1p_contributors",
  "log1p_stars",
  "log1p_issues",
  "ncloc_paper",
  "ncloc_python_snapshot",
  "analysis_ready_regular_module_function_agc_unique_body_paper_ncloc",
  "analysis_ready_regular_module_function_agc_unique_body_python_snapshot_ncloc",
  "has_parse_exclusion",
  "npr_detection_complete",
  "npr_specification",
  "npr_agc_threshold",
  "npr_algorithm_version",
  "npr_decision_rule",
  "npr_window_policy",
  "npr_function_aggregation",
  "npr_partial_body_policy",
  "npr_scoring_model",
  "npr_window_size_literal_space_tokens",
  "npr_perturbations_per_window",
  "npr_random_seed",
  "treatment_group",
  "regular_function_scope",
  "agc_count_unit",
  "agc_outcome_scale"
)
require_columns(panel_raw, base_required, "Input panel")

if (anyDuplicated(panel_raw[, .(dataset_source, repo_name, time)]) > 0) {
  stop("Input panel has duplicate dataset_source/repo_name/time keys.")
}
if (!all(panel_raw$dataset_source %in% c("control", "treatment"))) {
  stop("dataset_source contains unexpected values.")
}

forbidden_columns <- names(panel_raw)[
  grepl("hwc|ratio", names(panel_raw), ignore.case = TRUE)
]
if (length(forbidden_columns) > 0) {
  stop(
    "Focused input panel unexpectedly contains HWC or ratio columns: ",
    paste(forbidden_columns, collapse = ", ")
  )
}

specification_mismatch_rows <- sum(
  as.character(panel_raw$npr_specification) != specification_name,
  na.rm = TRUE
) + sum(is.na(panel_raw$npr_specification))
if (specification_mismatch_rows > 0) {
  stop(
    "npr_specification does not match the requested specification on ",
    specification_mismatch_rows,
    " rows."
  )
}

scope_mismatch_rows <- sum(
  as.character(panel_raw$regular_function_scope) != "module_function",
  na.rm = TRUE
) + sum(is.na(panel_raw$regular_function_scope))
if (scope_mismatch_rows > 0) {
  stop("Regular-function scope mismatch on ", scope_mismatch_rows, " rows.")
}

count_unit_expected <- "distinct_function_body_sha256_per_repository_month"
count_unit_mismatch_rows <- sum(
  as.character(panel_raw$agc_count_unit) != count_unit_expected,
  na.rm = TRUE
) + sum(is.na(panel_raw$agc_count_unit))
if (count_unit_mismatch_rows > 0) {
  stop("AGC count-unit mismatch on ", count_unit_mismatch_rows, " rows.")
}

outcome_scale_mismatch_rows <- sum(
  as.character(panel_raw$agc_outcome_scale) != "raw_count",
  na.rm = TRUE
) + sum(is.na(panel_raw$agc_outcome_scale))
if (outcome_scale_mismatch_rows > 0) {
  stop("AGC outcome-scale mismatch on ", outcome_scale_mismatch_rows, " rows.")
}

treatment_group_mismatch_rows <- sum(
  as.character(panel_raw$treatment_group) !=
    as.character(panel_raw$dataset_source),
  na.rm = TRUE
) + sum(is.na(panel_raw$treatment_group))
if (treatment_group_mismatch_rows > 0) {
  stop(
    "treatment_group does not match dataset_source on ",
    treatment_group_mismatch_rows,
    " rows."
  )
}

detection_complete_true <- panel_raw$npr_detection_complete %in%
  c(TRUE, 1L, 1.0, "True", "TRUE", "true", "1", "1.0")
detection_incomplete_rows <- sum(!detection_complete_true)
if (detection_incomplete_rows > 0) {
  stop(
    "npr_detection_complete is not uniformly true: ",
    detection_incomplete_rows,
    " rows are false, missing, or malformed."
  )
}

outcome_values <- panel_raw[[outcome_var]]
outcome_missing_rows <- sum(is.na(outcome_values))
outcome_negative_rows <- sum(outcome_values < 0, na.rm = TRUE)
outcome_noninteger_rows <- sum(
  !is.na(outcome_values) & abs(outcome_values - round(outcome_values)) > 1e-12
)
occurrence_mismatch_rows <- sum(
  as.integer(panel_raw[[occurrence_var]]) !=
    as.integer(outcome_values > 0),
  na.rm = TRUE
)
zero_flag_mismatch_rows <- sum(
  as.integer(panel_raw[[zero_var]]) !=
    as.integer(outcome_values == 0),
  na.rm = TRUE
)

if (
  outcome_missing_rows > 0 ||
    outcome_negative_rows > 0 ||
    outcome_noninteger_rows > 0 ||
    occurrence_mismatch_rows > 0 ||
    zero_flag_mismatch_rows > 0
) {
  stop(
    "Focused outcome contract violated. Missing: ", outcome_missing_rows,
    "; negative: ", outcome_negative_rows,
    "; noninteger: ", outcome_noninteger_rows,
    "; occurrence mismatches: ", occurrence_mismatch_rows,
    "; zero-flag mismatches: ", zero_flag_mismatch_rows
  )
}

cat("Loaded rows:", nrow(panel_raw), "\n")
cat("Loaded repositories:", uniqueN(panel_raw$repo_name), "\n")
cat("Zero-outcome rows:", sum(outcome_values == 0), "\n")
cat("Positive-outcome rows:", sum(outcome_values > 0), "\n")
cat("Total AGC unique-body repository-month occurrences:", sum(outcome_values), "\n")
```

# Configure Model

```{r configure-model}
if (ncloc_spec == "paper") {
  ncloc_column <- "ncloc_paper"
  readiness_column <-
    "analysis_ready_regular_module_function_agc_unique_body_paper_ncloc"
} else {
  ncloc_column <- "ncloc_python_snapshot"
  readiness_column <-
    "analysis_ready_regular_module_function_agc_unique_body_python_snapshot_ncloc"
}

covariates <- c(
  "log1p_age",
  ncloc_column,
  "log1p_contributors",
  "log1p_stars",
  "log1p_issues"
)
require_columns(
  panel_raw,
  c(outcome_var, covariates, readiness_column),
  "Configured model"
)

panel_data <- copy(panel_raw)
panel_data <- panel_data[get(readiness_column) == 1]
rows_after_readiness_filter <- nrow(panel_data)

if (parse_exclusion_mode == "parse_clean") {
  panel_data <- panel_data[has_parse_exclusion == 0]
}
rows_after_parse_filter <- nrow(panel_data)

if (nrow(panel_data) == 0) {
  stop("No rows remain after the explicit analysis filters.")
}

model_required <- c(outcome_var, covariates)
implicit_missing_rows <- sum(!complete.cases(panel_data[, ..model_required]))
if (implicit_missing_rows > 0) {
  stop(
    "Analysis-ready flag allowed rows with missing model variables: ",
    implicit_missing_rows
  )
}

panel_data[, time_yyyymm := normalize_yyyymm(time)]
event_yyyymm_raw <- normalize_yyyymm(panel_data$event)
event_yyyymm_raw[is.na(event_yyyymm_raw)] <- 0L
panel_data[, event_yyyymm := event_yyyymm_raw]

event_membership_mismatch_rows <- panel_data[
  ,
  sum((dataset_source == "treatment") != (event_yyyymm > 0L))
]
if (event_membership_mismatch_rows > 0) {
  stop(
    "Event encoding disagrees with dataset_source on ",
    event_membership_mismatch_rows,
    " rows."
  )
}

panel_data <- panel_data[
  event_yyyymm == 0L |
    (event_yyyymm > 202407L & event_yyyymm <= 202503L)
]
rows_after_cohort_filter <- nrow(panel_data)

panel_data[, repo_name_str := as.character(repo_name)]
panel_data[, repo_id := as.integer(factor(repo_name_str))]

if (time_mode == "original_yyyymm") {
  panel_data[, time_id := time_yyyymm]
  panel_data[, event_id := event_yyyymm]
  time_encoding_used <- "numeric_YYYYMM_original_notebook_compatible"
} else {
  panel_data[, time_id := yyyymm_to_month_id(time_yyyymm)]
  panel_data[, event_id := fifelse(
    event_yyyymm == 0L,
    0L,
    yyyymm_to_month_id(event_yyyymm)
  )]
  time_encoding_used <- "sequential_calendar_month_id"
}

panel_data <- panel_data[!is.na(time_id)]
panel_data <- panel_data[event_id == 0L | !is.na(event_id)]
panel_data[, treated := as.integer(event_id > 0L)]

first_stage_rhs <- paste(covariates, collapse = " + ")
first_stage_formula <- as.formula(
  paste0("~ ", first_stage_rhs, " | repo_id + time_id")
)

cat("Outcome:", outcome_var, "\n")
cat("Outcome unit: raw distinct-body count per repository-month\n")
cat("Readiness column:", readiness_column, "\n")
cat("Rows after readiness filter:", rows_after_readiness_filter, "\n")
cat("Rows after parse filter:", rows_after_parse_filter, "\n")
cat("Rows after cohort filter:", rows_after_cohort_filter, "\n")
cat("Rows used by models:", nrow(panel_data), "\n")
cat("Repositories used:", uniqueN(panel_data$repo_id), "\n")
cat("Time encoding:", time_encoding_used, "\n")
cat("First-stage formula:\n")
print(first_stage_formula)
```

# Panel Checks and Input Summary

```{r panel-checks}
panel_checks <- data.frame(
  check = c(
    "panel_label",
    "specification_name",
    "ncloc_specification",
    "readiness_column",
    "time_mode",
    "parse_exclusion_mode",
    "input_rows",
    "input_repositories",
    "forbidden_hwc_or_ratio_columns",
    "specification_mismatch_rows",
    "regular_function_scope_mismatch_rows",
    "count_unit_mismatch_rows",
    "outcome_scale_mismatch_rows",
    "treatment_group_mismatch_rows",
    "event_membership_mismatch_rows",
    "detection_incomplete_rows",
    "outcome_missing_rows",
    "outcome_negative_rows",
    "outcome_noninteger_rows",
    "occurrence_arithmetic_mismatch_rows",
    "zero_flag_arithmetic_mismatch_rows",
    "rows_after_readiness_filter",
    "rows_after_parse_filter",
    "rows_after_cohort_filter",
    "rows_used_by_models",
    "repositories_used_by_models",
    "treated_repositories",
    "control_repositories",
    "zero_outcome_rows_in_model_sample",
    "positive_outcome_rows_in_model_sample",
    "total_outcome_count_in_model_sample",
    "parse_exclusion_rows_in_model_sample",
    "outcome_missing_sum",
    "covariate_missing_sum",
    "npr_agc_threshold",
    "npr_algorithm_version",
    "npr_decision_rule",
    "npr_window_policy",
    "npr_function_aggregation",
    "npr_partial_body_policy",
    "npr_scoring_model",
    "npr_window_size_literal_space_tokens",
    "npr_perturbations_per_window",
    "npr_random_seed"
  ),
  value = c(
    panel_label,
    specification_name,
    ncloc_spec,
    readiness_column,
    time_mode,
    parse_exclusion_mode,
    nrow(panel_raw),
    uniqueN(panel_raw$repo_name),
    length(forbidden_columns),
    specification_mismatch_rows,
    scope_mismatch_rows,
    count_unit_mismatch_rows,
    outcome_scale_mismatch_rows,
    treatment_group_mismatch_rows,
    event_membership_mismatch_rows,
    detection_incomplete_rows,
    outcome_missing_rows,
    outcome_negative_rows,
    outcome_noninteger_rows,
    occurrence_mismatch_rows,
    zero_flag_mismatch_rows,
    rows_after_readiness_filter,
    rows_after_parse_filter,
    rows_after_cohort_filter,
    nrow(panel_data),
    uniqueN(panel_data$repo_id),
    uniqueN(panel_data[treated == 1, repo_id]),
    uniqueN(panel_data[treated == 0, repo_id]),
    sum(panel_data[[outcome_var]] == 0, na.rm = TRUE),
    sum(panel_data[[outcome_var]] > 0, na.rm = TRUE),
    sum(panel_data[[outcome_var]], na.rm = TRUE),
    sum(panel_data$has_parse_exclusion == 1, na.rm = TRUE),
    sum(is.na(panel_data[[outcome_var]])),
    sum(is.na(panel_data[, ..covariates])),
    paste(unique(panel_raw$npr_agc_threshold), collapse = ";"),
    paste(unique(panel_raw$npr_algorithm_version), collapse = ";"),
    paste(unique(panel_raw$npr_decision_rule), collapse = ";"),
    paste(unique(panel_raw$npr_window_policy), collapse = ";"),
    paste(unique(panel_raw$npr_function_aggregation), collapse = ";"),
    paste(unique(panel_raw$npr_partial_body_policy), collapse = ";"),
    paste(unique(panel_raw$npr_scoring_model), collapse = ";"),
    paste(unique(panel_raw$npr_window_size_literal_space_tokens), collapse = ";"),
    paste(unique(panel_raw$npr_perturbations_per_window), collapse = ";"),
    paste(unique(panel_raw$npr_random_seed), collapse = ";")
  ),
  stringsAsFactors = FALSE
)

print(panel_checks)
fwrite(
  panel_checks,
  file.path(
    out_dir,
    "borusyak_regular_module_function_agc_unique_body_panel_checks.csv"
  )
)

input_summary <- panel_data[, .(
  rows = .N,
  repositories = uniqueN(repo_id),
  total_agc_unique_body_count = sum(get(outcome_var), na.rm = TRUE),
  mean_agc_unique_body_count = mean(get(outcome_var), na.rm = TRUE),
  # median_agc_unique_body_count = median(get(outcome_var), na.rm = TRUE),
  median_agc_unique_body_count = as.numeric(median(get(outcome_var), na.rm = TRUE)),
  maximum_agc_unique_body_count = max(get(outcome_var), na.rm = TRUE),
  positive_month_share = mean(get(outcome_var) > 0, na.rm = TRUE),
  zero_month_share = mean(get(outcome_var) == 0, na.rm = TRUE),
  mean_ncloc = mean(get(ncloc_column), na.rm = TRUE)
), by = dataset_source]

print(input_summary)
fwrite(
  input_summary,
  file.path(
    out_dir,
    "borusyak_regular_module_function_agc_unique_body_input_summary.csv"
  )
)
```

# Static Borusyak Effect

```{r static-effect}
static_errors <- list()
static_result <- tryCatch(
  run_borusyak_static(
    data = panel_data,
    outcome_var = outcome_var,
    first_stage_formula = first_stage_formula,
    idname = "repo_id",
    tname = "time_id",
    gname = "event_id"
  ),
  error = function(e) {
    static_errors[[outcome_var]] <<- conditionMessage(e)
    NULL
  }
)

static_df <- extract_static_result(static_result, outcome_var)
static_df$outcome_label <- outcome_label
static_df$outcome_unit <- "distinct bodies per repository-month"
static_df$panel <- panel_label
static_df$specification <- specification_name
static_df$ncloc_spec <- ncloc_spec
static_df$time_mode <- time_mode
static_df$parse_exclusion_mode <- parse_exclusion_mode

print(static_df)
fwrite(
  static_df,
  file.path(
    out_dir,
    "borusyak_regular_module_function_agc_unique_body_static_effects.csv"
  )
)
write_error_table(
  static_errors,
  "static",
  file.path(
    out_dir,
    "borusyak_regular_module_function_agc_unique_body_static_errors.csv"
  )
)
```

# Dynamic Borusyak Effects

```{r dynamic-effects}
dynamic_errors <- list()
dynamic_result <- tryCatch(
  run_borusyak_dynamic(
    data = panel_data,
    outcome_var = outcome_var,
    first_stage_formula = first_stage_formula,
    horizon = -6:6,
    pretrends = -6:-2,
    idname = "repo_id",
    tname = "time_id",
    gname = "event_id"
  ),
  error = function(e) {
    dynamic_errors[[outcome_var]] <<- conditionMessage(e)
    NULL
  }
)

dynamic_df <- extract_dynamic_result(
  dynamic_result,
  outcome = outcome_var,
  outcome_label = outcome_label,
  min_horizon = -6,
  max_horizon = 6
)

if (nrow(dynamic_df) > 0) {
  dynamic_df$outcome_unit <- "distinct bodies per repository-month"
  dynamic_df$panel <- panel_label
  dynamic_df$specification <- specification_name
  dynamic_df$ncloc_spec <- ncloc_spec
  dynamic_df$time_mode <- time_mode
  dynamic_df$parse_exclusion_mode <- parse_exclusion_mode
}

print(dynamic_df)
fwrite(
  dynamic_df,
  file.path(
    out_dir,
    "borusyak_regular_module_function_agc_unique_body_dynamic_effects.csv"
  )
)
write_error_table(
  dynamic_errors,
  "dynamic",
  file.path(
    out_dir,
    "borusyak_regular_module_function_agc_unique_body_dynamic_errors.csv"
  )
)
```

# Dynamic Plot

```{r dynamic-plot, fig.width=10, fig.height=4.5}
if (nrow(dynamic_df) > 0) {
  plot_object <- ggplot(dynamic_df, aes(x = time, y = estimate)) +
    geom_errorbar(
      data = subset(dynamic_df, significant %in% TRUE),
      aes(ymin = conf_low, ymax = conf_high),
      width = 0.4,
      linetype = "solid"
    ) +
    geom_errorbar(
      data = subset(dynamic_df, !(significant %in% TRUE)),
      aes(ymin = conf_low, ymax = conf_high),
      width = 0.4,
      linetype = "dotted"
    ) +
    geom_point(
      data = subset(dynamic_df, significant %in% TRUE),
      shape = 19,
      size = 1.8
    ) +
    geom_point(
      data = subset(dynamic_df, !(significant %in% TRUE)),
      shape = 21,
      fill = "transparent",
      size = 1.8
    ) +
    geom_hline(yintercept = 0, linetype = "dashed") +
    geom_vline(xintercept = -0.5, linetype = "dashed") +
    scale_x_continuous(breaks = -6:6) +
    coord_cartesian(xlim = c(-6.5, 6.5)) +
    labs(
      title = paste(
        "Borusyak DiD: AGC-Like Regular-Function Unique Bodies",
        panel_label
      ),
      subtitle = paste(
        "Raw count outcome | NCLOC:", ncloc_spec,
        "| Time:", time_encoding_used,
        "| Parse:", parse_exclusion_mode
      ),
      x = "Months Relative to Cursor Adoption",
      y = "Estimated Change in Distinct AGC-Like Bodies per Repository-Month",
      caption = paste(
        "Filled dots: confidence interval excludes 0.",
        "Zero-count repository-months are retained."
      )
    ) +
    theme_minimal() +
    theme(
      panel.grid.minor = element_blank(),
      plot.caption = element_text(hjust = 0.5, size = 8)
    )

  print(plot_object)
  ggsave(
    filename = file.path(
      out_dir,
      "dynamic_effects_borusyak_regular_module_function_agc_unique_body.pdf"
    ),
    plot = plot_object,
    width = 10,
    height = 4.5
  )
} else {
  cat("No dynamic effects to plot.\n")
}
```

# Final Model Validation

```{r final-model-validation}
static_model_error_count <- length(static_errors)
dynamic_model_error_count <- length(dynamic_errors)

static_effect_complete <- nrow(static_df) == 1 &&
  static_df$outcome[1] == outcome_var &&
  !is.na(static_df$estimate[1])

dynamic_effects_nonempty <- nrow(dynamic_df) > 0 &&
  all(dynamic_df$outcome == outcome_var)

dynamic_pre_period_present <- if (dynamic_effects_nonempty) {
  any(dynamic_df$time < 0)
} else {
  FALSE
}

dynamic_post_period_present <- if (dynamic_effects_nonempty) {
  any(dynamic_df$time >= 0)
} else {
  FALSE
}

significant_pre_period_count <- if (dynamic_effects_nonempty) {
  sum(dynamic_df$time <= -2 & dynamic_df$significant %in% TRUE)
} else {
  NA_integer_
}

final_model_validation <- data.frame(
  check = c(
    "static_model_error_count",
    "dynamic_model_error_count",
    "static_effect_complete",
    "dynamic_effects_nonempty",
    "dynamic_pre_period_present",
    "dynamic_post_period_present",
    "significant_pre_period_count"
  ),
  value = c(
    static_model_error_count,
    dynamic_model_error_count,
    static_effect_complete,
    dynamic_effects_nonempty,
    dynamic_pre_period_present,
    dynamic_post_period_present,
    significant_pre_period_count
  ),
  stringsAsFactors = FALSE
)

print(final_model_validation)
fwrite(
  final_model_validation,
  file.path(
    out_dir,
    "borusyak_regular_module_function_agc_unique_body_final_model_validation.csv"
  )
)

if (static_model_error_count > 0) {
  stop("Static model failure: ", paste(names(static_errors), collapse = ", "))
}
if (dynamic_model_error_count > 0) {
  stop("Dynamic model failure: ", paste(names(dynamic_errors), collapse = ", "))
}
if (!static_effect_complete) {
  stop("Static effect is incomplete or contains a missing estimate.")
}
if (!dynamic_effects_nonempty) {
  stop("Dynamic effects are empty or missing the focused outcome.")
}
if (!dynamic_pre_period_present || !dynamic_post_period_present) {
  stop("Dynamic effects do not contain both pre- and post-treatment periods.")
}
```

# Metadata

```{r metadata}
metadata <- data.frame(
  key = c(
    "script",
    "helper_file",
    "panel_label",
    "panel_path",
    "out_dir",
    "specification_name",
    "ncloc_specification",
    "ncloc_column",
    "readiness_column",
    "time_mode",
    "parse_exclusion_mode",
    "outcome",
    "outcome_label",
    "outcome_scale",
    "outcome_unit",
    "function_scope",
    "classification",
    "count_unit",
    "covariates",
    "first_stage_formula",
    "rows_after_readiness_filter",
    "rows_after_parse_filter",
    "rows_after_cohort_filter",
    "rows_used_by_models",
    "repositories_used_by_models",
    "estimator",
    "time_encoding",
    "horizon",
    "pretrends",
    "static_model_error_count",
    "dynamic_model_error_count",
    "significant_pre_period_count",
    "npr_agc_threshold",
    "npr_algorithm_version",
    "npr_decision_rule",
    "npr_window_policy",
    "npr_function_aggregation",
    "npr_partial_body_policy",
    "npr_scoring_model",
    "npr_window_size_literal_space_tokens",
    "npr_perturbations_per_window",
    "npr_random_seed",
    "interpretation_note"
  ),
  value = c(
    "proc_r/DiffInDiffBorusyak_regular_module_function_agc_unique_body-v1.Rmd",
    helper_path,
    panel_label,
    panel_path,
    out_dir,
    specification_name,
    ncloc_spec,
    ncloc_column,
    readiness_column,
    time_mode,
    parse_exclusion_mode,
    outcome_var,
    outcome_label,
    "raw_count",
    "distinct bodies per repository-month",
    "module_function",
    "AGC-like only",
    count_unit_expected,
    paste(covariates, collapse = " + "),
    paste(deparse(first_stage_formula), collapse = " "),
    rows_after_readiness_filter,
    rows_after_parse_filter,
    rows_after_cohort_filter,
    nrow(panel_data),
    uniqueN(panel_data$repo_id),
    "Borusyak imputation via didimputation::did_imputation",
    time_encoding_used,
    "-6:6",
    "-6:-2",
    static_model_error_count,
    dynamic_model_error_count,
    significant_pre_period_count,
    paste(unique(panel_raw$npr_agc_threshold), collapse = ";"),
    paste(unique(panel_raw$npr_algorithm_version), collapse = ";"),
    paste(unique(panel_raw$npr_decision_rule), collapse = ";"),
    paste(unique(panel_raw$npr_window_policy), collapse = ";"),
    paste(unique(panel_raw$npr_function_aggregation), collapse = ";"),
    paste(unique(panel_raw$npr_partial_body_policy), collapse = ";"),
    paste(unique(panel_raw$npr_scoring_model), collapse = ";"),
    paste(unique(panel_raw$npr_window_size_literal_space_tokens), collapse = ";"),
    paste(unique(panel_raw$npr_perturbations_per_window), collapse = ";"),
    paste(unique(panel_raw$npr_random_seed), collapse = ";"),
    paste(
      "A dynamic coefficient at month X is the estimated average change",
      "in distinct AGC-like synchronous module-function bodies per",
      "repository-month. The AGC-like label is a detector classification,",
      "not verified AI provenance."
    )
  ),
  stringsAsFactors = FALSE
)

print(metadata)
fwrite(
  metadata,
  file.path(
    out_dir,
    "borusyak_regular_module_function_agc_unique_body_metadata.csv"
  )
)
```

# Session Info

```{r session-info}
sessionInfo()
```
